---
title: "Ribo Figures"
output: html_document
date: "2024-09-04"
editor_options: 
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(ggplot2)
library(ggpubr)
library(gridExtra)
library(ggpubr)
library(ComplexHeatmap)
library(survival)
library(survminer)
library(reshape2)
library(enrichplot)
library(dplyr)
library(extrafont)
library(ggrepel)
library(tidyr)
library(BSgenome.Hsapiens.NCBI.GRCh38)
library(BSgenome)
library(stringr)
library(ggmsa)
library(ggVennDiagram)
library(clusterProfiler)
library(ggh4x)
library(org.Hs.eg.db)
extrafont::loadfonts()
```

#Colors
```{r}
Parent_col<-"#0096FE"
HDR_col<-"#ced4da"
KO_col<-"#778da9"
L100_col<-"#FF2600"
L100_col2<-"#B93720"
L102_col<-"#FF40FF"
GFP_col<-"#6EA533"
KD_col<-"#7D6642"
```


#Figure S1

#Conservation
```{r Fig3A-1, message=F, warning=F,echo=F,fig.width=4, fig.height=1.5}
getwd()
my_cutstom <- data.frame(names = c(LETTERS[1:26],"-"), 
                         color = "#00000000", 
                         stringsAsFactors = FALSE)
ggmsa("FigureS1/Conservation/PCBP1_msa.fa",35,45, custom_color =my_cutstom,
      font = "helvetical", char_width = 0.4, seq_name = TRUE)+
  scale_y_discrete(position = "right")+
  theme(legend.position = "none",
        legend.text = element_text(family="Arial",size=8, color="black"),
        legend.title = element_blank(),
        panel.background = element_blank(),
        plot.background = element_blank(),
        panel.border = element_blank(),
        legend.background = element_blank(),
        legend.key.size = unit(0.4, "cm"),
        axis.text.y=element_text(family="Arial",size=8, color="black"),
        axis.text.x=element_blank(),
        axis.ticks=element_blank(),
        axis.line=element_blank())
ggsave("FigureS1/Seq_cons.pdf",height = 1.5,width = 4)
```

#Fig S1A
```{r,fig.width=1.75, fig.height=1}
rm(list=ls())
r_sec<-read.table("FigureS1/C2bbe1 SEC/R File/C2bbe1_SEC_.txt",header=T,sep="\t")

#Mean
r_sec$WT_Mean<-apply(r_sec[c("WT1","WT2","WT3")],1,mean,na.rm=T)
r_sec$L100Q_Mean<-apply(r_sec[c("MUT1","MUT2","MUT3")],1,mean,na.rm=T)

#sd
r_sec$WT_sd<-apply(r_sec[c("WT1","WT2","WT3")],1,sd,na.rm=T)
r_sec$L100Q_sd<-apply(r_sec[c("MUT1","MUT2","MUT3")],1,sd,na.rm=T)

#se
r_sec$WT_se<-r_sec$WT_sd/sqrt(3)
r_sec$L100Q_se<-r_sec$L100Q_sd/sqrt(3)

#test
r_sec$P_val<-NA
for (i in 1:nrow(r_sec)){
  test<-t.test(r_sec[i,c("WT1","WT2","WT3")],r_sec[i,c("MUT1","MUT2","MUT3")])
  r_sec$P_val[i]<-test$p.value
}
r_sec$FDR<-p.adjust(r_sec$P_val,method = "BH")

r_sec<-r_sec %>% mutate(Label=case_when(
  FDR<0.0001~"****",
  FDR<0.001~"***",
  FDR<0.01~"**",
  FDR<0.05~"*"
))


r_sec$wt_ymax<-r_sec$WT_Mean+r_sec$WT_se
r_sec$mut_ymax<-r_sec$L100Q_Mean+r_sec$L100Q_se

r_sec$Ypos<-apply(r_sec[c("wt_ymax","mut_ymax")],1,max)
r_sec$Fraction<-factor(r_sec$Fraction)


wt<-r_sec[c("Fraction","WT_Mean","WT_sd","WT_se")]
mut<-r_sec[c("Fraction","L100Q_Mean","L100Q_sd","L100Q_se")]

colnames(wt)<-c("Fraction","Mean","SD","SE")
colnames(mut)<-c("Fraction","Mean","SD","SE")

wt$Group<-"WT"
mut$Group<-"L100Q"

df<-data.frame(rbind(wt,mut))
df$Group<-factor(df$Group,levels=c("WT","L100Q"))
df$Fraction<-factor(df$Fraction)

ggplot()+
  geom_line(data=df,aes(x=Fraction,y=Mean,group = Group,color=Group),size=.25)+
  geom_point(data=df,aes(x=Fraction,y=Mean),color="black",size=0.3)+
  scale_color_manual(values=c("WT"=Parent_col, "L100Q"=L100_col))+
  geom_errorbar(data=df,aes(x=Fraction,ymin=Mean-SE, ymax=Mean+SE), color="black",width=0.3,size=0.3)+
  geom_text(inherit.aes = F,data = r_sec,aes(x=Fraction,y=Ypos,label=Label),size=2,vjust=-0.5)+
  theme_classic()+
  lims(y=c(0,1))+
  xlab("Fraction")+
  ylab("Rel. Signal")+
  theme_classic()+
  theme(legend.position = c(0.2,0.85),
        axis.text=element_text(family="Arial",size=6, color="black"),
        axis.title = element_text(family="Arial",size=6, color="black"),
        legend.text = element_text(family="Arial",size=6, color="black"),
        legend.title = element_blank(),
        panel.background = element_blank(),
        plot.background = element_blank(), 
        panel.border = element_blank(),
        legend.background = element_blank(),
        legend.key.size = unit(0.2, "cm"))
ggsave("FigureS1/FigS1A.pdf",height = 1,width = 1.75)
```

#Fig S1B
```{r,fig.width=1.75, fig.height=1}
rm(list=ls())
r_sec<-read.table("FigureS1/L100P:L102Q SEC/R_file_L100P/L100P_SEC_.txt",header=T,sep="\t")
r_sec2<-read.table("FigureS2/L102Q SEC/SEC_L102Q.txt",header=T,sep="\t")
colnames(r_sec2)<-c("Fraction","L1021","L1022","L1023")

r_sec<-merge(r_sec,r_sec2,by="Fraction")

#Mean
r_sec$WT_Mean<-apply(r_sec[c("WT1","WT2","WT3")],1,mean,na.rm=T)
r_sec$L100Q_Mean<-apply(r_sec[c("MUT1","MUT2","MUT3")],1,mean,na.rm=T)
r_sec$L102Q_Mean<-apply(r_sec[c("L1021","L1022","L1023")],1,mean,na.rm=T)

#sd
r_sec$WT_sd<-apply(r_sec[c("WT1","WT2","WT3")],1,sd,na.rm=T)
r_sec$L100Q_sd<-apply(r_sec[c("MUT1","MUT2","MUT3")],1,sd,na.rm=T)
r_sec$L102Q_sd<-apply(r_sec[c("L1021","L1022","L1023")],1,sd,na.rm=T)

#se
r_sec$WT_se<-r_sec$WT_sd/sqrt(3)
r_sec$L100Q_se<-r_sec$L100Q_sd/sqrt(3)
r_sec$L102Q_se<-r_sec$L102Q_sd/sqrt(3)


#test
r_sec$L100P_pval<-NA
r_sec$L102_pval<-NA
for (i in 1:nrow(r_sec)){
  test<-t.test(r_sec[i,c("WT1","WT2","WT3")],r_sec[i,c("MUT1","MUT2","MUT3")])
  test2<-t.test(r_sec[i,c("WT1","WT2","WT3")],r_sec[i,c("L1021","L1022","L1023")])
  r_sec$L100P_pval[i]<-test$p.value
  r_sec$L102_pval[i]<-test$p.value
  
}
r_sec$L100P_FDR<-p.adjust(r_sec$L100P_pval,method = "BH")
r_sec$L102_FDR<-p.adjust(r_sec$L102_pval,method = "BH")


r_sec<-r_sec %>% mutate(L100P_Label=case_when(
  L100P_FDR<0.0001~"****",
  L100P_FDR<0.001~"***",
  L100P_FDR<0.01~"**",
  L100P_FDR<0.05~"*"
))

r_sec<-r_sec %>% mutate(L102_Label=case_when(
  L102_FDR<0.0001~"****",
  L102_FDR<0.001~"***",
  L102_FDR<0.01~"**",
  L102_FDR<0.05~"*"
))

r_sec$wt_ymax<-r_sec$WT_Mean+r_sec$WT_se
r_sec$mut_ymax<-r_sec$L100Q_Mean+r_sec$L100Q_se

r_sec$Ypos<-apply(r_sec[c("wt_ymax","mut_ymax")],1,max)
r_sec$Fraction<-factor(r_sec$Fraction)


wt<-r_sec[c("Fraction","WT_Mean","WT_sd","WT_se")]
mut<-r_sec[c("Fraction","L100Q_Mean","L100Q_sd","L100Q_se")]
l102<-r_sec[c("Fraction","L102Q_Mean","L102Q_sd","L102Q_se")]

colnames(wt)<-c("Fraction","Mean","SD","SE")
colnames(mut)<-c("Fraction","Mean","SD","SE")
colnames(l102)<-c("Fraction","Mean","SD","SE")

wt$Group<-"WT"
mut$Group<-"L100P"
l102$Group<-"L102Q"

df<-data.frame(rbind(wt,mut,l102))
df$Group<-factor(df$Group,levels=c("WT","L100P","L102Q"))
df$Fraction<-factor(df$Fraction)

ggplot()+
  geom_line(data=df,aes(x=Fraction,y=Mean,group = Group,color=Group),size=.25)+
  geom_point(data=df,aes(x=Fraction,y=Mean),color="black",size=0.3)+
  scale_color_manual(values=c("WT"=Parent_col, "L100P"="#DC9581","L102Q"=L102_col))+
  geom_errorbar(data=df,aes(x=Fraction,ymin=Mean-SE, ymax=Mean+SE), color="black",width=0.3,size=0.3)+
  geom_text(inherit.aes = F,data = r_sec,aes(x=Fraction,y=L100Q_Mean,label=L100P_Label),size=2,vjust=-0.8,color="#DC9581")+
  geom_text(inherit.aes = F,data = r_sec,aes(x=Fraction,y=L102Q_Mean,label=L102_Label),size=2,vjust=0.2,color=L102_col)+
  theme_classic()+
  lims(y=c(0,1))+
  xlab("Fraction")+
  ylab("Rel. Signal")+
  theme_classic()+
  theme(legend.position = c(0.2,0.8),
        axis.text=element_text(family="Arial",size=6, color="black"),
        axis.title = element_text(family="Arial",size=6, color="black"),
        legend.text = element_text(family="Arial",size=6, color="black"),
        legend.title = element_blank(),
        panel.background = element_blank(),
        plot.background = element_blank(), 
        panel.border = element_blank(),
        legend.background = element_blank(),
        legend.key.size = unit(0.2, "cm"))
ggsave("FigureS1/FigS1B.pdf",height = 1,width = 1.75)
```

#Fig S1C
```{r,fig.width=3, fig.height=1.5}
NMR<-read.table("Figure 1-2 Combined /Figure2/Data/NMR/txt_file/NMR.txt",sep="\t",header=T)
names(NMR)=c("ppm","Protein","Intensity")
NMR$Protein<-factor(NMR$Protein,levels=c("WT","L100Q"))

ggplot()+
  geom_line(data=NMR,aes(x=ppm,y=Intensity,color=Protein,group=Protein),size=.2)+
  scale_color_manual(values=c("WT"=Parent_col, "L100Q"=L100_col),labels=c("WT"=bquote(KH1-2^WT),"L100Q"=bquote(KH1-2^L100Q)))+
  theme_classic()+
  xlab(bquote({}^1*H~"("*ppm*")"))+
  ylab("Intensity")+
  lims(x=c(10.5,5))+
  theme_classic()+
  theme(legend.position = c(0.15,0.9),
        axis.text=element_text(family="Arial",size=6, color="black"),
        axis.text.y=element_blank(),
        axis.title = element_text(family="Arial",size=6, color="black"),
        axis.title.y=element_blank(),
        legend.text = element_text(family="Arial",size=6, color="black"),
        legend.title = element_blank(),
        axis.ticks.y =element_blank(), 
        panel.background = element_blank(),
        plot.background = element_blank(), 
        panel.border = element_blank(),
        legend.background = element_blank(),
        legend.key.size = unit(0.3, "cm"))
ggsave("FigureS1/FigS1C.pdf",height = 1.5,width = 3)

```


#Figure S2

#Figure S2A
```{r,fig.width=1.5, fig.height=1.5}
rm(list=ls())
df<-read.table("Figure_Tables/all_kmer.txt",header=T)
df<-df[c("L100Q_r1_200","L100Q_r2_200","WT_r1_200","WT_r2_200")]

df$L100Q_mean<-rowMeans(df[c("L100Q_r1_200","L100Q_r2_200")])
df$WT_mean<-rowMeans(df[c("WT_r1_200","WT_r2_200")])

df$Col<-Parent_col
df$Col[which(df$L100Q_mean>df$WT_mean)]<-L100_col

ggplot(df,aes(x = WT_mean,y = L100Q_mean,color=Col,fill = Col))+
  geom_point(shape = 21,alpha=0.5,size=1)+
  scale_fill_identity()+
  scale_colour_identity()+
  lims(x=c(1,3.5),y=c(1,3.5))+
  labs(x="Enrichment (WT) ",y="Enrichment (L100Q)")+
  theme_classic()+
  geom_abline(slope=1, intercept=0,linetype = "dashed")+
  theme(legend.position = "none",
        axis.text=element_text(family="Arial",size=6, color="black"),
        axis.title = element_text(family="Arial",size=6, color="black"),
        panel.background = element_blank(),
        plot.background = element_blank(), 
        panel.border = element_blank(),
        legend.background = element_blank())
ggsave("FigureS3/FigS2A.pdf",width=1.5,height=1.5)



```

#Figure S2A-Insert
```{r}
rm(list=ls())
vals=read.table("Figure3/Data/SPR2/Grouped Rmax, Kd, ka, koff_2.txt", sep = "\t", header = T)
RU=subset(vals, vals$Vals=="Rmax")
RU_melt<-reshape2::melt(RU[c("WT","L100Q")])

test <- compare_means(value ~ variable,comparisons =list(c("WT","L100Q")), p.adjust.method = "fdr", method='t.test', data = RU_melt)
test<-test %>% mutate(y.position = c(330))

ggplot(data=RU_melt,aes(y=value,x=variable, color=variable))+
  geom_boxplot(alpha=1,width=0.5,fatten = 1)+
  geom_point(aes(y=value,x=variable, color=variable),size=0.3)+
  stat_pvalue_manual(test, label = "p.adj",xmin="group1",xmax="group2",size = 2)+
  scale_color_manual(values=c("L100Q"=L100_col, "WT"=Parent_col))+
  scale_fill_manual(values=c("L100Q"=L100_col, "WT"=Parent_col))+
  theme_classic()+
  labs(y="Response Units")+
  lims(y=c(0,350))+
  theme(
    axis.text = element_text(family="Arial",color="black",size=6), 
    axis.title.x = element_blank(), 
    axis.title.y = element_text(family="Arial",color ="black", size=6),
    legend.position = "none",
    plot.background = element_blank(),
    panel.background = element_blank(),
    strip.background = element_blank(),
    strip.text.x = element_blank() )+
  xlab("")+
  theme(legend.position = "none")
ggsave("FigureS3/FigS2RU.pdf",width=1.2,height=1.4)

```

#Figure S2C-new
```{r,fig.width=1.5, fig.height=1.5}
rm(list=ls())
df<-read.delim("FigureS3/Mass_spec_Expression/Normalized_PCBP1_expression.txt")
df_melt<-reshape2::melt(df)
df_melt$variable<-gsub("[.]","-",df_melt$variable)
df_melt$variable<-factor(df_melt$variable,levels=c("Parent","Silent","L100Q-1","L100Q-2","KO"))

test <- compare_means(value ~ variable,comparisons =list(c("Parent","Silent"),c("Parent","L100Q-1"),c("Parent","L100Q-2"),c("Parent","KO")), p.adjust.method = "fdr", method='t.test', data = df_melt)
test<-test[which(test$group1=="Parent"),]
test<-test %>% mutate(y.position = c(1.1,1.25,1.35,1.45))

ggplot(df_melt,aes(x=variable,y=value))+
  geom_boxplot(aes(color=variable))+
  geom_point(size=0.3)+
  stat_pvalue_manual(test, label = "p.signif",xmin="group1",xmax="group2",size = 2)+
  theme_classic()+
  lims(y=c(0,1.5))+
  scale_color_manual(values = c("WT"=Parent_col,"L100Q-2"=L100_col2,"L100Q-1"=L100_col,"KO"=KO_col,"Silent"=HDR_col))+
  labs(y="Norm. PCBP1 expression")+
  theme(legend.position = "none",
        axis.text=element_text(family="Arial",size=6, color="black"),
        axis.text.x=element_text(family="Arial",size=6, color="black",angle=45,hjust=1),
        axis.title = element_text(family="Arial",size=6, color="black"),
        axis.title.x = element_blank(),
        panel.background = element_blank(),
        plot.background = element_blank(), 
        panel.border = element_blank(),
        legend.background = element_blank(),
        plot.clip = "off")
ggsave("FigureS3/FigS2C_MS.pdf",width=1.5,height=1.5)

```

#Figure S2C-new2
```{r,fig.width=1.5, fig.height=1.5}
rm(list=ls())
df<-read.delim("FigureS3/Mass_spec_Expression/L100Q_peptide_percentage.txt")
df_melt<-reshape2::melt(df)
df_melt$variable<-gsub("[.]","-",df_melt$variable)
df_melt<-df_melt[grepl("L100Q",df_melt$variable),]

df_mean<-df_melt %>% group_by(variable) %>% summarize(Mean=mean(value)) %>% data.frame()
df_mean$variable<-factor(df_mean$variable,levels=c("L100Q-1","L100Q-2"))
df_mean$WT<-1-df_mean$Mean
df_mean_melt<-reshape2::melt(df_mean,id.vars = "variable")
colnames(df_mean_melt)<-c("Group","variable","value")
df_mean_melt$variable<-as.character(df_mean_melt$variable)
df_mean_melt$variable[which(df_mean_melt$variable=="Mean")]<-"L100Q"
df_mean_melt$variable<-factor(df_mean_melt$variable,levels=c("WT","L100Q"))

ggplot(df_mean_melt, aes(x=Group, y=value, fill=variable)) + 
  geom_bar(stat="identity", color="black",width=0.5,alpha=0.9,position="fill") +
  geom_point(inherit.aes = F,data=df_melt,aes(x=variable,y=value),size=.75)+
  theme_classic()+
  lims(y=c(0,1))+
  scale_fill_manual(values = c("WT"=Parent_col,"L100Q"=L100_col))+
  labs(y="% L100Q peptides")+
  theme(legend.position = "none",
        axis.text=element_text(family="Arial",size=6, color="black"),
        axis.text.x=element_text(family="Arial",size=6, color="black",angle=45,hjust=1),
        axis.title = element_text(family="Arial",size=6, color="black"),
        axis.title.x = element_blank(),
        panel.background = element_blank(),
        plot.background = element_blank(), 
        panel.border = element_blank(),
        legend.background = element_blank())
ggsave("FigureS3/FigS2C_MS2.pdf",width=1,height=1.5)

```

#Fig S2E
```{r,fig.width=1.8, fig.height=1.5}
rm(list=ls())
WT<-read.table("Figure3/Data/eCLIP/Collapsed/PCBP1_WT_Low_Meta.bed",sep = "\t")
L100Q<-read.table("Figure3/Data/eCLIP/Collapsed/PCBP1_l100_Low_Meta.bed",sep = "\t")
L100Q2<-read.table("Figure3/Data/eCLIP/Collapsed/PCBP1_F10_Meta.bed",sep = "\t")
HDR<-read.table("Figure3/Data/eCLIP/Collapsed/PCBP1_HDR_Meta.bed",sep = "\t")


WT$Width<-WT$V3-WT$V2
L100Q$Width<-L100Q$V3-L100Q$V2
L100Q2$Width<-L100Q2$V3-L100Q2$V2
HDR$Width<-HDR$V3-HDR$V2



df<-rbind(data.frame("Group"="WT","Val"=WT$Width),data.frame("Group"="L100Q","Val"=L100Q$Width),
          data.frame("Group"="L100Q-2","Val"=L100Q2$Width),data.frame("Group"="Silent","Val"=HDR$Width))

df$Group<-factor(df$Group,levels=c("WT","Silent","L100Q","L100Q-2"))
ggplot(df,aes(x = Val,color=Group))+
  geom_density()+
  scale_color_manual(values = c("WT" =Parent_col, "L100Q" =L100_col,"Silent"=HDR_col,"L100Q-2"=L100_col2))+
  #annotate("text", x = 250, y = 0.001, label = bquote(italic(P)<2.2e-16), color = "black", size = 2, family = "Arial") + 
  lims(x=c(0,500))+
  theme_classic()+
  labs(x="Peak Width (bp)",y="density")+
  theme(legend.position = c(.85,.85),
        legend.key.size = unit(0.2, "cm"),
        legend.spacing.y = unit(-0.15, "cm"),
        axis.text=element_text(family="Arial",size=6, color="black"),
        axis.title = element_text(family="Arial",size=6, color="black"),
        legend.text = element_text(family="Arial",size=6, color="black"),
        legend.title = element_blank(),
        panel.background = element_blank(),
        plot.background = element_blank(), 
        panel.border = element_blank(),
        legend.background = element_blank())
ggsave("FigureS3/FigS2E.pdf",width=1.8,height=1.5)
```

#Fig S2F
```{r,fig.width=1.8, fig.height=1.5}
rm(list=ls())
WT<-read.table("Figure3/Data/eCLIP/Collapsed/PCBP1_WT_Low_Meta.bed",sep = "\t")
L100Q<-read.table("Figure3/Data/eCLIP/Collapsed/PCBP1_l100_Low_Meta.bed",sep = "\t")
L100Q2<-read.table("Figure3/Data/eCLIP/Collapsed/PCBP1_F10_Meta.bed",sep = "\t")
HDR<-read.table("Figure3/Data/eCLIP/Collapsed/PCBP1_HDR_Meta.bed",sep = "\t")


df<-rbind(data.frame("Group"="WT","Val"=WT$V7),data.frame("Group"="L100Q","Val"=L100Q$V7),
          data.frame("Group"="L100Q-2","Val"=L100Q2$V7),data.frame("Group"="Silent","Val"=HDR$V7))

df$Group<-factor(df$Group,levels=c("WT","Silent","L100Q","L100Q-2"))
ggplot(df,aes(x = Val,color=Group))+
  stat_ecdf()+
  scale_color_manual(values = c("WT" =Parent_col, "L100Q" =L100_col,"L100Q-2"=L100_col2,"Silent"=HDR_col))+
  #annotate("text", x = 8, y = .92, label = bquote(italic(P)<2.2e-16), color = "black", size = 2, family = "Arial") + 
  theme_classic()+
  labs(x="Peak Enrichment",y="ecdf")+
  theme(legend.position = c(.8,.2),
        legend.key.size = unit(0.2, "cm"),
        legend.spacing.y = unit(-0.15, "cm"),
        axis.text=element_text(family="Arial",size=6, color="black"),
        axis.title = element_text(family="Arial",size=6, color="black"),
        legend.text = element_text(family="Arial",size=6, color="black"),
        legend.title = element_blank(),
        panel.background = element_blank(),
        plot.background = element_blank(), 
        panel.border = element_blank(),
        legend.background = element_blank())
ggsave("FigureS3/FigS2F.pdf",width=1.8,height=1.5)
```

#Fig S2G
```{r,fig.width=1.8, fig.height=1.5}
rm(list=ls())
WT<-read.table("Figure3/Data/eCLIP/Collapsed/PCBP1_WT_Low_Meta.bed",sep = "\t")
L100Q<-read.table("Figure3/Data/eCLIP/Collapsed/PCBP1_l100_Low_Meta.bed",sep = "\t")
L100Q2<-read.table("Figure3/Data/eCLIP/Collapsed/PCBP1_F10_Meta.bed",sep = "\t")
HDR<-read.table("Figure3/Data/eCLIP/Collapsed/PCBP1_HDR_Meta.bed",sep = "\t")


WT_gr<-makeGRangesFromDataFrame(WT,seqnames.field="V1",start.field="V2",end.field="V3",strand.field="V6")
L100Q_gr<-makeGRangesFromDataFrame(L100Q,seqnames.field="V1",start.field="V2",end.field="V3",strand.field="V6")
L100Q2_gr<-makeGRangesFromDataFrame(L100Q2,seqnames.field="V1",start.field="V2",end.field="V3",strand.field="V6")
HDR_gr<-makeGRangesFromDataFrame(HDR,seqnames.field="V1",start.field="V2",end.field="V3",strand.field="V6")


#Get Seq
bs<-BSgenome.Hsapiens.NCBI.GRCh38
seqlevelsStyle(bs) <- "UCSC"

WT_seqs<-getSeq(bs,WT_gr) %>% data.frame()
L100Q_seqs<-getSeq(bs,L100Q_gr) %>% data.frame()
HDR_seqs<-getSeq(bs,HDR_gr) %>% data.frame()
L100Q2_seqs<-getSeq(bs,L100Q2_gr) %>% data.frame()

WT_seqs$C_count<-str_count(WT_seqs$.,'C')
L100Q_seqs$C_count<-str_count(L100Q_seqs$.,'C')
HDR_seqs$C_count<-str_count(HDR_seqs$.,'C')
L100Q2_seqs$C_count<-str_count(L100Q2_seqs$.,'C')

WT_seqs$All_count<-nchar(WT_seqs$.)
L100Q_seqs$All_count<-nchar(L100Q_seqs$.)
HDR_seqs$All_count<-nchar(HDR_seqs$.)
L100Q2_seqs$All_count<-nchar(L100Q2_seqs$.)

WT_seqs$Prop<-WT_seqs$C_count/WT_seqs$All_count
L100Q_seqs$Prop<-L100Q_seqs$C_count/L100Q_seqs$All_count
HDR_seqs$Prop<-HDR_seqs$C_count/HDR_seqs$All_count
L100Q2_seqs$Prop<-L100Q2_seqs$C_count/L100Q2_seqs$All_count

test<-ks.test(L100Q_seqs$Prop,L100Q2_seqs$Prop)
test

df<-rbind(data.frame("Group"="WT","Val"=WT_seqs$Prop),data.frame("Group"="L100Q","Val"=L100Q_seqs$Prop),
          data.frame("Group"="Silent","Val"=HDR_seqs$Prop),data.frame("Group"="L100Q2","Val"=L100Q2_seqs$Prop))

df$Group<-factor(df$Group,levels=c("WT","Silent","L100Q","L100Q2"))
ggplot(df,aes(x = Val,color=Group))+
  stat_ecdf()+
  scale_color_manual(values = c("WT" =Parent_col, "L100Q" =L100_col,"Silent"=HDR_col,"L100Q2"=L100_col2))+
  #annotate("text", x = .85, y = .92, label = bquote(italic(P)<2.2e-16), color = "black", size = 2, family = "Arial") + 
  theme_classic()+
  labs(x="Proportion of C's",y="ecdf")+
  theme(legend.position = c(.8,.2),
        legend.key.size = unit(0.2, "cm"),
        legend.spacing.y = unit(-0.15, "cm"),
        axis.text=element_text(family="Arial",size=6, color="black"),
        axis.title = element_text(family="Arial",size=6, color="black"),
        legend.text = element_text(family="Arial",size=6, color="black"),
        legend.title = element_blank(),
        panel.background = element_blank(),
        plot.background = element_blank(), 
        panel.border = element_blank(),
        legend.background = element_blank())
ggsave("FigureS3/FigS2G.pdf",width=1.8,height=1.5)
```

#Fig S2H
```{r}
rm(list=ls())
pwn<-readRDS("Figure3/Data/eCLIP/PCBP1_PWMS.rds")
ggseqlogo::ggseqlogo(pwn[["PCBP1_HDR_Meta"]][[1]], method = 'bits')+
  theme_classic()+
  theme(axis.text = element_text(size=0),
        axis.title= element_text(size=0),
        panel.background = element_blank(),
        plot.background = element_blank(), 
        legend.background = element_blank(),
        plot.title = element_blank(),
        axis.ticks=element_blank())
ggsave("FigureS3/FigS2H-1.pdf",height =0.6 ,width = 1.2)

ggseqlogo::ggseqlogo(pwn[["PCBP1_F10_Meta"]][[1]], method = 'bits')+
  theme_classic()+
  theme(axis.text = element_text(size=0),
        axis.title= element_text(size=0),
        panel.background = element_blank(),
        plot.background = element_blank(), 
        legend.background = element_blank(),
        plot.title = element_blank(),
        axis.ticks=element_blank())
ggsave("FigureS3/FigS2H-2.pdf",height =0.6 ,width = 1.2)
```

#Fig S2I-1
```{r,fig.width=1, fig.height=1.5}
rm(list=ls())
load("Figure_Tables/RIP.RData")

WT<-WT[which(WT$gene_type=="up"),]
L100<-L100[which(L100$gene_type=="up"),]
L100$Group<-"Unique"
L100$Group[which(L100$Genes %in% WT$Genes)]<-"Common"

ggplot(data=L100,aes(y=log2FoldChange,x=Group))+
  geom_boxplot(color=L100_col, alpha=1,width=0.5,outlier.size = 0.5,fatten = 1,size=0.5)+
  theme_classic()+
  lims(y=c(0,15))+
  stat_compare_means(comparisons = list(c("Unique","Common")), label.y = c(13),label="p.signif",method = "wilcox.test")+
  theme(
    axis.text.x = element_text(family="Arial",color="black",size=6,angle=45,hjust=1), 
    axis.text.y = element_text(family="Arial",color="black",size=6),
    axis.title.x = element_blank(), 
    axis.title.y = element_text(family="Arial",color ="black", size=6),
    legend.position = "none",
    plot.background = element_blank(),
    panel.background = element_blank(),
    strip.background = element_blank(),
    strip.text.x = element_blank() )+
  xlab("")+
  ylab("L2FC (Mut / GFP)")+
  theme(legend.position = "none")
ggsave("FigureS3/FigS2I-1.pdf",height =1.5 ,width = 1)
```

#Fig S2I-2
```{r,fig.width=1.2, fig.height=1.4}
rm(list=ls())
load("Figure_Tables/RIP.RData")

WT<-WT[which(WT$gene_type=="up"),]
L100<-L100[which(L100$gene_type=="up"),]
WT$Group<-"Unique"
WT$Group[which(WT$Genes %in% L100$Genes)]<-"Common"

ggplot(data=WT,aes(y=log2FoldChange,x=Group))+
  geom_boxplot(color=Parent_col, alpha=1,width=0.5,outlier.size = 0.5,fatten = 1,size=0.5)+
  theme_classic()+
  lims(y=c(0,15))+
  stat_compare_means(comparisons = list(c("Unique","Common")), label.y = c(12),label="p.signif",method = "wilcox.test")+
  theme(
    axis.text.x = element_text(family="Arial",color="black",size=6,angle=45,hjust=1), 
    axis.text.y = element_text(family="Arial",color="black",size=6),
    axis.title.x = element_blank(), 
    axis.title.y = element_text(family="Arial",color ="black", size=6),
    legend.position = "none",
    plot.background = element_blank(),
    panel.background = element_blank(),
    strip.background = element_blank(),
    strip.text.x = element_blank() )+
  xlab("")+
  ylab("L2FC (WT / GFP)")+
  theme(legend.position = "none")
ggsave("FigureS3/FigS2I-2.pdf",height =1.5 ,width = 1)
```

#Fig S2J
```{r}
rm(list=ls())
L100<-read.table("FigureS3/RIP-HEK/Mut_vs_GFP_HEK.txt",header=T)
WT<-read.table("FigureS3/RIP-HEK/WT_vs_GFP_HEK.txt",header=T)

L100_sig<-L100[which(L100$gene_type=="up"),]
WT_sig<-WT[which(WT$gene_type=="up"),]

CE<-list("WT"=WT_sig$Genes,"L100Q"=L100_sig$Genes)
L100<-ggvenn::ggvenn(CE,fill_color=c(Parent_col,L100_col),set_name_size=3,show_percentage=F,text_size=2,fill_alpha=0.5,stroke_size=0.5)+
  coord_cartesian(ylim = c(-1.2, 1.5))+
  theme(legend.position = "none",
        panel.background = element_blank(),
        plot.background = element_blank(),
        panel.border = element_blank(),
        legend.background = element_blank(),
        axis.title = element_text(family="Arial",size=0, color="black"),
        axis.text=element_text(family="Arial",size=0, color="black"))
L100
ggsave("FigureS3/FigS2J.pdf",width=1.15,height=0.84)

```

#Fig S2K
```{r}
rm(list=ls())
L100<-read.table("FigureS3/RIP-HEK/Mut_vs_GFP_HEK.txt",header=T)
WT<-read.table("FigureS3/RIP-HEK/WT_vs_GFP_HEK.txt",header=T)

L100_sig<-L100[which(L100$gene_type=="up"),]
WT_sig<-WT[which(WT$gene_type=="up"),]

#Taking events that are bound in both
all_sig<-intersect(L100_sig$Genes,WT_sig$Genes)
df<-merge(L100[c("Genes","log2FoldChange")],WT[c("Genes","log2FoldChange")],by="Genes")
df<-df[which(df$Genes %in% all_sig),]
colnames(df)<-c("Genes","Mut","Wt")
df$Col<-Parent_col
df$Col[which(df$Mut>df$Wt)]<-L100_col

Up<-paste("L100Q>WT\n",as.character(length(which(df$Mut>df$Wt))),sep="")
Down<-paste("WT>L100Q\n",as.character(length(which(df$Wt>df$Mut))),sep="")

ggplot(df,aes(x = Wt,y = Mut,color=Col,fill = Col))+
  geom_point(shape = 21,alpha=0.5,size=0.5)+
  scale_fill_identity()+
  scale_colour_identity()+
  labs(x="L2FC (WT / GFP)",y="L2FC (Mut / GFP)")+
  theme_classic()+
  geom_abline(slope=1, intercept=0,linetype = "dashed")+
  annotate("text", x = 8.5, y = 2.5,label = Down, color = "black", size = 1.5, family = "Arial") + 
  annotate("text", x = 2.5, y = 8.5,label = Up, color = "black", size = 1.5, family = "Arial") + 
  lims(x=c(0,10),y=c(0,10))+
  theme(legend.position = "none",
        axis.text=element_text(family="Arial",size=6, color="black"),
        axis.title = element_text(family="Arial",size=6, color="black"),
        panel.background = element_blank(),
        plot.background = element_blank(), 
        panel.border = element_blank(),
        legend.background = element_blank())
ggsave("FigureS3/FigS2K.pdf",width=1.5,height=1.5)

```

#Fig S2L
```{r}
rm(list=ls())
L100_HEK<-read.table("FigureS3/RIP-HEK/Mut_vs_GFP_HEK.txt",header=T)
WT_HEK<-read.table("FigureS3/RIP-HEK/WT_vs_GFP_HEK.txt",header=T)

load("Figure_Tables/RIP.RData")

#Getting sig
L100_sig<-L100[which(L100$gene_type=="up"),]
WT_sig<-WT[which(WT$gene_type=="up"),]

L100_HEK_sig<-L100_HEK[which(L100_HEK$gene_type=="up"),]
WT_HEK_sig<-WT_HEK[which(WT_HEK$gene_type=="up"),]

#WT Overlap
CE<-list("C2BBe1"=WT_sig$Genes,"HEK"=WT_HEK_sig$Genes)
L100<-ggvenn::ggvenn(CE,fill_color=c("white","white"),stroke_color=c(Parent_col),set_name_size=3,show_percentage=F,text_size=2,fill_alpha=0.5,stroke_size=0.5)+
  coord_cartesian(ylim = c(-1.2, 1.5))+
  theme(legend.position = "none",
        panel.background = element_blank(),
        plot.background = element_blank(),
        panel.border = element_blank(),
        legend.background = element_blank(),
        axis.title = element_text(family="Arial",size=0, color="black"),
        axis.text=element_text(family="Arial",size=0, color="black"))
L100
ggsave("FigureS3/FigS2L-1.pdf",width=1.15,height=0.84)


#L100Q Overlap
CE<-list("C2BBe1"=L100_sig$Genes,"HEK"=L100_HEK_sig$Genes)
L100<-ggvenn::ggvenn(CE,fill_color=c("white","white"),stroke_color=c(L100_col),set_name_size=3,show_percentage=F,text_size=2,fill_alpha=0.5,stroke_size=0.5)+
  coord_cartesian(ylim = c(-1.2, 1.5))+
  theme(legend.position = "none",
        panel.background = element_blank(),
        plot.background = element_blank(),
        panel.border = element_blank(),
        legend.background = element_blank(),
        axis.title = element_text(family="Arial",size=0, color="black"),
        axis.text=element_text(family="Arial",size=0, color="black"))
L100
ggsave("FigureS3/FigS2L-2.pdf",width=1.15,height=0.84)


phyper(1058-1,1421,17044-1421,3023,lower.tail=F,exact=T)

```

#Fig S2M
```{r}
rm(list=ls())
L100_HEK<-read.table("FigureS3/RIP-HEK/Mut_vs_GFP_HEK.txt",header=T)

load("Figure_Tables/RIP.RData")

#Getting sig
L100_sig<-L100[which(L100$gene_type=="up"),]
L100_HEK_sig<-L100_HEK[which(L100_HEK$gene_type=="up"),]

l100_in<-intersect(L100_sig$Genes,L100_HEK_sig$Genes)
bound<-c(l100_in)

Go_up<-enrichGO(gene          = bound,
                OrgDb         = org.Hs.eg.db,
                keyType       = 'ENSEMBL',
                ont           = "BP",
                universe=L100_HEK$Genes,
                pAdjustMethod = "BH",
                pvalueCutoff  = 0.05,
                qvalueCutoff  = 0.05)


Go_up@result<-Go_up@result[which(Go_up@result$ID %in% c("GO:0007015","GO:0034333","GO:2001243","GO:0051495","GO:0043149")),]
dotplot(Go_up,font.size = 8)+
  scale_size_area(max_size = 3)+
  theme_classic()+
  theme(legend.position = "right",
        axis.text=element_text(family="Arial",size=8, color="black"),
        axis.text.x=element_text(family="Arial",size=8, color="black"),
        axis.title = element_text(family="Arial",size=8, color="black"),
        panel.background = element_blank(),
        plot.background = element_blank(), 
        legend.background = element_blank(),
        legend.key.size = unit(0.3, "cm"))
ggsave("FigureS3/FigS2M.pdf",width=4,height=2)

```


#Figure S3

#S3A
```{r}
rm(list=ls())
df<-read.csv("FigureS4/KH1-2_localization/txt_localizationKH12/KH12_localization.csv",header=T,sep=",")
df_melt<-reshape2::melt(df)

test <- compare_means(value ~ variable,comparisons = c("WT","L100Q"), p.adjust.method = "fdr", method='t.test', data = df_melt)
test<-test %>% mutate(y.position =0.95)

ggplot(df_melt,aes(x=variable,y=value))+
  geom_boxplot(alpha=0.5)+
  geom_jitter(aes(color=variable),position=position_jitter(0.2),size=1)+
  theme_classic()+
  stat_pvalue_manual(test, label = "p.signif",xmin="group1",xmax="group2",size = 2)+
  lims(y=c(0,1))+
  scale_color_manual(values = c("L100Q"=L100_col,"WT"=Parent_col))+
  scale_fill_manual(values = c("L100Q"=L100_col,"WT"=Parent_col))+
  stat_compare_means(comparisons = list(c("L100Q","WT")), label.y = c(2.3),label="p.signif",method = "wilcox.test")+
  labs(x="",y="Fluorescence \n (Nuclear/Perinuclear)")+
  theme(legend.position = "none",
        axis.text=element_text(family="Arial",size=6, color="black"),
        axis.title = element_text(family="Arial",size=6, color="black"),
        legend.text = element_text(family="Arial",size=6, color="black"),
        axis.title.x=element_blank(),
        panel.background = element_blank(),
        plot.title = element_blank(),
        plot.background = element_blank(), 
        panel.border = element_blank(),
        legend.background = element_blank(),
        legend.title=element_blank(),
        legend.key.width= unit(0.4, 'cm'),
        legend.key.height= unit(0.4, 'cm'))

ggsave("FigureS4/FigS4A-box.pdf",height = 1.5,width = 1.25)
```

#S3B
```{r}
sample<-c("A","A","A")
seq<-c("CAG","CTG","Other")
occurance<-c(3287,3922,22)

df<-data.frame(sample,seq,occurance)
df$Class<-c("L100Q","WT","Other")
df$sample<-"L102Q"

ggplot(df, aes(x=sample, y=occurance, fill=Class)) + 
  geom_bar(stat="identity", color="black",width=0.5,alpha=0.9,position="fill") +
  theme_classic()+
  scale_fill_manual(values = c("WT"=Parent_col,"L100Q"=L100_col,"Other"="gray"))+
  labs(x="Condition",y="Prop of Allele")+
  theme(legend.position = "none",
        axis.text=element_text(family="Arial",size=6, color="black"),
        axis.text.y=element_text(family="Arial",size=6, color="black"),
        axis.title.x = element_blank(),
        axis.title.y=element_text(family="Arial",size=6, color="black"),
        strip.text.x = element_text(family="Arial",size=6, color="black"),
        panel.background = element_blank(),
        plot.background = element_blank(), 
        panel.border = element_blank(),
        legend.background = element_blank())

ggsave("FigureS4/FigS4B-L102Q.pdf",height = 1.5,width = 1)
```

#S3C
```{r Fig3A-1, message=F, warning=F,echo=F,fig.width=6, fig.height=3.5}
rm(list=ls())
prot<-read.csv("Figure5/Data/20250216_DominguezLab_IP_Imputed_Enrichment_Dataframe.csv",header=T)
prot<-prot[c("PG.Genes",colnames(prot)[grepl("Pvalue|log2FC|Mean|Count",colnames(prot))])]
prot<-prot[which(prot$PG.Genes !=""),]

wt_unique<-read.table("Figure5/Data/MS-IP_WT_Unique.txt",header=T)
go_wt<-enrichGO(gene          = wt_unique$Gene,
                OrgDb         = org.Hs.eg.db,
                keyType       = 'SYMBOL',
                ont           = "BP",
             universe=prot$PG.Genes,
                pAdjustMethod = "BH",
                pvalueCutoff  = 0.05,
                qvalueCutoff  = 0.05)
dotplot(go_wt)

go_wt@result<-go_wt@result[which(go_wt@result$ID %in% c("GO:0006396","GO:0042254","GO:0008380","GO:0000245","GO:0007049",
                                                        "GO:0042273","GO:0000398","GO:0000398","GO:0034470","GO:0022613")),]
plot<-dotplot(go_wt,font.size = 8)+
  lims(x=c(0,0.5))+
  theme_classic()+
  theme(legend.position ="right",
        axis.text=element_text(family="Arial",size=12, color="black"),
        legend.text=element_text(family="Arial",size=12, color="black"),
        axis.title= element_text(family="Arial",size=12, color="black"),
        axis.title.x= element_blank(),
        panel.background = element_blank(),
        legend.title=element_text(family="Arial",size=12, color="black"),
        plot.background = element_blank(), 
        panel.border = element_blank(),
        legend.background = element_blank(),
        legend.key.size = unit(0.5, 'cm'))
plot
ggsave("FigureS4/WT_unique_GO.pdf",plot,width=6, height=3.5)

```

#S3D
```{r Fig3A-1, message=F, warning=F,echo=F,fig.width=6, fig.height=3.5}
rm(list=ls())
prot<-read.csv("Figure5/Data/20250216_DominguezLab_IP_Imputed_Enrichment_Dataframe.csv",header=T)
prot<-prot[c("PG.Genes",colnames(prot)[grepl("Pvalue|log2FC|Mean|Count",colnames(prot))])]
prot<-prot[which(prot$PG.Genes !=""),]

l100_unique<-read.table("Figure5/Data/MS-IP_L100Q_Unique.txt",header=T)
go<-enrichGO(gene          = l100_unique$Gene,
                OrgDb         = org.Hs.eg.db,
                keyType       = 'SYMBOL',
                ont           = "BP",
             universe=prot$PG.Genes,
                pAdjustMethod = "BH",
                pvalueCutoff  = 0.05,
                qvalueCutoff  = 0.05)
go@result<-go@result[which(go@result$ID %in% c("GO:0030029","GO:0007010","GO:0016477","GO:0007155","GO:0030834",
                                               "GO:0030050","GO:0071346","GO:0031623")),]
plot<-dotplot(go,font.size = 8)+
  lims(x=c(0,0.5))+
  theme_classic()+
  theme(legend.position ="right",
        axis.text=element_text(family="Arial",size=12, color="black"),
        legend.text=element_text(family="Arial",size=12, color="black"),
        axis.title= element_text(family="Arial",size=12, color="black"),
        axis.title.x= element_blank(),
        panel.background = element_blank(),
        legend.title=element_text(family="Arial",size=12, color="black"),
        plot.background = element_blank(), 
        panel.border = element_blank(),
        legend.background = element_blank(),
        legend.key.size = unit(0.5, 'cm'))
plot

m<-go@result
m<-m[which(m$ID=="GO:0030029"),]
m_sub<-m$geneID
m_sub<-strsplit(m_sub,"/")[[1]]

l_m<-l100_unique[which(l100_unique$Gene %in% m_sub),]
write.table(l_m,"~/Desktop/Actin_related_genes.txt",sep="\t",col.names = T,row.names = F,quote = F)

ggsave("FigureS4/L100Q_unique_GO.pdf",plot,width=6, height=3.5) 

```

#S3E
```{r Fig3A-1, message=F, warning=F,echo=F,fig.width=1, fig.height=1.5}
rm(list=ls())
HNRNPK_L100Q<-read.table("Figure5/Data/HNRNPK_L100Q.bed",sep="\t")
HNRNPK_WT<-read.table("Figure5/Data/HNRNPK_WT.bed",sep="\t")
L100Q<-read.table("Figure3/Data/eCLIP/Collapsed/PCBP1_l100_Low_Meta.bed",sep="\t")
WT<-read.table("Figure3/Data/eCLIP/Collapsed/PCBP1_WT_Low_Meta.bed",sep="\t")

HNRNPK_L100Q_gr<-makeGRangesFromDataFrame(HNRNPK_L100Q,seqnames.field = "V1",start.field = "V2",end.field = "V3",strand.field = "V6",keep.extra.columns = T)
HNRNPK_WT_gr<-makeGRangesFromDataFrame(HNRNPK_WT,seqnames.field = "V1",start.field = "V2",end.field = "V3",strand.field = "V6",keep.extra.columns = T)
L100Q_gr<-makeGRangesFromDataFrame(L100Q,seqnames.field = "V1",start.field = "V2",end.field = "V3",strand.field = "V6",keep.extra.columns = T)
WT_gr<-makeGRangesFromDataFrame(WT,seqnames.field = "V1",start.field = "V2",end.field = "V3",strand.field = "V6",keep.extra.columns = T)

wt_ov<-length(unique(queryHits(findOverlaps(HNRNPK_WT_gr,WT_gr))))/length(HNRNPK_WT_gr)
l100_ov<-length(unique(queryHits(findOverlaps(HNRNPK_L100Q_gr,L100Q_gr))))/length(HNRNPK_L100Q_gr)

df<-data.frame("Group"=c("WT","L100Q"),"Overlap"=c(wt_ov*100,l100_ov*100))
df$Group<-factor(df$Group,levels=c("WT","L100Q"))

ggplot(df, aes(x = Group, y = Overlap,fill=Group)) +
  geom_bar(stat = "identity",width=0.5,color="black")+
  theme_classic()+
  scale_fill_manual(values = c("L100Q"=L100_col,"WT"=Parent_col))+
  labs(y=c("HNRNPK Sites Overlaped (%)"))+
  theme(legend.position = "none",
        axis.text.x=element_text(family="Arial",size=6, color="black"),
        axis.text.y=element_text(family="Arial",size=6, color="black"),
        axis.title.y = element_text(family="Arial",size=6, color="black"),
        axis.title.x =  element_blank(),
        panel.background = element_blank(),
        plot.background = element_blank(), 
        legend.background = element_blank())
ggsave("FigureS4/HNRNPK_ov.pdf",width = 1,height=1.5)
```

#S3F
```{r, fig.width=2, fig.height=1.5}
rm(list=ls())
HNRNPK_L100Q<-read.table("Figure5/Data/HNRNPK_L100Q.bed",sep="\t")
HNRNPK_WT<-read.table("Figure5/Data/HNRNPK_WT.bed",sep="\t")
L100Q<-read.table("Figure3/Data/eCLIP/Collapsed/PCBP1_l100_Low_Meta.bed",sep="\t")

HNRNPK_L100Q_gr<-makeGRangesFromDataFrame(HNRNPK_L100Q,seqnames.field = "V1",start.field = "V2",end.field = "V3",strand.field = "V6",keep.extra.columns = T)
HNRNPK_WT_gr<-makeGRangesFromDataFrame(HNRNPK_WT,seqnames.field = "V1",start.field = "V2",end.field = "V3",strand.field = "V6",keep.extra.columns = T)
L100Q_gr<-makeGRangesFromDataFrame(L100Q,seqnames.field = "V1",start.field = "V2",end.field = "V3",strand.field = "V6",keep.extra.columns = T)

#overlapping ranges between WT and L100Q
ov<-findOverlaps(HNRNPK_L100Q_gr,HNRNPK_WT_gr)
HNRNPK_L100Q_gr_ov<-HNRNPK_L100Q_gr[unique(queryHits(ov))]
HNRNPK_WT_gr_ov<-HNRNPK_WT_gr[unique(subjectHits(ov))]


#overlaping with PCBP1
wt_pcbp1<-findOverlaps(HNRNPK_WT_gr_ov,L100Q_gr)
l100q_pcbp1<-findOverlaps(HNRNPK_L100Q_gr_ov,L100Q_gr)

HNRNPK_WT_gr_ov_PCBP1<-HNRNPK_WT_gr_ov[unique(queryHits(wt_pcbp1))] %>% data.frame()
HNRNPK_WT_gr_no_PCBP1<-HNRNPK_WT_gr_ov[-unique(queryHits(wt_pcbp1))] %>% data.frame()

HNRNPK_L100Q_gr_ov_PCBP1<-HNRNPK_L100Q_gr_ov[unique(queryHits(l100q_pcbp1))] %>% data.frame()
HNRNPK_L100Q_gr_no_PCBP1<-HNRNPK_L100Q_gr_ov[-unique(queryHits(l100q_pcbp1))] %>% data.frame()

ov_test<-ks.test(HNRNPK_WT_gr_ov_PCBP1$V7,HNRNPK_L100Q_gr_ov_PCBP1$V7,exact=T)
no_test<-ks.test(HNRNPK_WT_gr_no_PCBP1$V7,HNRNPK_L100Q_gr_no_PCBP1$V7,exact=T)
p.adjust(c(ov_test$p.value,no_test$p.value),method="fdr")

#overlaping df
ov_df<-rbind(data.frame("Group"="WT","Val"=HNRNPK_WT_gr_ov_PCBP1$V7),data.frame("Group"="L100Q","Val"=HNRNPK_L100Q_gr_ov_PCBP1$V7))
ov_df$Cond<-"Ov with PCBP1"

no_df<-rbind(data.frame("Group"="WT","Val"=HNRNPK_WT_gr_no_PCBP1$V7),data.frame("Group"="L100Q","Val"=HNRNPK_L100Q_gr_no_PCBP1$V7))
no_df$Cond<-"Unique"

df<-rbind(ov_df)
ggplot(df,aes(x = Val,color=Group))+
  stat_ecdf()+
  scale_color_manual(values = c("WT" =Parent_col, "L100Q" =L100_col))+
  #annotate("text", x = 8, y = .92, label = bquote(italic(P)<2.2e-16), color = "black", size = 2, family = "Arial") + 
  theme_classic()+
  labs(x="Peak Enrichment",y="ecdf")+
  theme(legend.position = c(.8,.1),
        legend.key.size = unit(0.2, "cm"),
        legend.spacing.y = unit(-0.15, "cm"),
        axis.text=element_text(family="Arial",size=6, color="black"),
        axis.title = element_text(family="Arial",size=6, color="black"),
        legend.text = element_text(family="Arial",size=6, color="black"),
        legend.title = element_blank(),
        panel.background = element_blank(),
        plot.background = element_blank(), 
        panel.border = element_blank(),
        legend.background = element_blank())
ggsave("FigureS4/HNRNPK_ov_LFC.pdf",width = 2,height=1.5)
```

#S3G
```{r, fig.width=3, fig.height=2}
rm(list=ls())
HNRNPK_L100Q<-read.table("Figure5/Data/HNRNPK_L100Q.bed",sep="\t")
HNRNPK_WT<-read.table("Figure5/Data/HNRNPK_WT.bed",sep="\t")
L100Q<-read.table("Figure3/Data/eCLIP/Collapsed/PCBP1_l100_Low_Meta.bed",sep="\t")

HNRNPK_L100Q_gr<-makeGRangesFromDataFrame(HNRNPK_L100Q,seqnames.field = "V1",start.field = "V2",end.field = "V3",strand.field = "V6",keep.extra.columns = T)
HNRNPK_WT_gr<-makeGRangesFromDataFrame(HNRNPK_WT,seqnames.field = "V1",start.field = "V2",end.field = "V3",strand.field = "V6",keep.extra.columns = T)
L100Q_gr<-makeGRangesFromDataFrame(L100Q,seqnames.field = "V1",start.field = "V2",end.field = "V3",strand.field = "V6",keep.extra.columns = T)

#overlapping ranges between WT and L100Q
ov<-findOverlaps(HNRNPK_L100Q_gr,HNRNPK_WT_gr)
HNRNPK_L100Q_gr_ov<-HNRNPK_L100Q_gr[unique(queryHits(ov))]
HNRNPK_WT_gr_ov<-HNRNPK_WT_gr[unique(subjectHits(ov))]


#overlaping with PCBP1
wt_pcbp1<-findOverlaps(HNRNPK_WT_gr_ov,L100Q_gr)
l100q_pcbp1<-findOverlaps(HNRNPK_L100Q_gr_ov,L100Q_gr)

HNRNPK_WT_gr_ov_PCBP1<-HNRNPK_WT_gr_ov[unique(queryHits(wt_pcbp1))] %>% data.frame()
HNRNPK_WT_gr_no_PCBP1<-HNRNPK_WT_gr_ov[-unique(queryHits(wt_pcbp1))] %>% data.frame()

HNRNPK_L100Q_gr_ov_PCBP1<-HNRNPK_L100Q_gr_ov[unique(queryHits(l100q_pcbp1))] %>% data.frame()
HNRNPK_L100Q_gr_no_PCBP1<-HNRNPK_L100Q_gr_ov[-unique(queryHits(l100q_pcbp1))] %>% data.frame()

HNRNPK_WT_gr_ov_PCBP1$Region<-sapply(HNRNPK_WT_gr_ov_PCBP1$V4,function(x){strsplit(x,"_")[[1]][2]})
HNRNPK_WT_gr_no_PCBP1$Region<-sapply(HNRNPK_WT_gr_no_PCBP1$V4,function(x){strsplit(x,"_")[[1]][2]})
HNRNPK_L100Q_gr_ov_PCBP1$Region<-sapply(HNRNPK_L100Q_gr_ov_PCBP1$V4,function(x){strsplit(x,"_")[[1]][2]})
HNRNPK_L100Q_gr_no_PCBP1$Region<-sapply(HNRNPK_L100Q_gr_no_PCBP1$V4,function(x){strsplit(x,"_")[[1]][2]})

#overlaping df
ov_df<-rbind(data.frame("Group"="WT","Val"=HNRNPK_WT_gr_ov_PCBP1$V7,"Region"=HNRNPK_WT_gr_ov_PCBP1$Region),
             data.frame("Group"="L100Q","Val"=HNRNPK_L100Q_gr_ov_PCBP1$V7,"Region"=HNRNPK_L100Q_gr_ov_PCBP1$Region))
ov_df$Region[which(ov_df$Region=="CDSFull")]<-"CDS"
ov_df<-ov_df[which(ov_df$Region %in% c("CDS","SS3","SS5","UTR3","UTR5","Intron")),]


cds_test<-ks.test(ov_df$Val[which(ov_df$Group=="WT" & ov_df$Region=="CDS")],ov_df$Val[which(ov_df$Group=="L100Q" & ov_df$Region=="CDS")],exact=T)
ss3_test<-ks.test(ov_df$Val[which(ov_df$Group=="WT" & ov_df$Region=="SS3")],ov_df$Val[which(ov_df$Group=="L100Q" & ov_df$Region=="SS3")],exact=T)
ss5_test<-ks.test(ov_df$Val[which(ov_df$Group=="WT" & ov_df$Region=="SS5")],ov_df$Val[which(ov_df$Group=="L100Q" & ov_df$Region=="SS5")],exact=T)
utr3_test<-ks.test(ov_df$Val[which(ov_df$Group=="WT" & ov_df$Region=="UTR3")],ov_df$Val[which(ov_df$Group=="L100Q" & ov_df$Region=="UTR3")],exact=T)
utr5_test<-ks.test(ov_df$Val[which(ov_df$Group=="WT" & ov_df$Region=="UTR5")],ov_df$Val[which(ov_df$Group=="L100Q" & ov_df$Region=="UTR5")],exact=T)
intron_test<-ks.test(ov_df$Val[which(ov_df$Group=="WT" & ov_df$Region=="Intron")],ov_df$Val[which(ov_df$Group=="L100Q" & ov_df$Region=="Intron")],exact=T)

test_df<-data.frame("Group"=c("CDS","Intron","SS3","SS5","UTR3","UTR5"),
                    "P_val"=c(cds_test$p.value,intron_test$p.value,ss3_test$p.value,ss5_test$p.value,utr3_test$p.value,utr5_test$p.value))
test_df$FDR<-p.adjust(test_df$P_val)
test_df$sigif<-sapply(test_df$FDR,signif,digits=3)
colnames(test_df)[1]<-"Region"
test_df$Label<-sapply(test_df$sigif,function(x){bquote(italic(P)==.(x))})

ggplot(ov_df,aes(x = Val,color=Group))+
  stat_ecdf()+
  facet_wrap(~Region)+
  scale_color_manual(values = c("WT" =Parent_col, "L100Q" =L100_col))+
  geom_text(data=test_df,mapping=aes(x=6.5,y=0.2,label=Label,group = Region),inherit.aes = FALSE,vjust = 1.2, colour = "black",family="Arial",size=2,parse=T)+
  theme_classic()+
  labs(x="Peak Enrichment",y="ecdf")+
  theme(legend.position = c("none"),
        legend.key.size = unit(0.2, "cm"),
        legend.spacing.y = unit(-0.15, "cm"),
        axis.text=element_text(family="Arial",size=6, color="black"),
        axis.title = element_text(family="Arial",size=6, color="black"),
        legend.text = element_text(family="Arial",size=6, color="black"),
        legend.title = element_blank(),
        strip.text = element_text(size = 6,margin = margin(2, 2, 2, 2)),
        panel.background = element_blank(),
        plot.background = element_blank(), 
        panel.border = element_blank(),
        legend.background = element_blank())
ggsave("FigureS4/HNRNPK_ov_LFC_y_region.pdf",width = 3,height=2)
```


#Figure S4

#Figure S4A
```{r}
rm(list=ls())

WT<-read.table("Figure3/Data/eCLIP/IDR/GG83_GG84_reprod_Meta.bed",sep = "\t")
L100Q<-read.table("Figure3/Data/eCLIP/IDR/GG87_GG88_reprod_Meta.bed",sep = "\t")
L100Q2<-read.table("Figure3/Data/eCLIP/IDR/GG93_GG94_reprod_Meta.bed",sep = "\t")
HDR<-read.table("Figure3/Data/eCLIP/IDR/GG91_GG92_reprod_Meta.bed",sep = "\t")

WT$Region<-sapply(WT$V4,function(x){strsplit(x,"_")[[1]][2]})
L100Q$Region<-sapply(L100Q$V4,function(x){strsplit(x,"_")[[1]][2]})
HDR$Region<-sapply(HDR$V4,function(x){strsplit(x,"_")[[1]][2]})
L100Q2$Region<-sapply(L100Q2$V4,function(x){strsplit(x,"_")[[1]][2]})

WT$groups<-"WT"
L100Q$groups<-"L100Q-1"
HDR$groups<-"Silent"
L100Q2$groups<-"L100Q-2"

df<-rbind(WT,L100Q,HDR,L100Q2)

df$Region[which(df$Region=="CDSFull")]<-"CDS"
comb<-df[c("groups","Region")] %>% gather(groups, Region) %>% dplyr::count(groups, Region)
comb$Region<-factor(comb$Region,levels=c("CDS","UTR3","UTR5","SS5","SS3","Intron","NC","Other"))
comb$groups<-factor(comb$groups,levels=c("WT","Silent","L100Q-1","L100Q-2"))

cls<-c("CDS"="#5AAC56","Intron"="#4356A1","NC"="#EFB143","Other"="gray","SS3"="#C7639C","SS5"="#7A5DA0","UTR3"="#42824F","UTR5"="#98C357")

g<-ggplot(comb,aes(x=groups,y=n,fill=Region))+
  geom_bar(position = "fill",stat = "identity",width=.8,size=1) +
  scale_y_continuous(labels = scales::percent_format())+
  scale_fill_manual(values =cls)+
  theme_classic()+
  labs(x="",y="eCLIP Peaks")+
  theme(legend.position = "none",
        axis.text.y=element_text(family="Arial",size=6, color="black"),
        axis.text.x=element_text(family="Arial",size=6, color="black"),
        axis.title = element_text(family="Arial",size=6, color="black"),
        legend.text = element_text(family="Arial",size=6, color="black"),
        panel.background = element_blank(),
        legend.title = element_blank(),
        plot.background = element_blank(), 
        panel.border = element_blank(),
        legend.background = element_blank(),
        legend.key.height= unit(0.5, 'cm'),
        legend.key.width= unit(0.5, 'cm'))
g
ggsave("FigureS5/FigS5A_Combined.pdf",width=2,height=1.5)

g2<-g+theme(legend.position = "left",legend.key.height= unit(0.5, 'cm'),legend.key.width= unit(0.5, 'cm'))
legend <- ggpubr::get_legend(g2)
ggsave("FigureS5/FigS5A-Leg.pdf",legend,width=1,height=2)

```

#Figure S4B
```{r, fig.width=1.2, fig.height=1.5}
rm(list=ls())
load("~/Desktop/Dominguez_Lab/PCBP1_FINAL/RNA-Seq/rMATS/HCT_rMATS.RData")

L100Q<-HCT$Parent_F10
L100Q<-lapply(L100Q, function(x){y<-x[which(x$FDR<0.05 & x$PValue<0.05 & abs(x$IncLevelDifference)>0.1 & 
                                                x$Total_Count_1>50 & x$Total_Count_2>50),];return(y)})
df<-data.frame(t(data.frame((lapply(L100Q, nrow)))))
df$Event<-rownames(df)
colnames(df)<-c("Count","Event")
df$Class<-"L100Q"
df$Event<-factor(df$Event,levels=c("SE","RI","MXE","A3SS","A5SS"))
df$Xpos<-cumsum(df$Count[5:1])[5:1]/sum(df$Count)
df$Label<-paste(df$Event,"=",df$Count,sep="")

ggplot(df,aes(x=Class,y=Count,fill=Event))+
  geom_bar(stat="identity", position="fill",alpha=0.75)+
  labs(x="",y="# of Sig. Events")+
  theme_classic()+
  geom_text(aes(y = Xpos, label = Count), vjust = 1.2, colour = "black",family="Arial",size=2)+
  #geom_text(aes(y = Xpos, label = Event),vjust = 1.2, colour = "black",family="Arial",size=2)+
  scale_fill_manual(values = c("SE"="#5770FF","RI"="#690002","MXE"="#D9C2EA", "A3SS"="#FB8808","A5SS"="#89AF84"))+
  theme(legend.position = "none",
        axis.text=element_blank(),
        axis.title = element_blank(),
        legend.text = element_text(family="Arial",size=8, color="black"),
        panel.background = element_blank(),
        legend.title = element_blank(),
        plot.background = element_blank(), 
        panel.border = element_blank(),
        legend.background = element_blank(),
        legend.key.height= unit(0.5, 'cm'),
        legend.key.width= unit(0.5, 'cm'),
        axis.ticks= element_blank(),
        line = element_blank())
ggsave("FigureS5/FigS5B.pdf",width=0.5,height=1.5)
```

#Figure S4C
```{r, fig.width=1.5, fig.height=1.5}
load("~/Desktop/Dominguez_Lab/PCBP1_FINAL/RNA-Seq/rMATS/HCT_rMATS.RData")

L100Q<-HCT$Parent_F10$SE
L100Q_sub<-L100Q[which(L100Q$Total_Count_1>50 & L100Q$Total_Count_2>50),]
L100Q_sub$Group<-"ns"
L100Q_sub$Group[which(L100Q_sub$PValue<0.05 & L100Q_sub$FDR<0.05 & L100Q_sub$IncLevelDifference>0.1)]<-"up"
L100Q_sub$Group[which(L100Q_sub$PValue<0.05 & L100Q_sub$FDR<0.05 & L100Q_sub$IncLevelDifference<(-0.1))]<-"down"

##Volcano Plot
cols <- c("up" = Parent_col, "down" = L100_col2, "ns" = "grey") 
sizes <- c("up" = 0.75, "down" = 0.75, "ns" = 0.25) 
alphas <- c("up" = 0.7, "down" = 0.7, "ns" = 0.5)

Up_genes<-as.character(length(which(L100Q_sub$Group=="up")))
Down_genes<-as.character(length(which(L100Q_sub$Group=="down")))

volcano<-L100Q_sub %>%
  ggplot(aes(x = IncLevelDifference,
             y = -log10(FDR),
             fill = Group,
             color=Group,
             size = Group,
             alpha =Group)) + 
  geom_point(shape = 21) +
  geom_hline(yintercept = -log10(0.05),
             linetype = "dashed") + 
  geom_vline(xintercept = c(-0.1,0.1),
             linetype = "dashed")+
  scale_fill_manual(values = cols) + # Modify point colour
  scale_color_manual(values = cols) + # Modify point colour
  scale_size_manual(values = sizes) + # Modify point size
  scale_alpha_manual(values = alphas) + # Modify point transparency
  scale_x_continuous(breaks = c(-0.4,-0.2,0,0.2,0.4),       
                     limits = c(-0.5, 0.5))+
  lims(y=c(0,40))+
  labs(x=bquote(Delta~PSI(Parent-L100Q_2)))+
  theme_classic()+
  geom_text(x=0.3, y=30, label=paste("Skipped \n",Up_genes,sep=""),color="black",size=2,family="Arial")+
  geom_text(x=-0.3, y=30, label=paste("Retained \n",Down_genes,sep=""),color="black",size=2,family="Arial")+
  theme(legend.position = "none",
        axis.text=element_text(family="Arial",size=6, color="black"),
        axis.title = element_text(family="Arial",size=6, color="black"),
        panel.background = element_blank(),
        plot.background = element_blank(), 
        panel.border = element_blank(),
        legend.background = element_blank())
volcano
ggsave("FigureS5/FigS5C.png",width=1.5,height=1.5)

```

#Figure S4D
```{r}
rm(list=ls())

load("~/Desktop/Dominguez_Lab/PCBP1_FINAL/RNA-Seq/rMATS/HCT_rMATS.RData")

HCT_L100Q2<-HCT$Parent_F10$SE
HCT_L100Q<-HCT$Parent_L100Q$SE

HCT_L100Q2<-HCT_L100Q2[which(HCT_L100Q2$FDR<0.05 & HCT_L100Q2$PValue<0.05 & abs(HCT_L100Q2$IncLevelDifference)>0.1
                     & HCT_L100Q2$Total_Count_1>50 & HCT_L100Q2$Total_Count_2>50),]
HCT_L100Q<-HCT_L100Q[which(HCT_L100Q$FDR<0.05 & HCT_L100Q$PValue<0.05 & abs(HCT_L100Q$IncLevelDifference)>0.1
                           & HCT_L100Q$Total_Count_1>50 & HCT_L100Q$Total_Count_2>50),]

HCT_L100Q2$Identifier<-paste(HCT_L100Q2$chr,"_",HCT_L100Q2$exonStart_0base,"-",HCT_L100Q2$exonEnd,"_",HCT_L100Q2$upstreamES,"-",HCT_L100Q2$upstreamEE,"_",
                         HCT_L100Q2$downstreamES,"-",HCT_L100Q2$downstreamEE,"_",HCT_L100Q2$strand,"_",HCT_L100Q2$GeneID,"_",HCT_L100Q2$geneSymbol,sep="")
HCT_L100Q$Identifier<-paste(HCT_L100Q$chr,"_",HCT_L100Q$exonStart_0base,"-",HCT_L100Q$exonEnd,"_",HCT_L100Q$upstreamES,"-",
                            HCT_L100Q$upstreamEE,"_",HCT_L100Q$downstreamES,"-",HCT_L100Q$downstreamEE,"_",HCT_L100Q$strand,"_",HCT_L100Q$GeneID,"_",HCT_L100Q$geneSymbol,sep="")

SE<-list("L100Q"=HCT_L100Q$Identifier,"L100Q_2"=HCT_L100Q2$Identifier)

v<-ggvenn::ggvenn(SE,fill_color=c(L100_col,L100_col2),set_name_size=3,show_percentage=F,text_size=2.5,fill_alpha=0.6,stroke_size=0.5)+
  coord_cartesian(ylim = c(-1.2, 1.5))+
  theme(legend.position = "none",
        panel.background = element_blank(), 
        plot.background = element_blank(), 
        panel.border = element_blank(),
        legend.background = element_blank(),
        axis.title = element_text(family="Arial",size=0, color="black"),
        axis.text=element_text(family="Arial",size=0, color="black"),
        textt=element_text(family="Arial", size=0,color="black"))
v
ggsave("FigureS5/FigS5D.pdf",width=1.15,height=0.84)

```

#C-rich introns
```{r,fig.width=4,fig.height=1.5}
rm(list=ls())
load("~/Desktop/Dominguez_Lab/PCBP1_FINAL/RNA-Seq/rMATS/HCT_rMATS.RData")

L100Q1<-HCT$Parent_L100Q$SE
F10<-HCT$Parent_F10$SE
KO<-HCT$Parent_KO$SE

#skipped
L100Q1_skipped<-L100Q1[which(L100Q1$PValue<0.05 & L100Q1$FDR<0.05 & L100Q1$Total_Count_1>50 & 
                         L100Q1$Total_Count_2>50 & L100Q1$IncLevelDifference>0.1),]
F10_skipped<-F10[which(F10$PValue<0.05 & F10$FDR<0.05 & F10$Total_Count_1>50 & 
                         F10$Total_Count_2>50 & F10$IncLevelDifference>0.1),]
KO_skipped<-KO[which(KO$PValue<0.05 & KO$FDR<0.05 & KO$Total_Count_1>50 & 
                         KO$Total_Count_2>50 & KO$IncLevelDifference>0.1),]

#retained
L100Q1_retained<-L100Q1[which(L100Q1$PValue<0.05 & L100Q1$FDR<0.05 & L100Q1$Total_Count_1>50 & 
                         L100Q1$Total_Count_2>50 & L100Q1$IncLevelDifference<(-0.1)),]
F10_retained<-F10[which(F10$PValue<0.05 & F10$FDR<0.05 & F10$Total_Count_1>50 & 
                         F10$Total_Count_2>50 & F10$IncLevelDifference<(-0.1)),]
KO_retained<-KO[which(KO$PValue<0.05 & KO$FDR<0.05 & KO$Total_Count_1>50 & 
                         KO$Total_Count_2>50 & KO$IncLevelDifference<(-0.1)),]

#unchanged
L100Q1_control<-L100Q1[which(L100Q1$PValue<0.9 & L100Q1$FDR>0.9 & L100Q1$Total_Count_1>50 & 
                         L100Q1$Total_Count_2>50 & abs(L100Q1$IncLevelDifference)<0.001),]
F10_control<-F10[which(F10$PValue<0.9 & F10$FDR>0.9 & F10$Total_Count_1>50 & 
                         F10$Total_Count_2>50 & abs(F10$IncLevelDifference)<0.001),]
KO_control<-KO[which(KO$PValue<0.9 & KO$FDR>0.9 & KO$Total_Count_1>50 & 
                         KO$Total_Count_2>50 & abs(KO$IncLevelDifference)<0.001),]

#making a list
df_list <- mget(c("L100Q1_skipped", "F10_skipped", "KO_skipped",
                  "L100Q1_retained", "F10_retained", "KO_retained",
                  "L100Q1_control", "F10_control", "KO_control"))

#making gr
UE_df<-df_list
UE_df<-lapply(UE_df, function(x){x$SS<-ifelse(x$strand=="+",x$upstreamES,x$downstreamES);x$EE<-ifelse(x$strand=="+",x$upstreamEE,x$downstreamEE);return(x)})
UE_gr<-lapply(UE_df, function(x){makeGRangesFromDataFrame(x,seqnames.field = "chr",start.field = "SS",end.field = "EE",strand.field = "strand")})

UI_df<-df_list
UI_df<-lapply(UI_df, function(x){x$SS<-ifelse(x$strand=="+",x$upstreamEE,x$exonEnd);x$EE<-ifelse(x$strand=="+",x$exonStart_0base,x$downstreamES);return(x)})
UI_gr<-lapply(UI_df, function(x){makeGRangesFromDataFrame(x,seqnames.field = "chr",start.field = "SS",end.field = "EE",strand.field = "strand")})

SE_df<-df_list
SE_df<-lapply(SE_df, function(x){x$SS<-x$exonStart_0base;x$EE<-x$exonEnd;return(x)})
SE_gr<-lapply(SE_df, function(x){makeGRangesFromDataFrame(x,seqnames.field = "chr",start.field = "SS",end.field = "EE",strand.field = "strand")})

DE_df<-df_list
DE_df<-lapply(DE_df, function(x){x$SS<-ifelse(x$strand=="+",x$downstreamES,x$upstreamES);x$EE<-ifelse(x$strand=="+",x$downstreamEE,x$upstreamEE);return(x)})
DE_gr<-lapply(DE_df, function(x){makeGRangesFromDataFrame(x,seqnames.field = "chr",start.field = "SS",end.field = "EE",strand.field = "strand")})

DI_df<-df_list
DI_df<-lapply(DI_df, function(x){x$SS<-ifelse(x$strand=="+",x$exonEnd,x$upstreamEE);x$EE<-ifelse(x$strand=="+",x$downstreamES,x$exonStart_0base);return(x)})
DI_gr<-lapply(DI_df, function(x){makeGRangesFromDataFrame(x,seqnames.field = "chr",start.field = "SS",end.field = "EE",strand.field = "strand")})

getwd()
#load sequences
library(BSgenome.Hsapiens.NCBI.GRCh38)
bs<-BSgenome.Hsapiens.NCBI.GRCh38
seqlevelsStyle(bs) <- "UCSC"

UE_gr_seq<-lapply(UE_gr, function(x){getSeq(bs,x) %>% data.frame()})
UI_gr_seq<-lapply(UI_gr, function(x){getSeq(bs,x) %>% data.frame()})
SE_gr_seq<-lapply(SE_gr, function(x){getSeq(bs,x) %>% data.frame()})
DE_gr_seq<-lapply(DE_gr, function(x){getSeq(bs,x) %>% data.frame()})
DI_gr_seq<-lapply(DI_gr, function(x){getSeq(bs,x) %>% data.frame()})

UE_gr_seq<-lapply(UE_gr_seq, function(x){x$c_count<-stringr::str_count(x$.,"C");x})
UI_gr_seq<-lapply(UI_gr_seq, function(x){x$c_count<-stringr::str_count(x$.,"C");x})
SE_gr_seq<-lapply(SE_gr_seq, function(x){x$c_count<-stringr::str_count(x$.,"C");x})
DE_gr_seq<-lapply(DE_gr_seq, function(x){x$c_count<-stringr::str_count(x$.,"C");x})
DI_gr_seq<-lapply(DI_gr_seq, function(x){x$c_count<-stringr::str_count(x$.,"C");x})

UE_gr_seq<-lapply(UE_gr_seq, function(x){x$c_prop<-x$c_count/nchar(x$.);x})
UI_gr_seq<-lapply(UI_gr_seq, function(x){x$c_prop<-x$c_count/nchar(x$.);x})
SE_gr_seq<-lapply(SE_gr_seq, function(x){x$c_prop<-x$c_count/nchar(x$.);x})
DE_gr_seq<-lapply(DE_gr_seq, function(x){x$c_prop<-x$c_count/nchar(x$.);x})
DI_gr_seq<-lapply(DI_gr_seq, function(x){x$c_prop<-x$c_count/nchar(x$.);x})


UE_gr_seq_df <- bind_rows(UE_gr_seq, .id = "Class")
UI_gr_seq_df <- bind_rows(UI_gr_seq, .id = "Class")
SE_gr_seq_df <- bind_rows(SE_gr_seq, .id = "Class")
DE_gr_seq_df <- bind_rows(DE_gr_seq, .id = "Class")
DI_gr_seq_df <- bind_rows(DI_gr_seq, .id = "Class")

UE_gr_seq_df$Region<-"UE"
UI_gr_seq_df$Region<-"UI"
SE_gr_seq_df$Region<-"SE"
DE_gr_seq_df$Region<-"DE"
DI_gr_seq_df$Region<-"DI"

comb<-rbind(UE_gr_seq_df,UI_gr_seq_df,SE_gr_seq_df,DI_gr_seq_df,DE_gr_seq_df)
comb$Group<-sapply(comb$Class,function(x){strsplit(x,"_")[[1]][2]})
comb$Condition<-sapply(comb$Class,function(x){strsplit(x,"_")[[1]][1]})
comb$Region<-factor(comb$Region,levels=c("UE","UI","SE","DI","DE"))

ggplot(comb[which(comb$Condition=="L100Q1"),], aes(x = Group, y = c_prop, fill = Group)) +
  geom_boxplot(width=0.5,size=0.25,outlier.size = 0.1) +
  stat_compare_means(comparisons = list(c("control","retained"),c("skipped","retained"),c("control","skipped")),
                     label = "p.signif",label.y = c(0.6, 0.75,0.9),size=3)+
  facet_wrap(~ Region, scales = "free_x",nrow = 1) +
  theme_classic()+
  labs(y="Prop. of C's")+
  scale_fill_manual(values=c("control"="gray","retained"="#FF2600","skipped"="#0096FE"))+
  lims(y=c(0,1))+
  theme(legend.position = "none",
        axis.text.x=element_text(family="Arial",size=6, color="black",angle=45,hjust=1),
        axis.text=element_text(family="Arial",size=6, color="black"),
        axis.title = element_text(family="Arial",size=6, color="black"),
        axis.title.x=element_blank(),
        panel.background = element_blank(),
        plot.title = element_blank(),
        plot.background = element_blank(), 
        panel.border = element_blank(),
        legend.background = element_blank(),
        strip.background = element_blank(),
        strip.text = element_blank())
ggsave("FIgureS5/C_prop_L100Q.pdf",width=4,height=1.5)


#Making heatmap
L100Q<-comb[which(comb$Condition=="L100Q1"),]
F10<-comb[which(comb$Condition=="F10"),]
KO<-comb[which(comb$Condition=="KO"),]


df<-L100Q
df_wide<-df %>% group_by(Group,Region) %>% summarise(Mean_C=mean(c_prop)) %>% data.frame()
df_pval <- df %>% group_by(Region) %>% summarise(
    retained = t.test(c_prop[Group == "control"],c_prop[Group == "retained"])$p.value,
    skipped = t.test(c_prop[Group == "control"],c_prop[Group == "skipped"])$p.value,.groups = "drop") %>% melt(id.vars="Region") %>% data.frame()
df_pval<-df_pval %>% mutate(Label=case_when(value<0.0001~"****",value<0.001~"***",value<0.01~"**",value<0.05~"*")) %>% data.frame()
df_wide<-merge(df_wide,df_pval,by.x=c("Group","Region"),by.y=c("variable","Region"),all.x="T")

ggplot(df_wide, aes(x = Region, y = Group, fill =Mean_C)) +
  geom_tile(color = "black",width = 0.9, height = 0.9) +
  geom_text(aes(label =Label), size = 2.5, color = "black") +
  scale_fill_gradient(low = "white",high="#FF0000",limits = c(0.2, 0.3))+
  theme_classic()+
  scale_x_discrete(position = "bottom")+
  scale_y_discrete(position = "left")+
  theme(legend.position = "none",
        legend.key.size = unit(0.2, "cm"),
        legend.spacing.y = unit(-0.15, "cm"),
        axis.title=element_blank(),
        axis.text.y=element_blank(),
        axis.text.x=element_blank(),
        axis.line = element_blank(),
        axis.ticks=element_blank(),
        legend.text = element_text(family="Arial",size=6, color="black"),
        legend.title = element_blank(),
        legend.margin = margin(t = 0, r = 0, b = 0, l = 5),
        panel.background = element_blank(),
        plot.background = element_blank(), 
        panel.border = element_blank(),
        legend.background = element_blank())
ggsave("FIgureS5/C_prop_L100Q_heatmap.pdf",width=2.5,height=.75)

df<-KO
df_wide<-df %>% group_by(Group,Region) %>% summarise(Mean_C=mean(c_prop)) %>% data.frame()
df_pval <- df %>% group_by(Region) %>% summarise(
    retained = t.test(c_prop[Group == "control"],c_prop[Group == "retained"])$p.value,
    skipped = t.test(c_prop[Group == "control"],c_prop[Group == "skipped"])$p.value,.groups = "drop") %>% melt(id.vars="Region") %>% data.frame()
df_pval<-df_pval %>% mutate(Label=case_when(value<0.0001~"****",value<0.001~"***",value<0.01~"**",value<0.05~"*")) %>% data.frame()
df_wide<-merge(df_wide,df_pval,by.x=c("Group","Region"),by.y=c("variable","Region"),all.x="T")

g2<-ggplot(df_wide, aes(x = Region, y = Group, fill =Mean_C)) +
  geom_tile(color = "black",width = 0.9, height = 0.9) +
  geom_text(aes(label =Label), size = 2.5, color = "black") +
  scale_fill_gradient(low = "white",high="#FF0000",limits = c(0.2, 0.3))+
  theme_classic()+
  scale_x_discrete(position = "bottom")+
  scale_y_discrete(position = "left")+
  theme(legend.position = "right",
        legend.key.size = unit(0.2, "cm"),
        legend.spacing.y = unit(-0.15, "cm"),
        axis.title=element_blank(),
        axis.text.y=element_blank(),
        axis.text.x=element_blank(),
        axis.line = element_blank(),
        axis.ticks=element_blank(),
        legend.text = element_text(family="Arial",size=6, color="black"),
        legend.title = element_blank(),
        legend.margin = margin(t = 0, r = 0, b = 0, l = 5),
        panel.background = element_blank(),
        plot.background = element_blank(), 
        panel.border = element_blank(),
        legend.background = element_blank())
ggsave("FIgureS5/C_prop_KO_heatmap.pdf",width=2.5,height=.75)

leg<-get_legend(g2+theme(legend.position = "right"))
ggsave("FIgureS5/C_prop_legend.pdf",leg,height=0.8,width=0.5)



```







#Figure S4E
```{r, fig.width=1.5, fig.height=1.5}
load("~/Desktop/Dominguez_Lab/PCBP1_FINAL/RNA-Seq/rMATS/HCT_rMATS.RData")

HCT_L100Q2<-HCT$Parent_F10$SE
HCT_L100Q<-HCT$Parent_L100Q$SE

HCT_L100Q2<-HCT_L100Q2[which(HCT_L100Q2$FDR<0.05 & HCT_L100Q2$PValue<0.05 & abs(HCT_L100Q2$IncLevelDifference)>0.1
                     & HCT_L100Q2$Total_Count_1>50 & HCT_L100Q2$Total_Count_2>50),]
HCT_L100Q<-HCT_L100Q[which(HCT_L100Q$FDR<0.05 & HCT_L100Q$PValue<0.05 & abs(HCT_L100Q$IncLevelDifference)>0.1
                           & HCT_L100Q$Total_Count_1>50 & HCT_L100Q$Total_Count_2>50),]

HCT_L100Q2$Identifier<-paste(HCT_L100Q2$chr,"_",HCT_L100Q2$exonStart_0base,"-",HCT_L100Q2$exonEnd,"_",HCT_L100Q2$upstreamES,"-",HCT_L100Q2$upstreamEE,"_",
                         HCT_L100Q2$downstreamES,"-",HCT_L100Q2$downstreamEE,"_",HCT_L100Q2$strand,"_",HCT_L100Q2$GeneID,"_",HCT_L100Q2$geneSymbol,sep="")
HCT_L100Q$Identifier<-paste(HCT_L100Q$chr,"_",HCT_L100Q$exonStart_0base,"-",HCT_L100Q$exonEnd,"_",HCT_L100Q$upstreamES,"-",
                            HCT_L100Q$upstreamEE,"_",HCT_L100Q$downstreamES,"-",HCT_L100Q$downstreamEE,"_",HCT_L100Q$strand,"_",HCT_L100Q$GeneID,"_",HCT_L100Q$geneSymbol,sep="")

SE<-list("L100Q"=HCT_L100Q$Identifier,"L100Q_2"=HCT_L100Q2$Identifier)

df<-merge(HCT_L100Q2[c("IncLevelDifference","Identifier")],HCT_L100Q[c("IncLevelDifference","Identifier")],by="Identifier")
colnames(df)<-c("Identifier","L100Q_2","L100Q")
df$Group<-"gray"
df$Group[which(df$L100Q>0 & df$L100Q_2>0)]<-L100_col
df$Group[which(df$L100Q<0 & df$L100Q<0)]<-L100_col

ggplot(df,aes(x = L100Q,y = L100Q_2,color=Group,fill = Group))+
  geom_point(shape = 21,alpha=0.5,size=0.5)+
  scale_fill_identity()+
  scale_colour_identity()+
  lims(x=c(-0.55,0.55),y=c(-0.5,0.55))+
  labs(x=bquote(Delta~PSI(Parent-L100Q-1)),y=bquote(Delta~PSI(Parent-L100Q-2)))+
  stat_cor(inherit.aes=F,data=df,aes(x = L100Q,y = L100Q_2),method = "spearman",size = 2,family="Arial")+
  theme_classic()+
  theme(axis.text=element_text(size=6, color="black",family="Arial"), 
        axis.title = element_text(size=6, color="black",family="Arial"),
        panel.background = element_blank(), 
        plot.background = element_blank(), 
        panel.border = element_blank(),
        legend.background = element_blank())
ggsave("FigureS5/FigS5E.pdf",width=1.5,height=1.5)
```

#Figure S4F
```{r, fig.width=1.5, fig.height=1.5}
rm(list=ls())
load("Figure_Tables/Porter_rMATS.RData")

KD<-Porter$WT_KD$SE
KD_sub<-KD[which(KD$Total_Count_1>50 & KD$Total_Count_2>50),]
KD_sub$Group<-"ns"
KD_sub$Group[which(KD_sub$PValue<0.05 & KD_sub$FDR<0.05 & KD_sub$IncLevelDifference>0.1)]<-"up"
KD_sub$Group[which(KD_sub$PValue<0.05 & KD_sub$FDR<0.05 & KD_sub$IncLevelDifference<(-0.1))]<-"down"

##Volcano Plot
cols <- c("up" = Parent_col, "down" = KD_col, "ns" = "grey") 
sizes <- c("up" = 0.75, "down" = 0.75, "ns" = 0.25) 
alphas <- c("up" = 0.7, "down" = 0.7, "ns" = 0.5)

Up_genes<-as.character(length(which(KD_sub$Group=="up")))
Down_genes<-as.character(length(which(KD_sub$Group=="down")))

volcano<-KD_sub %>%
  ggplot(aes(x = IncLevelDifference,
             y = -log10(FDR),
             fill = Group,
             color=Group,
             size = Group,
             alpha =Group)) + 
  geom_point(shape = 21) +
  geom_hline(yintercept = -log10(0.05),
             linetype = "dashed") + 
  geom_vline(xintercept = c(-0.1,0.1),
             linetype = "dashed")+
  scale_fill_manual(values = cols) + # Modify point colour
  scale_color_manual(values = cols) + # Modify point colour
  scale_size_manual(values = sizes) + # Modify point size
  scale_alpha_manual(values = alphas) + # Modify point transparency
  scale_x_continuous(breaks = c(-0.8,-0.4,0,0.4,0.8),       
                    limits = c(-0.8, 0.8))+
  lims(y=c(0,40))+
  labs(x=bquote(Delta~PSI(Parent-KD)))+
  theme_classic()+
  geom_text(x=0.5, y=30, label=paste("Skipped \n",Up_genes,sep=""),color="black",size=2,family="Arial")+
  geom_text(x=-0.5, y=30, label=paste("Retained \n",Down_genes,sep=""),color="black",size=2,family="Arial")+
  theme(legend.position = "none",
        axis.text=element_text(family="Arial",size=6, color="black"),
        axis.title = element_text(family="Arial",size=6, color="black"),
        panel.background = element_blank(),
        plot.background = element_blank(), 
        panel.border = element_blank(),
        legend.background = element_blank())
volcano
ggsave("FigureS5/FigS5F.png",width=1.5,height=1.5)

```

#Figure S4G
```{r, fig.width=1.5, fig.height=1.5}
rm(list=ls())
load("Figure_Tables/Porter_rMATS.RData")

KD<-Porter$WT_KD$SE
WT_KD<-Porter$WT_KD_WT$SE
L100_KD<-Porter$WT_KD_L100$SE

KD$Identifier<-paste(KD$chr,"_",KD$exonStart_0base,"-",KD$exonEnd,"_",KD$upstreamES,"-",KD$upstreamEE,"_",
                         KD$downstreamES,"-",KD$downstreamEE,"_",KD$strand,"_",KD$GeneID,"_",KD$geneSymbol,sep="")
WT_KD$Identifier<-paste(WT_KD$chr,"_",WT_KD$exonStart_0base,"-",WT_KD$exonEnd,"_",WT_KD$upstreamES,"-",WT_KD$upstreamEE,"_",
                        WT_KD$downstreamES,"-",WT_KD$downstreamEE,"_",WT_KD$strand,"_",WT_KD$GeneID,"_",WT_KD$geneSymbol,sep="")
L100_KD$Identifier<-paste(L100_KD$chr,"_",L100_KD$exonStart_0base,"-",L100_KD$exonEnd,"_",L100_KD$upstreamES,"-",L100_KD$upstreamEE,"_"
                          ,L100_KD$downstreamES,"-",L100_KD$downstreamEE,"_",L100_KD$strand,"_",L100_KD$GeneID,"_",L100_KD$geneSymbol,sep="")

#Getting sig events
KD_sig<-KD[which(KD$PValue<0.05 & KD$FDR<0.05 & KD$Total_Count_1>50 & KD$Total_Count_2>50 & abs(KD$IncLevelDifference)>0.1),]

#Combining
comb<-merge(KD_sig[c("Identifier","IncLevelDifference")],WT_KD[c("Identifier","IncLevelDifference")],by="Identifier")
comb<-merge(comb,L100_KD[c("Identifier","IncLevelDifference")],by="Identifier")
colnames(comb)<-c("Identifier","KD","KD+\nWT","KD+\nL100Q")
rownames(comb)<-comb$Identifier

comb_melt<-reshape2::melt(comb,id.vars = "Identifier")
comb_melt$variable<-factor(comb_melt$variable,levels =c("KD","KD+\nWT","KD+\nL100Q"))
cols<-c("KD"=KD_col,"KD+\nWT"=Parent_col,"KD+\nL100Q"=L100_col)

ggplot(comb_melt,aes(x=variable,y=abs(value),fill=variable))+
  geom_boxplot(alpha=0.8,outlier.size = 0.5)+
  theme_classic()+
  lims(y=c(0,1.2))+
  scale_fill_manual(values = cols)+
  labs(x="Condition",y=bquote(Abs.~Delta~PSI))+
  stat_compare_means(comparisons = list(c("KD","KD+\nWT"),c("KD+\nWT","KD+\nL100Q"),c("KD","KD+\nL100Q")), label.y = c(0.75, 0.83, 1),label="p.signif")+
  theme(legend.position = "none",
        axis.text=element_text(family="Arial",size=6, color="black"),
        axis.title = element_text(family="Arial",size=6, color="black"),
        axis.title.x=element_blank(),
        panel.background = element_blank(),
        plot.title = element_blank(),
        plot.background = element_blank(), 
        panel.border = element_blank(),
        legend.background = element_blank())

ggsave("FigureS5/FigS5G.pdf",width=1.5,height=1.5)
```

#Figure S4H
```{r}
rm(list = ls())
load("Figure_Tables/RKO_rMATS.RData")

L100Q<-RKO$Parent_L100Q
L100Q<-lapply(L100Q, function(x){y<-x[which(x$FDR<0.05 & x$PValue<0.05 & abs(x$IncLevelDifference)>0.1 & 
                                                x$Total_Count_1>50 & x$Total_Count_2>50),];return(y)})
df<-data.frame(t(data.frame((lapply(L100Q, nrow)))))
df$Event<-rownames(df)
colnames(df)<-c("Count","Event")
df$Class<-"L100Q"
df$Event<-factor(df$Event,levels=c("SE","RI","MXE","A3SS","A5SS"))
df$Xpos<-cumsum(df$Count[5:1])[5:1]/sum(df$Count)
df$Label<-paste(df$Event,"=",df$Count,sep="")

ggplot(df,aes(x=Class,y=Count,fill=Event))+
  geom_bar(stat="identity", position="fill",alpha=0.75)+
  labs(x="",y="# of Sig. Events")+
  theme_classic()+
  geom_text(aes(y = Xpos, label = Count), vjust = 1.2, colour = "black",family="Arial",size=2)+
  #geom_text(aes(y = Xpos, label = Event),vjust = 1.2, colour = "black",family="Arial",size=2)+
  scale_fill_manual(values = c("SE"="#5770FF","RI"="#690002","MXE"="#D9C2EA", "A3SS"="#FB8808","A5SS"="#89AF84"))+
  theme(legend.position = "none",
        axis.text=element_blank(),
        axis.title = element_blank(),
        legend.text = element_text(family="Arial",size=8, color="black"),
        panel.background = element_blank(),
        legend.title = element_blank(),
        plot.background = element_blank(), 
        panel.border = element_blank(),
        legend.background = element_blank(),
        legend.key.height= unit(0.5, 'cm'),
        legend.key.width= unit(0.5, 'cm'),
        axis.ticks= element_blank(),
        line = element_blank())
ggsave("FigureS5/FigS5H.pdf",width=0.5,height=1.5)
```

#Figure S4I
```{r, fig.width=1.5, fig.height=1.5}
load("Figure_Tables/RKO_rMATS.RData")

L100Q<-RKO$Parent_L100Q$SE
L100Q_sub<-L100Q[which(L100Q$Total_Count_1>50 & L100Q$Total_Count_2>50),]
L100Q_sub$Group<-"ns"
L100Q_sub$Group[which(L100Q_sub$PValue<0.05 & L100Q_sub$FDR<0.05 & L100Q_sub$IncLevelDifference>0.1)]<-"up"
L100Q_sub$Group[which(L100Q_sub$PValue<0.05 & L100Q_sub$FDR<0.05 & L100Q_sub$IncLevelDifference<(-0.1))]<-"down"

##Volcano Plot
cols <- c("up" = Parent_col, "down" = L100_col, "ns" = "grey") 
sizes <- c("up" = 0.75, "down" = 0.75, "ns" = 0.25) 
alphas <- c("up" = 0.7, "down" = 0.7, "ns" = 0.5)

Up_genes<-as.character(length(which(L100Q_sub$Group=="up")))
Down_genes<-as.character(length(which(L100Q_sub$Group=="down")))

volcano<-L100Q_sub %>%
  ggplot(aes(x = IncLevelDifference,
             y = -log10(FDR),
             fill = Group,
             color=Group,
             size = Group,
             alpha =Group)) + 
  geom_point(shape = 21) +
  geom_hline(yintercept = -log10(0.05),
             linetype = "dashed") + 
  geom_vline(xintercept = c(-0.1,0.1),
             linetype = "dashed")+
  scale_fill_manual(values = cols) + # Modify point colour
  scale_color_manual(values = cols) + # Modify point colour
  scale_size_manual(values = sizes) + # Modify point size
  scale_alpha_manual(values = alphas) + # Modify point transparency
  scale_x_continuous(breaks = c(-0.4,-0.2,0,0.2,0.4),       
                     limits = c(-0.5, 0.5))+
  lims(y=c(0,40))+
  labs(x=bquote(Delta~PSI(Parent-L100Q)))+
  theme_classic()+
  geom_text(x=0.3, y=30, label=paste("Skipped \n",Up_genes,sep=""),color="black",size=2,family="Arial")+
  geom_text(x=-0.3, y=30, label=paste("Retained \n",Down_genes,sep=""),color="black",size=2,family="Arial")+
  theme(legend.position = "none",
        axis.text=element_text(family="Arial",size=6, color="black"),
        axis.title = element_text(family="Arial",size=6, color="black"),
        panel.background = element_blank(),
        plot.background = element_blank(), 
        panel.border = element_blank(),
        legend.background = element_blank())
volcano
ggsave("FigureS5/FigS5I.png",width=1.5,height=1.5)

```

#Figure S4J
```{r, fig.width=1.2, fig.height=1.5}
rm(list=ls())
load("Figure_Tables/RKO_rMATS.RData")

KO<-RKO$Parent_KO
KO<-lapply(KO, function(x){y<-x[which(x$FDR<0.05 & x$PValue<0.05 & abs(x$IncLevelDifference)>0.1 & 
                                                x$Total_Count_1>50 & x$Total_Count_2>50),];return(y)})
df<-data.frame(t(data.frame((lapply(KO, nrow)))))
df$Event<-rownames(df)
colnames(df)<-c("Count","Event")
df$Class<-"KO"
df$Event<-factor(df$Event,levels=c("SE","RI","MXE","A3SS","A5SS"))
df$Xpos<-cumsum(df$Count[5:1])[5:1]/sum(df$Count)
df$Label<-paste(df$Event,"=",df$Count,sep="")

ggplot(df,aes(x=Class,y=Count,fill=Event))+
  geom_bar(stat="identity", position="fill",alpha=0.75)+
  labs(x="",y="# of Sig. Events")+
  theme_classic()+
  geom_text(aes(y = Xpos, label = Count), vjust = 1.2, colour = "black",family="Arial",size=2)+
  #geom_text(aes(y = Xpos, label = Event),vjust = 1.2, colour = "black",family="Arial",size=2)+
  scale_fill_manual(values = c("SE"="#5770FF","RI"="#690002","MXE"="#D9C2EA", "A3SS"="#FB8808","A5SS"="#89AF84"))+
  theme(legend.position = "none",
        axis.text=element_blank(),
        axis.title = element_blank(),
        legend.text = element_text(family="Arial",size=8, color="black"),
        panel.background = element_blank(),
        legend.title = element_blank(),
        plot.background = element_blank(), 
        panel.border = element_blank(),
        legend.background = element_blank(),
        legend.key.height= unit(0.5, 'cm'),
        legend.key.width= unit(0.5, 'cm'),
        axis.ticks= element_blank(),
        line = element_blank())
ggsave("FigureS5/Fig5J.pdf",width=0.5,height=1.5)
```

#Figure S4K
```{r, fig.width=1.5, fig.height=1.5}
load("Figure_Tables/RKO_rMATS.RData")

KO<-RKO$Parent_KO$SE
KO_sub<-KO[which(KO$Total_Count_1>50 & KO$Total_Count_2>50),]
KO_sub$Group<-"ns"
KO_sub$Group[which(KO_sub$PValue<0.05 & KO_sub$FDR<0.05 & KO_sub$IncLevelDifference>0.1)]<-"up"
KO_sub$Group[which(KO_sub$PValue<0.05 & KO_sub$FDR<0.05 & KO_sub$IncLevelDifference<(-0.1))]<-"down"

##Volcano Plot
cols <- c("up" = Parent_col, "down" = KO_col, "ns" = "grey") 
sizes <- c("up" = 0.75, "down" = 0.75, "ns" = 0.25) 
alphas <- c("up" = 0.7, "down" = 0.7, "ns" = 0.5)

Up_genes<-as.character(length(which(KO_sub$Group=="up")))
Down_genes<-as.character(length(which(KO_sub$Group=="down")))

volcano<-KO_sub %>%
  ggplot(aes(x = IncLevelDifference,
             y = -log10(FDR),
             fill = Group,
             color=Group,
             size = Group,
             alpha =Group)) + 
  geom_point(shape = 21) +
  geom_hline(yintercept = -log10(0.05),
             linetype = "dashed") + 
  geom_vline(xintercept = c(-0.1,0.1),
             linetype = "dashed")+
  scale_fill_manual(values = cols) + # Modify point colour
  scale_color_manual(values = cols) + # Modify point colour
  scale_size_manual(values = sizes) + # Modify point size
  scale_alpha_manual(values = alphas) + # Modify point transparency
  scale_x_continuous(breaks = c(-0.4,-0.2,0,0.2,0.4),       
                     limits = c(-0.5, 0.5))+
  lims(y=c(0,40))+
  labs(x=bquote(Delta~PSI(Parent-hetKO)))+
  theme_classic()+
  geom_text(x=0.3, y=30, label=paste("Skipped \n",Up_genes,sep=""),color="black",size=2,family="Arial")+
  geom_text(x=-0.3, y=30, label=paste("Retained \n",Down_genes,sep=""),color="black",size=2,family="Arial")+
  theme(legend.position = "none",
        axis.text=element_text(family="Arial",size=6, color="black"),
        axis.title = element_text(family="Arial",size=6, color="black"),
        panel.background = element_blank(),
        plot.background = element_blank(), 
        panel.border = element_blank(),
        legend.background = element_blank())
volcano
ggsave("FigureS5/FigS5K.png",width=1.5,height=1.5)

```

#Figure S4L
```{r}
rm(list=ls())
load("Figure_Tables/RKO_rMATS.RData")

HCT_KO<-RKO$Parent_KO$SE
HCT_L100Q<-RKO$Parent_L100Q$SE

HCT_KO<-HCT_KO[which(HCT_KO$FDR<0.05 & HCT_KO$PValue<0.05 & abs(HCT_KO$IncLevelDifference)>0.1 
                     & HCT_KO$Total_Count_1>50 & HCT_KO$Total_Count_2>50),]
HCT_L100Q<-HCT_L100Q[which(HCT_L100Q$FDR<0.05 & HCT_L100Q$PValue<0.05 & abs(HCT_L100Q$IncLevelDifference)>0.1
                           & HCT_L100Q$Total_Count_1>50 & HCT_L100Q$Total_Count_2>50),]

HCT_KO$Identifier<-paste(HCT_KO$chr,"_",HCT_KO$exonStart_0base,"-",HCT_KO$exonEnd,"_",HCT_KO$upstreamES,"-",HCT_KO$upstreamEE,"_",
                         HCT_KO$downstreamES,"-",HCT_KO$downstreamEE,"_",HCT_KO$strand,"_",HCT_KO$GeneID,"_",HCT_KO$geneSymbol,sep="")
HCT_L100Q$Identifier<-paste(HCT_L100Q$chr,"_",HCT_L100Q$exonStart_0base,"-",HCT_L100Q$exonEnd,"_",HCT_L100Q$upstreamES,"-",
                            HCT_L100Q$upstreamEE,"_",HCT_L100Q$downstreamES,"-",HCT_L100Q$downstreamEE,"_",HCT_L100Q$strand,"_",HCT_L100Q$GeneID,"_",HCT_L100Q$geneSymbol,sep="")

SE<-list("L100Q"=HCT_L100Q$Identifier,"hetKO"=HCT_KO$Identifier)

v<-ggvenn::ggvenn(SE,fill_color=c(L100_col,KO_col),set_name_size=3,show_percentage=F,text_size=2.5,fill_alpha=0.6,stroke_size=0.5)+
  coord_cartesian(ylim = c(-1.2, 1.5))+
  theme(legend.position = "none",
        panel.background = element_blank(), 
        plot.background = element_blank(), 
        panel.border = element_blank(),
        legend.background = element_blank(),
        axis.title = element_text(family="Arial",size=0, color="black"),
        axis.text=element_text(family="Arial",size=0, color="black"),
        textt=element_text(family="Arial", size=0,color="black"))
v
ggsave("FigureS5/FigS5L.pdf",width=1.15,height=0.84)

```

#Figure S4M
```{r,fig.width=1, fig.height=1}
rm(list=ls())

load("Figure_Tables/RKO_rMATS.RData")
HCT_KO<-RKO$Parent_KO$SE
HCT_L100Q<-RKO$Parent_L100Q$SE

HCT_KO<-HCT_KO[which(HCT_KO$FDR<0.05 & HCT_KO$PValue<0.05 & abs(HCT_KO$IncLevelDifference)>0.1 
                     & HCT_KO$Total_Count_1>50 & HCT_KO$Total_Count_2>50),]
HCT_L100Q<-HCT_L100Q[which(HCT_L100Q$FDR<0.05 & HCT_L100Q$PValue<0.05 & abs(HCT_L100Q$IncLevelDifference)>0.1
                           & HCT_L100Q$Total_Count_1>50 & HCT_L100Q$Total_Count_2>50),]

HCT_KO$Identifier<-paste(HCT_KO$chr,"_",HCT_KO$exonStart_0base,"-",HCT_KO$exonEnd,"_",HCT_KO$upstreamES,"-",HCT_KO$upstreamEE,"_",
                         HCT_KO$downstreamES,"-",HCT_KO$downstreamEE,"_",HCT_KO$strand,"_",HCT_KO$GeneID,"_",HCT_KO$geneSymbol,sep="")
HCT_L100Q$Identifier<-paste(HCT_L100Q$chr,"_",HCT_L100Q$exonStart_0base,"-",HCT_L100Q$exonEnd,"_",HCT_L100Q$upstreamES,"-",
                            HCT_L100Q$upstreamEE,"_",HCT_L100Q$downstreamES,"-",HCT_L100Q$downstreamEE,"_",HCT_L100Q$strand,"_",HCT_L100Q$GeneID,"_",HCT_L100Q$geneSymbol,sep="")


df<-merge(HCT_KO[c("IncLevelDifference","Identifier")],HCT_L100Q[c("IncLevelDifference","Identifier")],by="Identifier")
colnames(df)<-c("Identifier","KO","L100Q")
df$Group<-"gray"
df$Group[which(df$L100Q>0 & df$KO>0)]<-Parent_col
df$Group[which(df$L100Q<0 & df$KO<0)]<-L100_col

ggplot(df,aes(x = L100Q,y = KO,color=Group,fill = Group))+
  geom_point(shape = 21,alpha=0.5,size=0.5)+
  scale_fill_identity()+
  scale_colour_identity()+
  lims(x=c(-0.55,0.55),y=c(-0.5,0.55))+
  labs(x=bquote(Delta~PSI(Parent-L100Q)),y=bquote(Delta~PSI(Parent-hetKO)))+
  stat_cor(inherit.aes=F,data=df,aes(x = L100Q,y = KO),method = "spearman",size = 1.25,family="Arial",label.y=0.55)+
  theme_classic()+
  theme(axis.text=element_text(size=6, color="black",family="Arial"), 
        axis.title = element_text(size=6, color="black",family="Arial"),
        panel.background = element_blank(), 
        plot.background = element_blank(), 
        panel.border = element_blank(),
        legend.background = element_blank())

ggsave("FigureS5/FigS5M.pdf",width=1.5,height=1.5)

```

#Figure S4N
```{r,fig.width=3, fig.height=3}
rm(list=ls())
load("Figure_Tables/RKO_rMATS.RData")
KO<-RKO$Parent_KO$SE
L1001<-RKO$Parent_L100Q$SE
HDR2<-RKO$Parent_HDR$SE

KO$Identifier<-paste(KO$chr,"_",KO$exonStart_0base,"-",KO$exonEnd,"_",KO$upstreamES,"-",
                     KO$upstreamEE,"_",KO$downstreamES,"-",KO$downstreamEE,"_",KO$strand,"_",
                     KO$GeneID,"_",KO$geneSymbol,sep="")
L1001$Identifier<-paste(L1001$chr,"_",L1001$exonStart_0base,"-",L1001$exonEnd,"_",
                        L1001$upstreamES,"-",L1001$upstreamEE,"_",L1001$downstreamES,"-",
                        L1001$downstreamEE,"_",L1001$strand,"_",L1001$GeneID,"_",L1001$geneSymbol,sep="")
HDR2$Identifier<-paste(HDR2$chr,"_",HDR2$exonStart_0base,"-",HDR2$exonEnd,"_",HDR2$upstreamES,"-",
                       HDR2$upstreamEE,"_",HDR2$downstreamES,"-",HDR2$downstreamEE,"_",HDR2$strand,"_",
                       HDR2$GeneID,"_",HDR2$geneSymbol,sep="")

#selecting events that changed between Parent and L100
L1001_sig<-L1001[which(L1001$PValue<0.05 & L1001$FDR<0.05 & L1001$Total_Count_1>50 & 
                         L1001$Total_Count_2>50 & abs(L1001$IncLevelDifference)>0.1),]
changed_events<-L1001_sig$Identifier

#Getting intersection of events
KO_sub<-KO[which(KO$Identifier %in% changed_events),]
L1001_sub<-L1001[which(L1001$Identifier %in% changed_events),]
HDR2_sub<-HDR2[which(HDR2$Identifier %in% changed_events),]

comb<-merge(KO_sub[c("Identifier","IncLevel1","IncLevel2")],
            L1001_sub[c("Identifier","IncLevel1","IncLevel2")],by="Identifier")
comb<-merge(comb,HDR2_sub[c("Identifier","IncLevel1","IncLevel2")],by="Identifier")


colnames(comb)<-c("Identifier","WT","KO","WT2","L1001","WT4","HDR2")
comb<-comb[c("Identifier","WT","KO","L1001","HDR2")]


comb <- comb %>% separate(WT, into = c("WT1", "WT2","WT3"), sep = ",")
comb <- comb %>% separate(KO, into = c("KO1", "KO2","KO3"), sep = ",")
comb <- comb %>% separate(L1001, into = c("L10011", "L10012","L10013"), sep = ",")
comb <- comb %>% separate(HDR2, into = c("HDR21", "HDR22","HDR23"), sep = ",")
rownames(comb)<-comb$Identifier
comb<-comb[,-1]
comb<-as.data.frame(sapply(comb,as.numeric))


legeng<-data.frame(colnames(comb))
legeng$Condition<-c("Parent","Parent","Parent","KO","KO","KO","L100Q","L100Q","L100Q","Silent","Silent","Silent")
rownames(legeng)<-legeng$colnames.comb.


Condition<-c("Parent"=Parent_col,"KO"=KO_col,"L100Q"=L100_col,"Silent"=HDR_col)
my_colors<-list("Condition"=Condition)

pdf("FigureS5/FigS5N.pdf",width = 3,height = 3)
pheatmap(comb,show_rownames=F,show_colnames = F, cluster_cols=T, cluster_rows=T,scale="row",
         clustering_distance_rows="euclidean", clustering_distance_cols="euclidean",
         clustering_method="complete",border_color=FALSE,legend=T,fontsize = 6,
         color = colorRampPalette(c("#3AAFA9", "white", "#D97700"))(100),annotation_legend = T,annotation_names_col=F,
         annotation_col=legeng["Condition"],annotation_colors = my_colors,treeheight_col =6,treeheight_row=0)
dev.off()
```

#Figure S4O-ATP13A2.txt
```{r,fig.width=1.2, fig.height=1.2}
rm(list=ls())
PSI<-read.table("Figure4/Round3 RT-PCR txt/ATP13A2.txt",header=T,sep="\t")


PSI$ID<-"ATP13A2"
PSI_melt<-melt(PSI,id.vars = "ID")
PSI_melt$variable<-as.character(PSI_melt$variable)
PSI_melt$variable[which(PSI_melt$variable=="L100Q.1.")]<-"L100Q-1"
PSI_melt$variable[which(PSI_melt$variable=="L100Q.2.")]<-"L100Q-2"
PSI_melt$variable[which(PSI_melt$variable=="HDR2")]<-"Silent"
PSI_melt$variable[which(PSI_melt$variable=="KO")]<-"hetKO"
PSI_melt$variable<-sapply(as.character(PSI_melt$variable),function(x){strsplit(x,"[.]")[[1]][1]})
PSI_melt$variable<-factor(PSI_melt$variable,levels = c("Parent","Silent","L100Q-1","L100Q-2","hetKO","shCTRL","shPCBP1"))
PSI_melt$value<-as.numeric(PSI_melt$value)

m_HCT<-PSI_melt[which(!(PSI_melt$variable %in% c("shCTRL","shPCBP1"))),]
m_sh<-PSI_melt[which(PSI_melt$variable %in% c("shCTRL","shPCBP1")),]

#means
PSI_mean<-aggregate(value ~ variable, data = PSI_melt, FUN = base::mean)

mean_HCT<-PSI_mean[which(!(PSI_mean$variable %in% c("shCTRL","shPCBP1"))),]
mean_sh<-PSI_mean[which(PSI_mean$variable %in% c("shCTRL","shPCBP1")),]

m_HCT$Diff<-mean_HCT$value[which(mean_HCT$variable=="Parent")]-m_HCT$value
m_sh$Diff<-mean_sh$value[which(mean_sh$variable=="shCTRL")]-m_sh$value

comparisons_hct<-list(c("Parent","Silent"),c("Parent","L100Q-1"),c("Parent","L100Q-2"),c("Parent","hetKO"))
comparisons_sh<-list(c("shCTRL","shPCBP1"))

colors_hct<-c("Parent"=Parent_col,"Silent"=HDR_col,"L100Q-1"=L100_col,"L100Q-2"=L100_col2,"hetKO"=KO_col)
colors_sh<-c("shCTRL"="gray","shPCBP1"=KD_col)

hct_test <- compare_means(Diff ~ variable,comparisons = comparisons_hct, p.adjust.method = "fdr", method='t.test', data = m_HCT)
hct_test<-hct_test[which(hct_test$group1=="Parent"),]
hct_test<-hct_test %>% mutate(y.position = c(0.07,0.1,0.13,0.16)+0.01)

ggplot(m_HCT,aes(x=variable,y=Diff,group=variable))+
  geom_boxplot(aes(color=variable),fill="white",outlier.size = 0.2,flatten=0.1,size = 0.3)+
  stat_pvalue_manual(hct_test, label = "p.signif",xmin="group1",xmax="group2",size = 2)+
  geom_point(aes(color=variable),size=0.05)+
  scale_color_manual(values =colors_hct)+
  lims(y=c(-0.1,0.20))+
  theme_classic()+
  ylab(bquote(Delta~PSI~(Exon~Skipping)))+
  theme(legend.position = "none",
        axis.text=element_text(family="Arial",size=5, color="black"),
        axis.text.x=element_text(family="Arial",size=5, color="black",angle=90,hjust=1),
        axis.title = element_text(family="Arial",size=5, color="black"),
        axis.title.x = element_blank(),
        panel.background = element_blank(),
        plot.background = element_blank(), 
        panel.border = element_blank(),
        legend.background = element_blank())
ggsave("FigureS5/ATP13A2_Splicing_1.pdf",width=1.2,height=1.2)


sh_test <- compare_means(Diff ~ variable,comparisons = colors_sh, p.adjust.method = "fdr", method='t.test', data = m_sh)
sh_test<-sh_test %>% mutate(y.position =0.2)

ggplot(m_sh,aes(x=variable,y=Diff))+
  geom_boxplot(aes(color=variable),fill="white",outlier.size = 0.3,flatten=0.1,size = 0.3)+
  stat_pvalue_manual(sh_test, label = "p.signif",xmin="group1",xmax="group2",size = 2)+
  geom_point(aes(color=variable),size=0.2)+
  scale_y_continuous(position = "right",limits = c(-0.01,0.25))+
  scale_color_manual(values =colors_sh)+
  theme_classic()+
  ylab(bquote(Delta~PSI~(Exon~Skipping)))+
  theme(legend.position = "none",
        axis.text=element_text(family="Arial",size=5, color="black"),
        axis.text.x=element_text(family="Arial",size=5, color="black",angle=90,hjust=1),
        axis.title = element_text(family="Arial",size=5, color="black"),
        axis.title.x = element_blank(),
        panel.background = element_blank(),
        plot.background = element_blank(), 
        panel.border = element_blank(),
        legend.background = element_blank(),
        axis.line.y.left = element_blank(),
        axis.ticks.y.left = element_blank(),
        axis.text.y.left = element_blank(),
        axis.title.y.left = element_blank(),
        )
ggsave("FigureS5/ATP13A2_Splicing_2.pdf",width=0.8,height=1.2)
```

#Figure S4P-BIRCA
```{r,fig.width=1.2, fig.height=1.2}
rm(list=ls())
PSI<-read.table("Figure4/Round3 RT-PCR txt/BIRCA.txt",header=T,sep="\t")


PSI$ID<-"BIRCA"
PSI_melt<-reshape2::melt(PSI,id.vars = "ID")
PSI_melt$variable<-as.character(PSI_melt$variable)
PSI_melt$variable[which(PSI_melt$variable=="L100Q.1.")]<-"L100Q-1"
PSI_melt$variable[which(PSI_melt$variable=="L100Q.2.")]<-"L100Q-2"
PSI_melt$variable[which(PSI_melt$variable=="HDR2")]<-"Silent"
PSI_melt$variable[which(PSI_melt$variable=="KO")]<-"hetKO"
PSI_melt$variable<-sapply(as.character(PSI_melt$variable),function(x){strsplit(x,"[.]")[[1]][1]})
PSI_melt$variable<-factor(PSI_melt$variable,levels = c("Parent","Silent","L100Q-1","L100Q-2","hetKO","shCTRL","shPCBP1"))
PSI_melt$value<-as.numeric(PSI_melt$value)

m_HCT<-PSI_melt[which(!(PSI_melt$variable %in% c("shCTRL","shPCBP1"))),]
m_sh<-PSI_melt[which(PSI_melt$variable %in% c("shCTRL","shPCBP1")),]

#means
PSI_mean<-aggregate(value ~ variable, data = PSI_melt, FUN = base::mean)

mean_HCT<-PSI_mean[which(!(PSI_mean$variable %in% c("shCTRL","shPCBP1"))),]
mean_sh<-PSI_mean[which(PSI_mean$variable %in% c("shCTRL","shPCBP1")),]

m_HCT$Diff<-mean_HCT$value[which(mean_HCT$variable=="Parent")]-m_HCT$value
m_sh$Diff<-mean_sh$value[which(mean_sh$variable=="shCTRL")]-m_sh$value

comparisons_hct<-list(c("Parent","Silent"),c("Parent","L100Q-1"),c("Parent","L100Q-2"),c("Parent","hetKO"))
comparisons_sh<-list(c("shCTRL","shPCBP1"))

colors_hct<-c("Parent"=Parent_col,"Silent"=HDR_col,"L100Q-1"=L100_col,"L100Q-2"=L100_col2,"hetKO"=KO_col)
colors_sh<-c("shCTRL"="gray","shPCBP1"=KD_col)

hct_test <- compare_means(Diff ~ variable,comparisons = comparisons_hct, p.adjust.method = "fdr", method='t.test', data = m_HCT)
hct_test<-hct_test[which(hct_test$group1=="Parent"),]
hct_test<-hct_test %>% mutate(y.position = c(0.07,0.1,0.13,0.16)+0.03)

ggplot(m_HCT,aes(x=variable,y=Diff,group=variable))+
  geom_boxplot(aes(color=variable),fill="white",outlier.size = 0.2,flatten=0.1,size = 0.3)+
  stat_pvalue_manual(hct_test, label = "p.signif",xmin="group1",xmax="group2",size = 2)+
  geom_point(aes(color=variable),size=0.2)+
  scale_color_manual(values =colors_hct)+
  lims(y=c(-0.01,0.20))+
  theme_classic()+
  ylab(bquote(Delta~PSI~(Exon~Skipping)))+
  theme(legend.position = "none",
        axis.text=element_text(family="Arial",size=5, color="black"),
        axis.text.x=element_text(family="Arial",size=5, color="black",angle=90,hjust=1),
        axis.title = element_text(family="Arial",size=5, color="black"),
        axis.title.x = element_blank(),
        panel.background = element_blank(),
        plot.background = element_blank(), 
        panel.border = element_blank(),
        legend.background = element_blank())
ggsave("FigureS5/BIRCA_Splicing_1.pdf",width=1.2,height=1.2)


sh_test <- compare_means(Diff ~ variable,comparisons = colors_sh, p.adjust.method = "fdr", method='t.test', data = m_sh)
sh_test<-sh_test %>% mutate(y.position =0.35)

ggplot(m_sh,aes(x=variable,y=Diff))+
  geom_boxplot(aes(color=variable),fill="white",outlier.size = 0.3,flatten=0.1,size = 0.3)+
  stat_pvalue_manual(sh_test, label = "p.signif",xmin="group1",xmax="group2",size = 2)+
  geom_point(aes(color=variable),size=0.3)+
  scale_y_continuous(position = "right",limits = c(-0.01,0.4))+
  scale_color_manual(values =colors_sh)+
  theme_classic()+
  ylab(bquote(Delta~PSI~(Exon~Skipping)))+
  theme(legend.position = "none",
        axis.text=element_text(family="Arial",size=5, color="black"),
        axis.text.x=element_text(family="Arial",size=5, color="black",angle=90,hjust=1),
        axis.title = element_text(family="Arial",size=5, color="black"),
        axis.title.x = element_blank(),
        panel.background = element_blank(),
        plot.background = element_blank(), 
        panel.border = element_blank(),
        legend.background = element_blank(),
        axis.line.y.left = element_blank(),
        axis.ticks.y.left = element_blank(),
        axis.text.y.left = element_blank(),
        axis.title.y.left = element_blank(),
        )
ggsave("FigureS5/BIRCA_Splicing_2.pdf",width=0.8,height=1.2)
```

#Figure S4Q---PCYT2
```{r,fig.width=1.2, fig.height=1.2}
rm(list=ls())
PSI<-read.table("Figure4/Round3 RT-PCR txt/PYCT2_PSI.txt",header=T,sep="\t")


PSI$ID<-"PYCT2"
PSI_melt<-melt(PSI,id.vars = "ID")
PSI_melt$variable<-as.character(PSI_melt$variable)
PSI_melt$variable[which(PSI_melt$variable=="L100Q_1")]<-"L100Q-1"
PSI_melt$variable[which(PSI_melt$variable=="L100Q_2")]<-"L100Q-2"
PSI_melt$variable[which(PSI_melt$variable=="Silent_Edit")]<-"Silent"
PSI_melt$variable[which(PSI_melt$variable=="Het_KO")]<-"hetKO"
PSI_melt$variable<-sapply(as.character(PSI_melt$variable),function(x){strsplit(x,"[.]")[[1]][1]})
PSI_melt$variable<-factor(PSI_melt$variable,levels = c("Parent","Silent","L100Q-1","L100Q-2","hetKO","shCTRL","shPCBP1"))
PSI_melt$value<-as.numeric(PSI_melt$value)

m_HCT<-PSI_melt[which(!(PSI_melt$variable %in% c("shCTRL","shPCBP1"))),]
m_sh<-PSI_melt[which(PSI_melt$variable %in% c("shCTRL","shPCBP1")),]

#means
PSI_mean<-aggregate(value ~ variable, data = PSI_melt, FUN = base::mean)

mean_HCT<-PSI_mean[which(!(PSI_mean$variable %in% c("shCTRL","shPCBP1"))),]
mean_sh<-PSI_mean[which(PSI_mean$variable %in% c("shCTRL","shPCBP1")),]

m_HCT$Diff<-mean_HCT$value[which(mean_HCT$variable=="Parent")]-m_HCT$value
m_sh$Diff<-mean_sh$value[which(mean_sh$variable=="shCTRL")]-m_sh$value

comparisons_hct<-list(c("Parent","Silent"),c("Parent","L100Q-1"),c("Parent","L100Q-2"),c("Parent","hetKO"))
comparisons_sh<-list(c("shCTRL","shPCBP1"))

colors_hct<-c("Parent"=Parent_col,"Silent"=HDR_col,"L100Q-1"=L100_col,"L100Q-2"=L100_col2,"hetKO"=KO_col)
colors_sh<-c("shCTRL"="gray","shPCBP1"=KD_col)

hct_test <- compare_means(Diff ~ variable,comparisons = comparisons_hct, p.adjust.method = "fdr", method='t.test', data = m_HCT)
hct_test<-hct_test[which(hct_test$group1=="Parent"),]
hct_test<-hct_test %>% mutate(y.position = c(0.34,0.42,0.48,0.55))


ggplot(m_HCT,aes(x=variable,y=Diff,group=variable))+
  geom_boxplot(aes(color=variable),fill="white",outlier.size = 0.2,flatten=0.1,size = 0.3)+
  stat_pvalue_manual(hct_test, label = "p.signif",xmin="group1",xmax="group2",size = 2)+
  geom_point(aes(color=variable),size=0.05)+
  scale_color_manual(values =colors_hct)+
  #lims(y=c(-0.05,0.50))+
  theme_classic()+
  ylab(bquote(Delta~PSI~(Exon~Skipping)))+
  theme(legend.position = "none",
        axis.text=element_text(family="Arial",size=5, color="black"),
        axis.text.x=element_text(family="Arial",size=5, color="black",angle=90,hjust=1),
        axis.title = element_text(family="Arial",size=5, color="black"),
        axis.title.x = element_blank(),
        panel.background = element_blank(),
        plot.background = element_blank(), 
        panel.border = element_blank(),
        legend.background = element_blank())
ggsave("FigureS5/PCYT2_Splicing_1.pdf",width=1.2,height=1.2)


sh_test <- compare_means(Diff ~ variable,comparisons = comparisons_sh, p.adjust.method = "fdr", method='t.test', data = m_sh)
sh_test<-sh_test %>% mutate(y.position =0.45)

ggplot(m_sh,aes(x=variable,y=Diff))+
  geom_boxplot(aes(color=variable),fill="white",outlier.size = 0.3,flatten=0.1,size = 0.3)+
  stat_pvalue_manual(sh_test, label = "p.signif",xmin="group1",xmax="group2",size = 2)+
  geom_point(aes(color=variable),size=0.3)+
  scale_y_continuous(position = "right",limits = c(-0.07,0.5))+
  scale_color_manual(values =colors_sh)+
  theme_classic()+
  ylab(bquote(Delta~PSI~(Exon~Skipping)))+
  theme(legend.position = "none",
        axis.text=element_text(family="Arial",size=5, color="black"),
        axis.text.x=element_text(family="Arial",size=5, color="black",angle=90,hjust=1),
        axis.title = element_text(family="Arial",size=5, color="black"),
        axis.title.x = element_blank(),
        panel.background = element_blank(),
        plot.background = element_blank(), 
        panel.border = element_blank(),
        legend.background = element_blank(),
        axis.line.y.left = element_blank(),
        axis.ticks.y.left = element_blank(),
        axis.text.y.left = element_blank(),
        axis.title.y.left = element_blank(),
        )
ggsave("FigureS5/PCYT2_Splicing_2.pdf",width=0.8,height=1.2)
```

#Ov between binding and splicing changes
```{r}
rm(list=ls())
load("~/Desktop/Dominguez_Lab/PCBP1_FINAL/RNA-Seq/rMATS/HCT_rMATS.RData")
L1001<-HCT$Parent_L100Q$SE
L1002<-HCT$Parent_F10$SE
KO<-HCT$Parent_KO$SE

L1001<-L1001[which(L1001$FDR<0.05 & L1001$PValue<0.05 & abs(L1001$IncLevelDifference)>0.1 & L1001$Total_Count_1>50 & L1001$Total_Count_2>50),]
L1002<-L1002[which(L1002$FDR<0.05 & L1002$PValue<0.05 & abs(L1002$IncLevelDifference)>0.1 & L1002$Total_Count_1>50 & L1002$Total_Count_2>50),]
KO<-KO[which(KO$FDR<0.05 & KO$PValue<0.05 & abs(KO$IncLevelDifference)>0.1 & KO$Total_Count_1>50 & KO$Total_Count_2>50),]


bind_WT<-read.table("Figure3/Data/eCLIP/IDR/GG83_GG84_reprod_Meta.bed",sep = "\t")
bind_L100Q<-read.table("Figure3/Data/eCLIP/IDR/GG87_GG88_reprod_Meta.bed",sep = "\t")
bind_L100Q2<-read.table("Figure3/Data/eCLIP/IDR/GG93_GG94_reprod_Meta.bed",sep = "\t")
bind_HDR<-read.table("Figure3/Data/eCLIP/IDR/GG91_GG92_reprod_Meta.bed",sep = "\t")

all_bound<-c(unique(strsplit(paste(bind_WT$V5,collapse=","),",")[[1]]),
             unique(strsplit(paste(bind_L100Q$V5,collapse=","),",")[[1]]),
             unique(strsplit(paste(bind_L100Q2$V5,collapse=","),",")[[1]]),
             unique(strsplit(paste(bind_HDR$V5,collapse=","),",")[[1]]))

L1001$Bound<-ifelse(L1001$GeneID %in% all_bound,"Bound","Not Bound")
L1002$Bound<-ifelse(L1002$GeneID %in% all_bound,"Bound","Not Bound")
KO$Bound<-ifelse(KO$GeneID %in% all_bound,"Bound","Not Bound")

L1001_bound<-data.frame(table(L1001$Bound))
L1002_bound<-data.frame(table(L1002$Bound))
KO_bound<-data.frame(table(KO$Bound))


#L100 -pie
L1001_bound$fraction = L1001_bound$Freq / sum(L1001_bound$Freq)
L1001_bound$ymax = cumsum(L1001_bound$fraction)
L1001_bound$ymin = c(0, head(L1001_bound$ymax, n = -1))
L1001_bound$label_position = (L1001_bound$ymax + L1001_bound$ymin) / 2.5  # For text positioning
L1001_bound$Label<-paste0(L1001_bound$Var1,"\n",round(L1001_bound$fraction*100,digits=0),"%")

my_colors<-c("Bound"="#AE6BAB","Not Bound"="#C2C1C2")
ggplot(L1001_bound, aes(ymax = ymax, ymin = ymin, xmax = 1, xmin = 0, fill = Var1)) +
  geom_rect() +
  coord_polar(theta = "y") +
  theme_void() +
  scale_fill_manual(values = my_colors) + 
  geom_text(aes(x = 0.6, y = label_position, label = Label), size = 4,family="Arial") +
  theme(legend.position = "none")
ggsave("FIgureS5/L1001_bound_pie.pdf",width=2,height=2)


#L100 -pie
L1002_bound$fraction = L1002_bound$Freq / sum(L1002_bound$Freq)
L1002_bound$ymax = cumsum(L1002_bound$fraction)
L1002_bound$ymin = c(0, head(L1002_bound$ymax, n = -1))
L1002_bound$label_position = (L1002_bound$ymax + L1002_bound$ymin) / 2.5  # For text positioning
L1002_bound$Label<-paste0(L1002_bound$Var1,"\n",round(L1002_bound$fraction*100,digits=0),"%")

my_colors<-c("Bound"="#AE6BAB","Not Bound"="#C2C1C2")
ggplot(L1002_bound, aes(ymax = ymax, ymin = ymin, xmax = 1, xmin = 0, fill = Var1)) +
  geom_rect() +
  coord_polar(theta = "y") +
  theme_void() +
  scale_fill_manual(values = my_colors) + 
  geom_text(aes(x = 0.6, y = label_position, label = Label), size = 4,family="Arial") +
  theme(legend.position = "none")
ggsave("FIgureS5/L1002_bound_pie.pdf",width=2,height=2)

#KO -pie
KO_bound$fraction = KO_bound$Freq / sum(KO_bound$Freq)
KO_bound$ymax = cumsum(KO_bound$fraction)
KO_bound$ymin = c(0, head(KO_bound$ymax, n = -1))
KO_bound$label_position = (KO_bound$ymax + KO_bound$ymin) / 2.5  # For text positioning
KO_bound$Label<-paste0(KO_bound$Var1,"\n",round(KO_bound$fraction*100,digits=0),"%")

my_colors<-c("Bound"="#AE6BAB","Not Bound"="#C2C1C2")
ggplot(KO_bound, aes(ymax = ymax, ymin = ymin, xmax = 1, xmin = 0, fill = Var1)) +
  geom_rect() +
  coord_polar(theta = "y") +
  theme_void() +
  scale_fill_manual(values = my_colors) + 
  geom_text(aes(x = 0.6, y = label_position, label = Label), size = 4,family="Arial") +
  theme(legend.position = "none")
ggsave("FIgureS5/KO_bound_pie.pdf",width=2,height=2)

#Overlaping in all
ovs<-

```


#Translation Supp-S5

#Trace
```{r,fig.width=3, fig.height=1.5}
rm(list=ls())
df<-read.table("Figure5/Data/polysometrace.txt",sep="\t",header=T)

df_melt<-reshape2::melt(df[c("X","Snaps","WT.A","GFP.A","L100Q.A")],id.vars=c("X","Snaps"))
df_melt$variable<-sapply(as.character(df_melt$variable),function(x){strsplit(x,"[.]")[[1]][1]})

min<-df[c("X","Snaps")] %>% group_by(X) %>% summarise(min_value = min(Snaps)) %>% data.frame()
max<-df[c("X","Snaps")] %>% group_by(X) %>% summarise(min_value = max(Snaps)) %>% data.frame()
box<-merge(min,max,by="X")
box$Col<-"00000000"
box$Col[which(box$X==5)]<-"#BFE0DB"
box$Col[which(box$X==7)]<-"#BFE0DB"
box$Col[which(box$X==10)]<-"#C5D4D6"
box$Col[which(box$X==11)]<-"#B4C4CD"
box$Col[which(box$X==12)]<-"#B3BECC"
box$Col[which(box$X==15)]<-"#B2B0C4"
box$Col[which(box$X==16)]<-"#B5A3B4"
box$Col[which(box$X==17)]<-"#B596A0"
box$Label<-ifelse(box$X %in% c(5,7,10,11,12,15,16,17),paste0("F",box$X),NA)


ggplot()+
  geom_rect(inherit.aes = F,data=box,aes(xmin = min_value.x,ymin = -1,xmax=min_value.y,ymax=4,fill=Col),alpha=0.7)+
  scale_fill_identity()+
  geom_text(inherit.aes = F,data=box,aes(x = (min_value.x+min_value.y)/2,y=3.8,label=Label),size=1.5)+
  geom_line(data=df_melt,aes(x=Snaps,y=value,group=variable,color=variable))+
  scale_color_manual(values=c("WT"=Parent_col,"GFP"=GFP_col,"L100Q"=L100_col))+
  lims(y=c(-1,4))+
  theme_classic()+
  theme(legend.position = c(0.08,0.15),
        axis.title = element_blank(),
        legend.text = element_text(family="Arial",size=4, color="black"),
        legend.title = element_blank(),
        panel.background = element_blank(),
        plot.background = element_blank(), 
        panel.border = element_blank(),
        legend.background = element_blank(),
        axis.ticks = element_blank(),
        axis.text=element_blank(),
        legend.key.size = unit(0.2, "cm"))
ggsave("Translation_Figure/Trace.pdf",width=3,height=1.5)

```

#eCLIP_LFC
```{r}
rm(list=ls())
WT<-read.table("../Omics-data/Binding/PCBP1/eCLIP/C2BB/WT_Meta_C2_IDR.bed",sep = "\t")
L100Q<-read.table("../Omics-data/Binding/PCBP1/eCLIP/C2BB/Mut_Meta_C2_IDR.bed",sep = "\t")

test<-ks.test(WT$V7,L100Q$V7)
test

df<-rbind(data.frame("Group"="WT","Val"=WT$V7),data.frame("Group"="L100Q","Val"=L100Q$V7))
df$Group<-factor(df$Group,levels=c("WT","L100Q"))

ggplot(df,aes(x = Val,color=Group))+
  stat_ecdf()+
  scale_color_manual(values = c("WT" =Parent_col, "L100Q" =L100_col))+
  annotate("text", x = 5.2, y = .92, label = bquote(italic(P)<2.2e-16), color = "black", size = 2, family = "Arial") + 
  theme_classic()+
  labs(x="Peak Enrichment",y="ecdf")+
  theme(legend.position = c(.8,.15),
        legend.key.size = unit(0.2, "cm"),
        legend.spacing.y = unit(-0.15, "cm"),
        axis.text=element_text(family="Arial",size=6, color="black"),
        axis.title = element_text(family="Arial",size=6, color="black"),
        legend.text = element_text(family="Arial",size=6, color="black"),
        legend.title = element_blank(),
        panel.background = element_blank(),
        plot.background = element_blank(), 
        panel.border = element_blank(),
        legend.background = element_blank())
ggsave("Translation_Figure/eCLIP_LFC.pdf",width=1.8,height=1.5)

```

#eCLIP_numPeaks
```{r}
rm(list=ls())
WT<-read.table("../Omics-data/Binding/PCBP1/eCLIP/C2BB/WT_Meta_C2_IDR.bed",sep = "\t")
L100Q<-read.table("../Omics-data/Binding/PCBP1/eCLIP/C2BB/Mut_Meta_C2_IDR.bed",sep = "\t")

df<-rbind(data.frame("Group"="WT","Val"=nrow(WT)),data.frame("Group"="L100Q","Val"=nrow(L100Q)))
df$Group<-factor(df$Group,levels=c("WT","L100Q"))

ggplot(df, aes(x=Group, y=Val, fill=Group)) + 
  geom_bar(stat="identity", color="black", position=position_dodge(),width=0.8,alpha=0.9) +
  theme_classic()+
  scale_fill_manual(values = c("WT" =Parent_col, "L100Q" =L100_col))+
  labs(y="No. of Peaks")+
  theme(legend.position = "none",
        axis.text=element_text(family="Arial",size=6, color="black"),
        axis.text.x=element_text(family="Arial",size=6, color="black"),
        axis.title = element_text(family="Arial",size=6, color="black"),
        axis.title.x=element_blank(),
        strip.text.x = element_text(family="Arial",size=6, color="black"),
        panel.background = element_blank(),
        plot.background = element_blank(), 
        panel.border = element_blank(),
        legend.background = element_blank())
ggsave("FIgureS5/FigS5S.pdf",width=1.2,height=1.5)

```













#Figure S4N
```{r,fig.width=4, fig.height=1.5}
rm(list=ls())
df<-read.table("Figure5/Data/Polysome_TPM.txt",header=T)
rownames(df)<-df$Genes
df<-df[,-42]

#getting names
sample<-paste("a",1:42,sep="")
fraction<-factor(rep(c("F5","F10","F11","F12","F15","F16","F17"),6),
                  levels=c("F5","F10","F11","F12","F15","F16","F17"))
condition<-factor(c(rep("WT",14),rep("L100Q",14),rep("GFP",14)),levels=c("GFP","WT","L100Q"))
Rep<-rep(c(rep(1,7),rep(2,7)),3)
sampleInfo<-data.frame(sample,fraction,condition,Rep)
sampleInfo$Identifier<-paste(sampleInfo$fraction,sampleInfo$condition,sampleInfo$Rep,sep="_")
sampleInfo<-sampleInfo[which(sampleInfo$sample!="a22"),]
sampleInfo
table(colnames(df)==sampleInfo$sample)

#renaming
colnames(df)<-sampleInfo$Identifier
Sums<-rowSums(df, na.rm = TRUE)
df_sub<-df[order(Sums,decreasing = T)[1:1000],]

df_t <- t(df_sub)
df_t <- df_t[, apply(df_t, 2, function(x) sd(x) != 0)]
df_scaled <- prcomp(df_t, center = TRUE, scale. = TRUE)

pca_df <- data.frame(df_scaled$x)
pca_df$Fraction<-sapply(rownames(pca_df),function(x){strsplit(x,"_")[[1]][1]})
pca_df$Condition<-sapply(rownames(pca_df),function(x){strsplit(x,"_")[[1]][2]})
pca_df$Fraction<-factor(pca_df$Fraction,levels=c("F5","F10","F11","F12","F15","F16","F17"))

library(ggplot2)
g1<-ggplot(pca_df, aes(x = PC1, y = PC2,color=Fraction)) +
  geom_point() +
  theme_classic() +
  labs( x = "PC1", y = "PC2")+
  scale_color_manual(values=c("F5"="#BFE0DB","F10"="#C5D4D6","F11"="#B4C4CD","F12"="#B3BECC","F15"="#B2B0C4","F16"="#B5A3B4","F17"="#B596A0"))+
  theme(legend.position = c(0.5,0.75),
        axis.text=element_text(family="Arial",size=6, color="black"),
        axis.title = element_text(family="Arial",size=6, color="black"),
        legend.text = element_text(family="Arial",size=6, color="black"),
        axis.title.x=element_blank(),
        panel.background = element_blank(),
        plot.title = element_blank(),
        plot.background = element_blank(), 
        panel.border = element_blank(),
        legend.background = element_blank(),
        legend.title=element_blank(),
        legend.key.width= unit(0.2, 'cm'),
        legend.key.height= unit(0.2, 'cm'))

g2<-ggplot(pca_df, aes(x = PC1, y = PC2,color=Condition)) +
  geom_point() +
  theme_classic() +
  labs( x = "PC1", y = "PC2")+
  scale_color_manual(values=c("GFP"=GFP_col,"WT"=Parent_col,"L100Q"=L100_col))+
  theme(legend.position = c(0.5,0.9),
        axis.text=element_text(family="Arial",size=6, color="black"),
        axis.title = element_text(family="Arial",size=6, color="black"),
        legend.text = element_text(family="Arial",size=6, color="black"),
        axis.title.x=element_blank(),
        panel.background = element_blank(),
        plot.title = element_blank(),
        plot.background = element_blank(), 
        panel.border = element_blank(),
        legend.background = element_blank(),
        legend.title=element_blank(),
        legend.key.width= unit(0.2, 'cm'),
        legend.key.height= unit(0.2, 'cm'))

g<-ggarrange(g1,g2)
g
ggsave("FIgureS5/Polysome_QC.pdf",g,width=4,height=1.5)
```


#Figure S4U
```{r}
rm(list=ls())
WT<-read.table("../Omics-data/Binding/PCBP1/eCLIP/C2BB/WT_Meta_C2_IDR.bed",sep = "\t")
L100Q<-read.table("../Omics-data/Binding/PCBP1/eCLIP/C2BB/Mut_Meta_C2_IDR.bed",sep = "\t")

CE<-list("WT"=WT$V5,"L100Q"=L100Q$V5)
L100<-ggvenn::ggvenn(CE,fill_color=c(Parent_col,L100_col),set_name_size=3,show_percentage=F,text_size=2,fill_alpha=0.5,stroke_size=0.5)+
  coord_cartesian(ylim = c(-1.2, 1.5))+
  theme(legend.position = "none",
        panel.background = element_blank(),
        plot.background = element_blank(),
        panel.border = element_blank(),
        legend.background = element_blank(),
        axis.title = element_text(family="Arial",size=0, color="black"),
        axis.text=element_text(family="Arial",size=0, color="black"))
L100
ggsave("FIgureS5/FigS5U.pdf",width=1.15,height=0.84)

```

#Changes on common bound
```{r}
rm(list=ls())
poly<-read.table("Figure5/Data/Polysome/LFC_by_conditions.txt")
prot<-read.csv("../Omics-data/Proteomics/C2BB/250415_DominguezLab_TotalProteome_Imputation_Normalized_candidates.csv")
prot$ensg<-mapIds(org.Hs.eg.db,keys = prot$Genes,column = "ENSEMBL",keytype="SYMBOL",multiVals = "first")

#bound
L100_bound<-read.table("../Omics-data/Binding/PCBP1/eCLIP/C2BB/Mut_Meta_C2_IDR.bed",sep="\t")
WT_bound<-read.table("../Omics-data/Binding/PCBP1/eCLIP/C2BB/WT_Meta_C2_IDR.bed",sep="\t")
L100_bound$Region<-sapply(L100_bound$V4,function(x){strsplit(x,"_")[[1]][2]})
WT_bound$Region<-sapply(WT_bound$V4,function(x){strsplit(x,"_")[[1]][2]})
all_bound_genes<-union(strsplit(paste(L100_bound$V5,collapse=","),",")[[1]],strsplit(paste(WT_bound$V5,collapse=","),",")[[1]])

#looking at sig changes
poly<-poly[which(rownames(poly) %in% all_bound_genes),]
poly$Genes<-rownames(poly)
poly_LFC<-reshape2::melt(poly[c(grep("log2FoldChange",colnames(poly),value=T),"Genes")],id.vars="Genes")
poly_pval<-reshape2::melt(poly[c(grep("padj",colnames(poly),value=T),"Genes")],id.vars="Genes")

poly_LFC$Fraction<-sapply(as.character(poly_LFC$variable),function(x){strsplit(x,"[.]")[[1]][1]})
poly_pval$Fraction<-sapply(as.character(poly_pval$variable),function(x){strsplit(x,"[.]")[[1]][1]})

poly_LFC$Condition<-sapply(as.character(poly_LFC$variable),function(x){strsplit(x,"[.]")[[1]][2]})
poly_pval$Condition<-sapply(as.character(poly_pval$variable),function(x){strsplit(x,"[.]")[[1]][2]})

colnames(poly_LFC)[3]<-"LFC"
colnames(poly_pval)[3]<-"FDR"

df<-cbind(poly_LFC,poly_pval$FDR)
df_sub<-df[which(df$`poly_pval$FDR`<0.05),]
df_sub<-df_sub[which(abs(df_sub$LFC)>1),]

table(df_sub$Fraction,df_sub$Condition,df_sub$LFC>0)

changes_by_fraction<-data.frame(table(df_sub$Fraction,df_sub$Condition,df_sub$LFC>0))
changes_by_fraction$Var1<-factor(changes_by_fraction$Var1,levels=c("F5","F10","F11","F12","F15","F16","F17"))

ggplot(changes_by_fraction[which(changes_by_fraction$Var3==TRUE),], aes(x = Var1, y = Freq, fill = Var2)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(x = "Fractions", y = "No. of Significant Changes") +
  scale_fill_manual(values=c("L100Q"=L100_col,"WT"=Parent_col))+
  theme_classic()+
  theme(legend.position = c(0.9,0.9),
        axis.text.x=element_text(family="Arial",size=6, color="black"),
        axis.text.y=element_text(family="Arial",size=6, color="black"),
        axis.title.y = element_text(family="Arial",size=6, color="black"),
        legend.text = element_text(family="Arial",size=6, color="black"),
        axis.title.x =  element_blank(),
        legend.title=element_blank(),
        panel.background = element_blank(),
        plot.background = element_blank(),
        legend.key.size = unit(0.2, "cm"),
        legend.spacing.y = unit(-0.15, "cm"),
        legend.background = element_blank())
ggsave("Figure5/Polysome_changes_L100Q_unique.pdf",width=2.5,height=1.5)
```

#Changes on common LFC
```{r}
rm(list=ls())
poly<-read.table("Figure5/Data/Polysome/LFC_by_conditions.txt")
prot<-read.csv("../Omics-data/Proteomics/C2BB/250415_DominguezLab_TotalProteome_Imputation_Normalized_candidates.csv")
prot$ensg<-mapIds(org.Hs.eg.db,keys = prot$Genes,column = "ENSEMBL",keytype="SYMBOL",multiVals = "first")

#bound
L100_bound<-read.table("../Omics-data/Binding/PCBP1/eCLIP/C2BB/Mut_Meta_C2_IDR.bed",sep="\t")
WT_bound<-read.table("../Omics-data/Binding/PCBP1/eCLIP/C2BB/WT_Meta_C2_IDR.bed",sep="\t")
L100_bound$Region<-sapply(L100_bound$V4,function(x){strsplit(x,"_")[[1]][2]})
WT_bound$Region<-sapply(WT_bound$V4,function(x){strsplit(x,"_")[[1]][2]})
all_bound_genes<-intersect(L100_bound$V5,WT_bound$V5)

#looking at sig changes
poly<-poly[which(rownames(poly) %in% all_bound_genes),]
poly$Genes<-rownames(poly)
poly_LFC<-reshape2::melt(poly[c(grep("log2FoldChange",colnames(poly),value=T),"Genes")],id.vars="Genes")
poly_pval<-reshape2::melt(poly[c(grep("padj",colnames(poly),value=T),"Genes")],id.vars="Genes")

poly_LFC$Fraction<-sapply(as.character(poly_LFC$variable),function(x){strsplit(x,"[.]")[[1]][1]})
poly_pval$Fraction<-sapply(as.character(poly_pval$variable),function(x){strsplit(x,"[.]")[[1]][1]})

poly_LFC$Condition<-sapply(as.character(poly_LFC$variable),function(x){strsplit(x,"[.]")[[1]][2]})
poly_pval$Condition<-sapply(as.character(poly_pval$variable),function(x){strsplit(x,"[.]")[[1]][2]})

colnames(poly_LFC)[3]<-"LFC"
colnames(poly_pval)[3]<-"FDR"

df<-cbind(poly_LFC,poly_pval$FDR)
WT<-df[which(df$Condition=="WT"),]
L100Q<-df[which(df$Condition=="L100Q"),]

comb_cond<-merge(WT,L100Q,by=c("Genes","Fraction"))
comb_cond<-comb_cond[c("Genes","Fraction","LFC.x","LFC.y","poly_pval$FDR.x","poly_pval$FDR.y")]
colnames(comb_cond)<-c("Genes","Fraction","LFC.WT","LFC.L100Q","pval_WT","pval_L100Q")

comb_cond<-comb_cond[(abs(comb_cond$LFC.WT)>1 & comb_cond$pval_WT<0.05) | (abs(comb_cond$LFC.L100Q)>1 & comb_cond$pval_L100Q<0.05),]
comb_cond_melt<-reshape2::melt(comb_cond[c("Fraction","LFC.WT","LFC.L100Q")],id.vars = "Fraction")

comb_cond_melt$variable<-gsub("LFC.","",comb_cond_melt$variable)
comb_cond_melt$variable<-factor(comb_cond_melt$variable,levels=c("WT","L100Q"))
comb_cond_melt<-comb_cond_melt[which(comb_cond_melt$Fraction!="F5"),]
comb_cond_melt$Fraction<-factor(comb_cond_melt$Fraction,levels=c("F5","F10","F11","F12","F15","F16","F17"))

ggplot(comb_cond_melt,aes(x=variable,y=abs(value),color=variable))+
  geom_violin(outlier.size = 0.5)+
  geom_boxplot(width = 0.1, outlier.shape = NA)+
  scale_color_manual(values=c("WT"=Parent_col,"L100Q"=L100_col))+
  stat_compare_means(comparisons = list(c("WT","L100Q")), label.y = c(3.3),label="p.signif",method = "wilcox.test")+
  facet_wrap(~Fraction,ncol = 6,nrow=1)+
  lims(y=c(0,4))+
  labs(y="Abs. LFC / GFP")+
  theme_classic()+
    theme(legend.position = "none",
          strip.text = element_text(size = 6, margin = margin(1, 1, 1.5, 1.5)),
        axis.text.x=element_text(family="Arial",size=6, color="black"),
        axis.text.y=element_text(family="Arial",size=6, color="black"),
        axis.title.y = element_text(family="Arial",size=6, color="black"),
        legend.text = element_text(family="Arial",size=6, color="black"),
        axis.title.x =  element_blank(),
        legend.title=element_blank(),
        panel.background = element_blank(),
        plot.background = element_blank(),
        legend.key.size = unit(0.2, "cm"),
        legend.spacing.y = unit(-0.15, "cm"),
        legend.background = element_blank())
ggsave("FigureS5/Polysome_LFC_common.pdf",width=4,height=1.5)
  

```

#Percent of Bound Genes
```{r}
rm(list=ls())
poly<-read.table("Figure5/Data/Polysome/LFC_by_conditions.txt")
prot<-read.csv("../Omics-data/Proteomics/C2BB/250415_DominguezLab_TotalProteome_Imputation_Normalized_candidates.csv")
prot$ensg<-mapIds(org.Hs.eg.db,keys = prot$Genes,column = "ENSEMBL",keytype="SYMBOL",multiVals = "first")

#bound
L100_bound<-read.table("../Omics-data/Binding/PCBP1/eCLIP/C2BB/Mut_Meta_C2_IDR.bed",sep="\t")
WT_bound<-read.table("../Omics-data/Binding/PCBP1/eCLIP/C2BB/WT_Meta_C2_IDR.bed",sep="\t")
L100_bound$Region<-sapply(L100_bound$V4,function(x){strsplit(x,"_")[[1]][2]})
WT_bound$Region<-sapply(WT_bound$V4,function(x){strsplit(x,"_")[[1]][2]})
all_bound_genes<-union(WT_bound$V5,L100_bound$V5)
WT_unique<-setdiff(WT_bound$V5,L100_bound$V5)
L100Q_unique<-setdiff(L100_bound$V5,WT_bound$V5)
common<-intersect(WT_bound$V5,L100_bound$V5)

#looking at sig changes
poly$Genes<-rownames(poly)
poly_LFC<-reshape2::melt(poly[c(grep("log2FoldChange",colnames(poly),value=T),"Genes")],id.vars="Genes")
poly_pval<-reshape2::melt(poly[c(grep("padj",colnames(poly),value=T),"Genes")],id.vars="Genes")

poly_LFC$Fraction<-sapply(as.character(poly_LFC$variable),function(x){strsplit(x,"[.]")[[1]][1]})
poly_pval$Fraction<-sapply(as.character(poly_pval$variable),function(x){strsplit(x,"[.]")[[1]][1]})

poly_LFC$Condition<-sapply(as.character(poly_LFC$variable),function(x){strsplit(x,"[.]")[[1]][2]})
poly_pval$Condition<-sapply(as.character(poly_pval$variable),function(x){strsplit(x,"[.]")[[1]][2]})

colnames(poly_LFC)[3]<-"LFC"
colnames(poly_pval)[3]<-"FDR"

df<-merge(poly_LFC,poly_pval,by=c("Genes","Condition","Fraction"))
df<-df[which(df$FDR<0.05 & abs(df$LFC)>1),]
changed_genes<-unique(df$Genes)

Ov<-data.frame("Group"=c("WT","L100Q"),"Ov"=c(length(intersect(changed_genes,WT_bound$V5)),length(intersect(changed_genes,L100_bound$V5))))
Ov$Ov<-Ov$Ov/length(changed_genes)
Ov$Group<-factor(Ov$Group,levels=c("WT","L100Q"))
ggplot(Ov, aes(x=Group, y=Ov*100, fill=Group)) + 
  geom_bar(stat="identity", color="black", position=position_dodge(),width=0.8,alpha=0.9) +
  theme_classic()+
  scale_fill_manual(values = c("WT" =Parent_col, "L100Q" =L100_col))+
  labs(y="% of Regulated Genes Bound")+
  theme(legend.position = "none",
        axis.text=element_text(family="Arial",size=6, color="black"),
        axis.text.x=element_text(family="Arial",size=6, color="black"),
        axis.title = element_text(family="Arial",size=6, color="black"),
        axis.title.x=element_blank(),
        strip.text.x = element_text(family="Arial",size=6, color="black"),
        panel.background = element_blank(),
        plot.background = element_blank(), 
        panel.border = element_blank(),
        legend.background = element_blank())
ggsave("FIgureS5/Reg_Bound_ov.pdf",width=1.2,height=1.5)


```

```{r}
rm(list=ls())
poly<-read.table("Figure5/Data/Polysome/LFC_by_conditions.txt")
prot<-read.csv("../Omics-data/Proteomics/C2BB/250415_DominguezLab_TotalProteome_Imputation_Normalized_candidates.csv")
prot$ensg<-mapIds(org.Hs.eg.db,keys = prot$Genes,column = "ENSEMBL",keytype="SYMBOL",multiVals = "first")

#bound
L100_bound<-read.table("../Omics-data/Binding/PCBP1/eCLIP/C2BB/Mut_Meta_C2_IDR.bed",sep="\t")
WT_bound<-read.table("../Omics-data/Binding/PCBP1/eCLIP/C2BB/WT_Meta_C2_IDR.bed",sep="\t")
L100_bound$Region<-sapply(L100_bound$V4,function(x){strsplit(x,"_")[[1]][2]})
WT_bound$Region<-sapply(WT_bound$V4,function(x){strsplit(x,"_")[[1]][2]})
WT_unique<-setdiff(WT_bound$V5,L100_bound$V5)
L100Q_unique<-setdiff(L100_bound$V5,WT_bound$V5)
common<-intersect(WT_bound$V5,L100_bound$V5)

#looking at sig changes
poly$Genes<-rownames(poly)
poly_LFC<-reshape2::melt(poly[c(grep("log2FoldChange",colnames(poly),value=T),"Genes")],id.vars="Genes")
poly_pval<-reshape2::melt(poly[c(grep("padj",colnames(poly),value=T),"Genes")],id.vars="Genes")

poly_LFC$Fraction<-sapply(as.character(poly_LFC$variable),function(x){strsplit(x,"[.]")[[1]][1]})
poly_pval$Fraction<-sapply(as.character(poly_pval$variable),function(x){strsplit(x,"[.]")[[1]][1]})

poly_LFC$Condition<-sapply(as.character(poly_LFC$variable),function(x){strsplit(x,"[.]")[[1]][2]})
poly_pval$Condition<-sapply(as.character(poly_pval$variable),function(x){strsplit(x,"[.]")[[1]][2]})

colnames(poly_LFC)[3]<-"LFC"
colnames(poly_pval)[3]<-"FDR"

df<-merge(poly_LFC,poly_pval,by=c("Genes","Condition","Fraction"))
df<-df[which(df$FDR<0.05 & abs(df$LFC)>1),]

df_sub<-df[which(df$Condition=="L100Q"),]
wt_sub<-df[which(df$Condition=="WT"),]
df_sub<-df_sub[which(!(df_sub$Genes %in% wt_sub$Genes)),]
df_sub<-df_sub[which(df_sub$Fraction %in% c("F15","F16","F17")),]
table(df_sub$LFC<0,df_sub$Fraction)

mut_changed<-unique(df$Genes[which(df$Condition=="L100Q")])
wt_changed<-unique(df$Genes[which(df$Condition=="WT")])

mut_spec<-setdiff(mut_changed,wt_changed)
#mut_spec<-mut_spec[which(mut_spec %in% L100_bound$V5)]

go<-enrichGO(gene          = mut_spec,
                  OrgDb         = org.Hs.eg.db,
                  keyType       = 'ENSEMBL',
                  ont           = "BP",
                  universe     = rownames(poly),
                  pAdjustMethod = "BH",
                  pvalueCutoff  = 0.05,
                  qvalueCutoff  = 0.05)

go@result<-go@result[which(go@result$ID %in% c("GO:0031623","GO:0007015","GO:0001837","GO:0045216","GO:0045216")),]
dotplot(go,font.size = 8)+
  scale_size_area(max_size = 3)+
  theme_classic()+
  theme(legend.position = "right",
        axis.text=element_text(family="Arial",size=8, color="black"),
        axis.text.x=element_text(family="Arial",size=8, color="black"),
        axis.title = element_text(family="Arial",size=8, color="black"),
        panel.background = element_blank(),
        plot.background = element_blank(), 
        legend.background = element_blank(),
        legend.key.size = unit(0.3, "cm"))
ggsave("FigureS5/Mut_reg_poly.pdf",width=4,height=2)


```


#S5

#S5Survival_Male
```{r}
rm(list=ls())
df<-read.table("Figure6/L100Q Mouse/Survival/survival_male.txt",sep="\t",header=T)
df<-df[,c(2:4)]
df_melt<-reshape2::melt(df,id.vars = "Days.elapsed")


surv_obj <- Surv(time = df_melt$Days.elapsed, event = df_melt$value)
fit <- survfit(surv_obj ~ variable, data = df_melt)

# Plot the survival curve using ggsurvplot (ggplot2-based)
ggsurvplot(fit,
           data = df_melt,
           pval = TRUE,
           pval.size = 2,
           conf.int = F,       
           risk.table = F,
           legend = "none",
           ggtheme = theme_classic(base_family = "Arial",base_size = 6),  # ggplot2 theme
           palette = c(Parent_col,"#921A1D"), # Custom colors
           legend.labs = c("WT","L100Q"),size=0.5)

ggsave("Figure6/Fig6H-Male.pdf",width=1.8,height=1)

```

```{r}
rm(list=ls())
df<-read.table("Figure6/L100Q Mouse/Survival/survival_female.txt",sep="\t",header=T)
df<-df[,c(2:4)]
df_melt<-reshape2::melt(df,id.vars = "Days.elapsed")


surv_obj <- Surv(time = df_melt$Days.elapsed, event = df_melt$value)
fit <- survfit(surv_obj ~ variable, data = df_melt)

# Plot the survival curve using ggsurvplot (ggplot2-based)
ggsurvplot(fit,
           data = df_melt,
           pval = TRUE,
           pval.size = 2,
           conf.int = F,       
           risk.table = F,
           legend = "none",
           ggtheme = theme_classic(base_family = "Arial",base_size = 6),  # ggplot2 theme
           palette = c(Parent_col,"#921A1D"), # Custom colors
           legend.labs = c("WT","L100Q"),size=0.5)

ggsave("Figure6/Fig6H-Female.pdf",width=1.8,height=1)

```

#blood counts

#Hemo
```{r,fig.width=1, fig.height=1.2}
rm(list=ls())
df<-read.table("FIgureS5/blood_counts/hemoglobin.txt",header=T,sep="\t")
df_melt<-melt(df)
df_melt$variable<-gsub("[.]","/",df_melt$variable)
Parent_col<-"#0096FE"
L100_col<-"#FF2600"
test <- compare_means(value ~ variable,comparisons = c("wt/wt","L100Q/wt"), p.adjust.method = "fdr", method='t.test', data = df_melt)
test
test<-test %>% mutate(y.position = 11)
df_melt$variable<-factor(df_melt$variable,levels=c("wt/wt","L100Q/wt"))

ggplot(df_melt,aes(x=variable,y=value,group=variable))+
  geom_boxplot(aes(color=variable),fill="white",outlier.size = 0.2,flatten=0.1,size = 0.3)+
  stat_pvalue_manual(test, label = "p.signif",xmin="group1",xmax="group2",size = 2)+
  geom_point(aes(color=variable),size=0.2)+
  scale_color_manual(values =c("wt/wt"=Parent_col,"L100Q/wt"=L100_col))+
  lims(y=c(0,12))+
  theme_classic()+
  ylab("Hemoglobin (g/dL)")+
  theme(legend.position = "none",
        axis.text=element_text(family="Arial",size=6, color="black"),
        axis.text.x=element_text(family="Arial",size=6, color="black",angle=45,hjust=1),
        axis.title = element_text(family="Arial",size=6, color="black"),
        axis.title.x = element_blank(),
        panel.background = element_blank(),
        plot.background = element_blank(), 
        panel.border = element_blank(),
        legend.background = element_blank())
ggsave("FigureS6/Hemoglobin_Count.pdf",height=1.5,width=1)

```

#Platlets
```{r,fig.width=1, fig.height=1.2}
rm(list=ls())
df<-read.table("FIgureS5/blood_counts/Platlets.txt",header=T,sep="\t")
df_melt<-melt(df)
df_melt$variable<-gsub("[.]","/",df_melt$variable)
Parent_col<-"#0096FE"
L100_col<-"#FF2600"
test <- compare_means(value ~ variable,comparisons = c("wt/wt","L100Q/wt"), p.adjust.method = "fdr", method='t.test', data = df_melt)
test
test<-test %>% mutate(y.position = 1300)
df_melt$variable<-factor(df_melt$variable,levels=c("wt/wt","L100Q/wt"))

ggplot(df_melt,aes(x=variable,y=value,group=variable))+
  geom_boxplot(aes(color=variable),fill="white",outlier.size = 0.2,flatten=0.1,size = 0.3)+
  stat_pvalue_manual(test, label = "p.signif",xmin="group1",xmax="group2",size = 2)+
  geom_point(aes(color=variable),size=0.2)+
  scale_color_manual(values =c("wt/wt"=Parent_col,"L100Q/wt"=L100_col))+
  lims(y=c(0,1500))+
  theme_classic()+
  ylab(quote("Platelets (10^3/" * mu * "L)"))+
  theme(legend.position = "none",
        axis.text=element_text(family="Arial",size=6, color="black"),
        axis.text.x=element_text(family="Arial",size=6, color="black",angle=45,hjust=1),
        axis.title = element_text(family="Arial",size=6, color="black"),
        axis.title.x = element_blank(),
        panel.background = element_blank(),
        plot.background = element_blank(), 
        panel.border = element_blank(),
        legend.background = element_blank())
ggsave("Figures6/Platlets_Count.pdf",height=1.5,width=1)

```

#RBC
```{r,fig.width=1, fig.height=1.2}
rm(list=ls())
df<-read.table("FIgureS5/blood_counts/RBC.txt",header=T,sep="\t")
df_melt<-melt(df)
df_melt$variable<-gsub("[.]","/",df_melt$variable)
Parent_col<-"#0096FE"
L100_col<-"#FF2600"

test <- compare_means(value ~ variable,comparisons = c("wt/wt","L100Q/wt"), p.adjust.method = "fdr", method='t.test', data = df_melt)
test
test<-test %>% mutate(y.position = 7.8)
df_melt$variable<-factor(df_melt$variable,levels=c("wt/wt","L100Q/wt"))

ggplot(df_melt,aes(x=variable,y=value,group=variable))+
  geom_boxplot(aes(color=variable),fill="white",outlier.size = 0.2,flatten=0.1,size = 0.3)+
  stat_pvalue_manual(test, label = "p.signif",xmin="group1",xmax="group2",size = 2)+
  geom_point(aes(color=variable),size=0.2)+
  scale_color_manual(values =c("wt/wt"=Parent_col,"L100Q/wt"=L100_col))+
  lims(y=c(0,8))+
  theme_classic()+
  ylab(quote("RBCs (10^6/" * mu * "L)"))+
  theme(legend.position = "none",
        axis.text=element_text(family="Arial",size=6, color="black"),
        axis.text.x=element_text(family="Arial",size=6, color="black",angle=45,hjust=1),
        axis.title = element_text(family="Arial",size=6, color="black"),
        axis.title.x = element_blank(),
        panel.background = element_blank(),
        plot.background = element_blank(), 
        panel.border = element_blank(),
        legend.background = element_blank())
ggsave("FigureS6/RBC_Count.pdf",height=1.5,width=1)

```

#WBC
```{r,fig.width=1, fig.height=1.2}
rm(list=ls())
df<-read.table("FIgureS5/blood_counts/WBC.txt",header=T,sep="\t")
df_melt<-melt(df)
df_melt$variable<-gsub("[.]","/",df_melt$variable)
Parent_col<-"#0096FE"
L100_col<-"#FF2600"

test <- compare_means(value ~ variable,comparisons = c("wt/wt","L100Q/wt"), p.adjust.method = "fdr", method='t.test', data = df_melt)
test
test<-test %>% mutate(y.position = 5)
df_melt$variable<-factor(df_melt$variable,levels=c("wt/wt","L100Q/wt"))

ggplot(df_melt,aes(x=variable,y=value,group=variable))+
  geom_boxplot(aes(color=variable),fill="white",outlier.size = 0.2,flatten=0.1,size = 0.3)+
  stat_pvalue_manual(test, label = "p.signif",xmin="group1",xmax="group2",size = 2)+
  geom_point(aes(color=variable),size=0.2)+
  scale_color_manual(values =c("wt/wt"=Parent_col,"L100Q/wt"=L100_col))+
  lims(y=c(0,6))+
  theme_classic()+
  ylab(quote("WBCs (10^3/" * mu * "L)"))+
  theme(legend.position = "none",
        axis.text=element_text(family="Arial",size=6, color="black"),
        axis.text.x=element_text(family="Arial",size=6, color="black",angle=45,hjust=1),
        axis.title = element_text(family="Arial",size=6, color="black"),
        axis.title.x = element_blank(),
        panel.background = element_blank(),
        plot.background = element_blank(), 
        panel.border = element_blank(),
        legend.background = element_blank())
ggsave("FigureS6/WBC_Count.pdf",height=1.5,width=1)

```

```{r}
rm(list=ls())
df<-read.csv("~/Desktop/KH1-KH2 Per cell nuc over perinuclear mean intensity.csv",header=T)

means<-data.frame(colMeans(df,na.rm = T))
means$Group<-"WT"
means$Group[which(rownames(means) %in% c("L100Q.Rep.1","L100Q.Rep.2","L100Q.Rep.3"))]<-"L100Q"
colnames(means)<-c("Mean","Group")

df_melt<-melt(df)
df_melt$Group<-"WT"
df_melt$Group[which(df_melt$variable %in% c("L100Q.Rep.1","L100Q.Rep.2","L100Q.Rep.3"))]<-"L100Q"
df_melt$Group<-factor(df_melt$Group,levels=c("WT","L100Q"))

ggplot(df_melt,aes(x=Group,y=value,fill=Group))+
  geom_violin(alpha=0.5)+
  geom_boxplot(inherit.aes = F,data=means,aes(x=Group,y=Mean,fill=Group))+
  geom_jitter(inherit.aes = F,data=means,aes(x=Group,y=Mean,fill=Group,color=Group),position=position_jitter(0.2),size=1)+
  theme_classic()+
  lims(y=c(0,2))+
  scale_color_manual(values = c("L100Q"=L100_col,"WT"=Parent_col))+
  scale_fill_manual(values = c("L100Q"=L100_col,"WT"=Parent_col))+
  stat_compare_means(comparisons = list(c("L100Q","WT")), label.y = c(1.7),label="p.signif",method = "wilcox.test")+
  labs(x="",y="Fluorescence \n (Nuclear / Cytoplasm)")+
  theme(legend.position = "none",
        axis.text=element_text(family="Arial",size=6, color="black"),
        axis.title = element_text(family="Arial",size=6, color="black"),
        legend.text = element_text(family="Arial",size=6, color="black"),
        axis.title.x=element_blank(),
        panel.background = element_blank(),
        plot.title = element_blank(),
        plot.background = element_blank(), 
        panel.border = element_blank(),
        legend.background = element_blank(),
        legend.title=element_blank(),
        legend.key.width= unit(0.4, 'cm'),
        legend.key.height= unit(0.4, 'cm'))

ggsave("FigureS4/FigS4A-box.pdf",height = 1.5,width = 1.25)
```


*******************************

```{r}
m<-read.table("../Omics-data/RNA-seq-expression/HCT/L100Q_vs_WT_DESEQ.txt",header=T)
m2<-read.table("../Omics-data/RNA-seq-expression/HCT/F10_vs_WT_DESEQ.txt",header=T)
m<-m[which(m$gene_type!="ns"),]
m2<-m2[which(m2$gene_type!="ns"),]

m<-intersect(m$Gene_Sym,m2$Gene_Sym)


table(Parent_vs_L100Q_sig$Genes %in% m)
table(Parent_vs_L100Q2_sig$Genes %in% m)


```




```{r,fig.width=}


wt_df<-merge(wt_df,local2[c("Gene.name","Main.location","Additional.location")],all.x=T,by.x="Gene",by.y="Gene.name")
l100Q_df<-merge(l100Q_df,local2[c("Gene.name","Main.location","Additional.location")],all.x=T,by.x="Gene",by.y="Gene.name")

wt_df$All_Location<-paste(wt_df$Main.location,wt_df$Additional.location,sep=";")
l100Q_df$All_Location<-paste(l100Q_df$Main.location,l100Q_df$Additional.location,sep=";")


wt_df<-wt_df %>% mutate(Local=case_when(
  grepl("Cyto|Endo|Mitochondria|Golgi|Microtubules|Peroxisomes|Vesicles",All_Location) & grepl("Nucle",All_Location)~"Both",
  grepl("Cyto|Endo|Mitochondria|Golgi|Microtubules|Peroxisomes|Vesicles",All_Location)~"Cytoplasmic",
  grepl("Nucle",All_Location)~"Nuclear",
  grepl("membrane|filaments",All_Location)~"Membrane",
  TRUE~"Other"))


l100Q_df<-l100Q_df %>% mutate(Local=case_when(
  grepl("Cyto|Endo|Mitochondria|Golgi|Microtubules|Peroxisomes|Vesicles",All_Location) & grepl("Nucle",All_Location)~"Both",
  grepl("Cyto|Endo|Mitochondria|Golgi|Microtubules|Peroxisomes|Vesicles",All_Location)~"Cytoplasmic",
  grepl("Nucle",All_Location)~"Nuclear",
  grepl("membrane|filaments",All_Location)~"Membrane",
  TRUE~"Other"))


WT_peak<-read.table("../Omics-data/Binding/PCBP1/eCLIP/C2BB/WT_Meta_C2_IDR.bed",sep = "\t")
L100Q_peak<-read.table("../Omics-data/Binding/PCBP1/eCLIP/C2BB/Mut_Meta_C2_IDR.bed",sep = "\t")

WT_peak$Gene<-sapply(WT_peak$V4, function(x){strsplit(x,"_")[[1]][1]})
L100Q_peak$Gene<-sapply(L100Q_peak$V4, function(x){strsplit(x,"_")[[1]][1]})


SE<-list("PPI"=wt_df$Gene,"eCLIP"=WT_peak$Gene)
v<-ggvenn::ggvenn(SE,fill_color=c(Parent_col,Parent_col),set_name_size=3,show_percentage=F,text_size=2.5,fill_alpha=0.6,stroke_size=0.5)+
  coord_cartesian(ylim = c(-1.2, 1.5))+
  theme(legend.position = "none",
        panel.background = element_blank(), 
        plot.background = element_blank(), 
        panel.border = element_blank(),
        legend.background = element_blank(),
        axis.title = element_text(family="Arial",size=0, color="black"),
        axis.text=element_text(family="Arial",size=0, color="black"),
        textt=element_text(family="Arial", size=0,color="black"))
v

SE<-list("PPI"=l100Q_df$Gene,"eCLIP"=L100Q_peak$Gene)
v<-ggvenn::ggvenn(SE,fill_color=c(L100_col,L100_col),set_name_size=3,show_percentage=F,
                  text_size=2.5,fill_alpha=0.6,stroke_size=0.5)+
  coord_cartesian(ylim = c(-1.2, 1.5))+
  theme(legend.position = "none",
        #panel.background = element_blank(), 
        #plot.background = element_blank(), 
        #panel.border = element_blank(),
        #legend.background = element_blank(),
        axis.title = element_text(family="Arial",size=0, color="white"),
        axis.text=element_text(family="Arial",size=0, color="white"),
        text=element_text(family="Arial", size=0,color="white"))
v
ggsave("~/Desktop/Ov_plot.pdf",width=1.15,height=0.84)




Go_up<-enrichGO(gene          = intersect(l100Q_df$Gene,L100Q_peak$Gene),
                  OrgDb         = org.Hs.eg.db,
                  keyType       = 'SYMBOL',
                  ont           = "BP",
                universe =prot$PG.Genes,
                  pAdjustMethod = "BH",
                  pvalueCutoff  = 0.05,
                  qvalueCutoff  = 0.05)
dotplot(Go_up,showCategory=6)

dotplot(Go_up,font.size = 8,showCategory=6)+
  scale_size_area(max_size = 3)+
  theme_classic()+
  theme(legend.position = "right",
        axis.text=element_text(size=8, color="black"),
        axis.text.x=element_text(size=8, color="black"),
        axis.title = element_text(size=8, color="black"),
        panel.background = element_blank(),
        plot.background = element_blank(), 
        legend.background = element_blank(),
        legend.key.size = unit(0.3, "cm"))
ggsave("~/Desktop/GO.pdf",width=4,height=2)
```





```{r,fig.width=3,fig.height=2}
rm(list=ls())
sec<-readxl::read_excel("~/Desktop/241111 SEC Burkitt.xlsx") %>% data.frame()
sec_melt<-reshape2::melt(sec,id.vars="Fraction..")
sec_melt<-sec_melt[which(sec_melt$variable!="R325G"),]
sec_melt<-sec_melt[!is.na(sec_melt$value),]
sec_melt$variable<-factor(sec_melt$variable,levels=c("WT","G292D","I302M"))
sec_melt$Fraction..<-factor(sec_melt$Fraction..)

ggplot()+
  geom_line(data=sec_melt,aes(x=Fraction..,y=value,group = variable,color=variable),size=.25)+
  geom_point(data=sec_melt,aes(x=Fraction..,y=value),color="black",size=0.3)+
  scale_color_manual(values=c("WT"="black", "R325G"="blue","I302M"="purple","G292D"="red"))+
  theme_classic()+
  lims(y=c(0,0.5))+
  xlab("Fraction")+
  ylab("Rel. Signal")+
  theme_classic()+
  theme(legend.position = c(0.15,0.9),
        axis.text=element_text(size=8, color="black"),
        axis.title = element_text(size=8, color="black"),
        legend.text = element_text(size=8, color="black"),
        legend.title = element_blank(),
        panel.background = element_blank(),
        plot.background = element_blank(),
        panel.border = element_blank(),
        legend.background = element_blank(),
        legend.key.size = unit(0.2, "cm"))
ggsave("~/Desktop/Love_Mike3.pdf",height=1.5,width=3)

```




```{r}
rm(list=ls())
WT_eclip<-read.table("Figure3/Data/eCLIP/IDR/GG83_GG84_reprod_Meta.bed",sep = "\t")
L100Q_eclip<-read.table("Figure3/Data/eCLIP/IDR/GG87_GG88_reprod_Meta.bed",sep = "\t")


WT_eclip_Sym<-sapply(WT_eclip$V4, function(x){strsplit(x,"_")[[1]][1]})
L100Q_eclip_Sym<-sapply(L100Q_eclip$V4, function(x){strsplit(x,"_")[[1]][1]})


go<-enrichGO(gene          = L100Q_eclip_Sym,
                OrgDb         = org.Hs.eg.db,
                keyType       = 'SYMBOL',
                ont           = "BP",
                pAdjustMethod = "BH",
                pvalueCutoff  = 0.05,
                qvalueCutoff  = 0.05)
m<-go@result

go@result<-go@result[which(go@result$ID %in% c("GO:0072659","GO:0032956","GO:0098876","GO:1905475","GO:0051494","GO:0051495")),]
plot<-dotplot(go,font.size = 8)+
  theme_classic()+
  theme(legend.position ="right",
        axis.text=element_text(size=12, color="black"),
        legend.text=element_text(size=12, color="black"),
        axis.title= element_text(size=12, color="black"),
        axis.title.x= element_blank(),
        panel.background = element_blank(),
        legend.title=element_text(size=12, color="black"),
        plot.background = element_blank(), 
        panel.border = element_blank(),
        legend.background = element_blank(),
        legend.key.size = unit(0.5, 'cm'))
plot
ggsave("~/Desktop/Dan/L100Q_all.pdf",plot,width=6, height=3.5)

################


go<-enrichGO(gene          = setdiff(L100Q_eclip_Sym,WT_eclip_Sym),
                OrgDb         = org.Hs.eg.db,
                keyType       = 'SYMBOL',
                ont           = "BP",
                pAdjustMethod = "BH",
                pvalueCutoff  = 0.05,
                qvalueCutoff  = 0.05)
m<-go@result

go@result<-go@result[which(go@result$ID %in% c("GO:0022604","GO:0072659","GO:0120032","GO:0032956","GO:1990778","GO:0007015")),]
plot<-dotplot(go,font.size = 8)+
  theme_classic()+
  theme(legend.position ="right",
        axis.text=element_text(size=12, color="black"),
        legend.text=element_text(size=12, color="black"),
        axis.title= element_text(size=12, color="black"),
        axis.title.x= element_blank(),
        panel.background = element_blank(),
        legend.title=element_text(size=12, color="black"),
        plot.background = element_blank(), 
        panel.border = element_blank(),
        legend.background = element_blank(),
        legend.key.size = unit(0.5, 'cm'))
plot
ggsave("~/Desktop/Dan/L100Q_uniq.pdf",plot,width=6, height=3.5)




```

#HNRNPA1 Seq
```{r,fig.height=1.5,fig.width=4}
rm(list=ls())
my_cutstom <- data.frame(names = c(LETTERS[1:26],"-"), 
                         color = "#00000000", 
                         stringsAsFactors = FALSE)
ggmsa("~/Desktop/HNRNPA.fa",custom_color =my_cutstom,
      font = "helvetical", char_width = 0.4, seq_name = TRUE)+
  scale_y_discrete(position = "right")+
  theme(legend.position = "none",
        legend.text = element_text(family="Arial",size=8, color="black"),
        legend.title = element_blank(),
        panel.background = element_blank(),
        plot.background = element_blank(),
        panel.border = element_blank(),
        legend.background = element_blank(),
        legend.key.size = unit(0.4, "cm"),
        axis.text.y=element_text(family="Arial",size=8, color="black"),
        axis.text.x=element_blank(),
        axis.ticks=element_blank(),
        axis.line=element_blank())
ggsave("Burkitt/HNRNPA.pdf",height = 1.5,width = 4)
getwd()
```

#HNRNPA_homo
```{r}
rm(list=ls())
my_cutstom <- data.frame(names = c(LETTERS[1:26],"-"), 
                         color = "#00000000", 
                         stringsAsFactors = FALSE)
ggmsa("~/Desktop/HNRNPA_homo.fa",custom_color =my_cutstom,
      font = "helvetical", char_width = 0.4, seq_name = TRUE)+
  scale_y_discrete(position = "right")+
  theme(legend.position = "none",
        legend.text = element_text(family="Arial",size=8, color="black"),
        legend.title = element_blank(),
        panel.background = element_blank(),
        plot.background = element_blank(),
        panel.border = element_blank(),
        legend.background = element_blank(),
        legend.key.size = unit(0.4, "cm"),
        axis.text.y=element_text(family="Arial",size=8, color="black"),
        axis.text.x=element_blank(),
        axis.ticks=element_blank(),
        axis.line=element_blank())
ggsave("Burkitt/HNRNPA_homo.pdf",height = 1.5,width = 4)
getwd()
```

```{r}
rm(list=ls())
my_cutstom <- data.frame(names = c(LETTERS[1:26],"-"), 
                         color = "#00000000", 
                         stringsAsFactors = FALSE)
ggmsa("../Omics-data/Conservation_Seqs/A1_Specicies_conservation.txt",custom_color =my_cutstom,
      font = "helvetical", char_width = 0.4, seq_name = TRUE)+
  scale_y_discrete(position = "right")+
  theme(legend.position = "none",
        legend.text = element_text(family="Arial",size=8, color="black"),
        legend.title = element_blank(),
        panel.background = element_blank(),
        plot.background = element_blank(),
        panel.border = element_blank(),
        legend.background = element_blank(),
        legend.key.size = unit(0.4, "cm"),
        axis.text.y=element_text(family="Arial",size=8, color="black"),
        axis.text.x=element_blank(),
        axis.ticks=element_blank(),
        axis.line=element_blank())
ggsave("Burkitt/A1_cons.pdf",height = 1.5,width = 4)

ggmsa("../Omics-data/Conservation_Seqs/A2_conservation.txt",custom_color =my_cutstom,
      font = "helvetical", char_width = 0.4, seq_name = TRUE)+
  scale_y_discrete(position = "right")+
  theme(legend.position = "none",
        legend.text = element_text(family="Arial",size=8, color="black"),
        legend.title = element_blank(),
        panel.background = element_blank(),
        plot.background = element_blank(),
        panel.border = element_blank(),
        legend.background = element_blank(),
        legend.key.size = unit(0.4, "cm"),
        axis.text.y=element_text(family="Arial",size=8, color="black"),
        axis.text.x=element_blank(),
        axis.ticks=element_blank(),
        axis.line=element_blank())
ggsave("Burkitt/A2_cons.pdf",height = 1.5,width = 4)


ggmsa("../Omics-data/Conservation_Seqs/HNRNPK_conservation.txt",custom_color =my_cutstom,
      font = "helvetical", char_width = 0.4, seq_name = TRUE)+
  scale_y_discrete(position = "right")+
  theme(legend.position = "none",
        legend.text = element_text(family="Arial",size=8, color="black"),
        legend.title = element_blank(),
        panel.background = element_blank(),
        plot.background = element_blank(),
        panel.border = element_blank(),
        legend.background = element_blank(),
        legend.key.size = unit(0.4, "cm"),
        axis.text.y=element_text(family="Arial",size=8, color="black"),
        axis.text.x=element_blank(),
        axis.ticks=element_blank(),
        axis.line=element_blank())
ggsave("Burkitt/HNRNPK_cons.pdf",height = 1.5,width = 4)
```

#SOX9
```{r}
rm(list=ls())
WT_IP<-read.table("../Omics-data/Browsers/C2_WT_IP_chr17_72120658_72126817.genomecov")
WT_IN<-read.table("../Omics-data/Browsers/C2_WT_IN_chr17_72120658_72126817.genomecov")

L100Q_IP<-read.table("../Omics-data/Browsers/C2_L100Q_IP_chr17_72120658_72126817.genomecov")
L100Q_IN<-read.table("../Omics-data/Browsers/C2_L100Q_IN_chr17_72120658_72126817.genomecov")

gene<-rtracklayer::import("~/Desktop/Dominguez_Lab/Chimera/Reference/Homo_sapiens.GRCh38.108.chr.gtf") %>% data.frame()
SOX9<-gene[which(gene$gene_name=="SOX9"),]
SOX9<-gene[which(gene$transcript_id=="ENST00000245479"),]
SOX9<-SOX9[which(SOX9$type %in% c("CDS","five_prime_utr","three_prime_utr")),]

SOX9$y_start<-ifelse(SOX9$type=="CDS",0,0.2)
SOX9$y_end<-ifelse(SOX9$type=="CDS",1,0.8)

arrow_positions <- seq(min(SOX9$start),max(SOX9$end), by = 5000)
arrow_df <- data.frame(x = arrow_positions,xend = arrow_positions + 5000,  y = 0.5,yend = 0.5)

min<-	min(SOX9$start)
max<-max(SOX9$start)

ggplot()+
  geom_rect(data = data.frame(1),xmin = min(SOX9$start), xmax = max(SOX9$end), ymin = 0.45, ymax = 0.55,fill="black")+
  geom_rect(data=SOX9,aes(xmin=start,xmax=end,ymin=y_start,ymax=y_end,fill=type))+
  #geom_vline(xintercept = c(min,max), linetype = "dashed", color = "black", size = 0.1)+
  theme_classic()+
  scale_fill_manual(values=c("CDS"="black","five_prime_utr"="gray","three_prime_utr"="gray"))+
  theme(axis.text = element_blank(), 
    axis.title = element_blank(), 
    legend.position = "none",
    plot.background = element_blank(),
    panel.background = element_blank(),
    strip.background = element_blank(),
    strip.text.x = element_blank(),
    axis.ticks = element_blank(),
    axis.line = element_blank())
ggsave("Browsers/SOX9_structure.pdf",width=4,height=.5)



#browser
WT_IP<-WT_IP[which(WT_IP$V2>=min & WT_IP$V2<=max),]
WT_IN<-WT_IN[which(WT_IN$V2>=min & WT_IN$V2<=max),]
L100Q_IP<-L100Q_IP[which(L100Q_IP$V2>=min & L100Q_IP$V2<=max),]
L100Q_IN<-L100Q_IN[which(L100Q_IN$V2>=min & L100Q_IN$V2<=max),]
y_max<-max(c(WT_IP$V3,WT_IN$V3,L100Q_IP$V3,L100Q_IN$V3))

#WT_IP
ggplot()+
  geom_area(data=WT_IP,aes(x=V2,y=V3),fill=Parent_col)+
  #geom_rect(data=wt_peak,aes(xmin=Start,xmax=End),ymin=0,ymax=y_max,color = NA,linetype = "dashed",linewidth = 0,fill=Parent_col,alpha=0.2)+
  theme_classic()+
  lims(y=c(0,y_max),x=c(min,max))+
  scale_fill_manual(values=c("CDS"="#073B4C","five_prime_utr"="#118AB2","three_prime_utr"="#118AB2"))+
  theme(axis.text = element_blank(), 
    axis.title = element_blank(),
    legend.position = "none",
    plot.background = element_blank(),
    panel.background = element_blank(),
    strip.background = element_blank(),
    strip.text.x = element_blank(),
    axis.ticks = element_blank(),
    axis.line = element_blank())
ggsave("Browsers/SOX9_structure_WT_IP.pdf",width=4,height=.5)

#WT_IN
ggplot()+
  geom_area(data=WT_IN,aes(x=V2,y=V3),fill=Parent_col)+
  #geom_rect(data=wt_peak,aes(xmin=Start,xmax=End),ymin=0,ymax=y_max,color =NA,linetype = "dashed",linewidth = 0,fill=Parent_col,alpha=0.2)+
  theme_classic()+
  lims(y=c(0,y_max),x=c(min,max))+
  scale_fill_manual(values=c("CDS"="#073B4C","five_prime_utr"="#118AB2","three_prime_utr"="#118AB2"))+
  theme(axis.text = element_blank(), 
    axis.title = element_blank(), 
    legend.position = "none",
    plot.background = element_blank(),
    panel.background = element_blank(),
    strip.background = element_blank(),
    strip.text.x = element_blank(),
    axis.ticks = element_blank(),
    axis.line = element_blank())
ggsave("Browsers/SOX9_structure_WT_IN.pdf",width=4,height=.5)

#L100Q_IP
ggplot()+
  geom_area(data=L100Q_IP,aes(x=V2,y=V3),fill=L100_col)+
  #geom_rect(data=l100_peak,aes(xmin=Start,xmax=End),ymin=0,ymax=y_max,color = NA,linetype = "dashed",linewidth = 0,fill=L100_col,alpha=0.2)+
  theme_classic()+
  lims(y=c(0,y_max),x=c(min,max))+
  scale_fill_manual(values=c("CDS"="#073B4C","five_prime_utr"="#118AB2","three_prime_utr"="#118AB2"))+
  theme(axis.text = element_blank(), 
    axis.title = element_blank(), 
    legend.position = "none",
    plot.background = element_blank(),
    panel.background = element_blank(),
    strip.background = element_blank(),
    strip.text.x = element_blank(),
    axis.ticks = element_blank(),
    axis.line = element_blank())
ggsave("Browsers/SOX9_structure_L100Q_IP.pdf",width=4,height=.5)

#L100Q_IN
ggplot()+
  geom_area(data=L100Q_IN,aes(x=V2,y=V3),fill=L100_col)+
  #geom_rect(data=l100_peak,aes(xmin=Start,xmax=End),ymin=0,ymax=y_max,color = NA,linetype = "dashed",linewidth = 0,fill=L100_col,alpha=0.2)+
  theme_classic()+
  lims(y=c(0,y_max),x=c(min,max))+
  scale_fill_manual(values=c("CDS"="#073B4C","five_prime_utr"="#118AB2","three_prime_utr"="#118AB2"))+
  theme(axis.text = element_blank(), 
    axis.title = element_blank(), 
    legend.position = "none",
    plot.background = element_blank(),
    panel.background = element_blank(),
    strip.background = element_blank(),
    strip.text.x = element_blank(),
    axis.ticks = element_blank(),
    axis.line = element_blank())
ggsave("Browsers/SOX9_structure_L100Q_IN.pdf",width=4,height=.5)

```

#CEACAM
```{r}
rm(list=ls())
WT_IP<-read.table("../Omics-data/Browsers/C2_WT_IP_chr19_42505306_42530481.genomecov")
WT_IN<-read.table("../Omics-data/Browsers/C2_WT_IN_chr19_42505306_42530481.genomecov")

L100Q_IP<-read.table("../Omics-data/Browsers/C2_L100Q_IP_chr19_42505306_42530481.genomecov")
L100Q_IN<-read.table("../Omics-data/Browsers/C2_L100Q_IN_chr19_42505306_42530481.genomecov")

gene<-rtracklayer::import("~/Desktop/Dominguez_Lab/Chimera/Reference/Homo_sapiens.GRCh38.108.chr.gtf") %>% data.frame()
CEACAM1<-gene[which(gene$gene_name=="CEACAM1"),]
CEACAM1<-gene[which(gene$transcript_id=="ENST00000352591"),]
CEACAM1<-CEACAM1[which(CEACAM1$type %in% c("CDS","five_prime_utr","three_prime_utr")),]

CEACAM1$y_start<-ifelse(CEACAM1$type=="CDS",0,0.2)
CEACAM1$y_end<-ifelse(CEACAM1$type=="CDS",1,0.8)

arrow_positions <- seq(min(CEACAM1$start),max(CEACAM1$end), by = 5000)
arrow_df <- data.frame(x = arrow_positions,xend = arrow_positions + 5000,  y = 0.5,yend = 0.5)

min<-	min(CEACAM1$start)
max<-max(CEACAM1$start)

ggplot()+
  geom_rect(data = data.frame(1),xmin = min(CEACAM1$start), xmax = max(CEACAM1$end), ymin = 0.45, ymax = 0.55,fill="black")+
  geom_rect(data=CEACAM1,aes(xmin=start,xmax=end,ymin=y_start,ymax=y_end,fill=type))+
  #geom_vline(xintercept = c(min,max), linetype = "dashed", color = "black", size = 0.1)+
  theme_classic()+
  scale_fill_manual(values=c("CDS"="black","five_prime_utr"="gray","three_prime_utr"="gray"))+
  theme(axis.text = element_blank(), 
    axis.title = element_blank(), 
    legend.position = "none",
    plot.background = element_blank(),
    panel.background = element_blank(),
    strip.background = element_blank(),
    strip.text.x = element_blank(),
    axis.ticks = element_blank(),
    axis.line = element_blank())
ggsave("Browsers/CEACAM1_structure.pdf",width=4,height=.5)

#browser
WT_IP<-WT_IP[which(WT_IP$V2>=min & WT_IP$V2<=max),]
WT_IN<-WT_IN[which(WT_IN$V2>=min & WT_IN$V2<=max),]
L100Q_IP<-L100Q_IP[which(L100Q_IP$V2>=min & L100Q_IP$V2<=max),]
L100Q_IN<-L100Q_IN[which(L100Q_IN$V2>=min & L100Q_IN$V2<=max),]
y_max<-max(c(WT_IP$V3,WT_IN$V3,L100Q_IP$V3,L100Q_IN$V3))

#WT_IP
ggplot()+
  geom_area(data=WT_IP,aes(x=V2,y=V3),fill=Parent_col)+
  #geom_rect(data=wt_peak,aes(xmin=Start,xmax=End),ymin=0,ymax=y_max,color = NA,linetype = "dashed",linewidth = 0,fill=Parent_col,alpha=0.2)+
  theme_classic()+
  lims(y=c(0,y_max),x=c(min,max))+
  scale_fill_manual(values=c("CDS"="#073B4C","five_prime_utr"="#118AB2","three_prime_utr"="#118AB2"))+
  theme(axis.text = element_blank(), 
    axis.title = element_blank(),
    legend.position = "none",
    plot.background = element_blank(),
    panel.background = element_blank(),
    strip.background = element_blank(),
    strip.text.x = element_blank(),
    axis.ticks = element_blank(),
    axis.line = element_blank())
ggsave("Browsers/CEACAM1_structure_WT_IP.pdf",width=4,height=.5)

#WT_IN
ggplot()+
  geom_area(data=WT_IN,aes(x=V2,y=V3),fill=Parent_col)+
  #geom_rect(data=wt_peak,aes(xmin=Start,xmax=End),ymin=0,ymax=y_max,color =NA,linetype = "dashed",linewidth = 0,fill=Parent_col,alpha=0.2)+
  theme_classic()+
  lims(y=c(0,y_max),x=c(min,max))+
  scale_fill_manual(values=c("CDS"="#073B4C","five_prime_utr"="#118AB2","three_prime_utr"="#118AB2"))+
  theme(axis.text = element_blank(), 
    axis.title = element_blank(), 
    legend.position = "none",
    plot.background = element_blank(),
    panel.background = element_blank(),
    strip.background = element_blank(),
    strip.text.x = element_blank(),
    axis.ticks = element_blank(),
    axis.line = element_blank())
ggsave("Browsers/CEACAM1_structure_WT_IN.pdf",width=4,height=.5)

#L100Q_IP
ggplot()+
  geom_area(data=L100Q_IP,aes(x=V2,y=V3),fill=L100_col)+
  #geom_rect(data=l100_peak,aes(xmin=Start,xmax=End),ymin=0,ymax=y_max,color = NA,linetype = "dashed",linewidth = 0,fill=L100_col,alpha=0.2)+
  theme_classic()+
  lims(y=c(0,y_max),x=c(min,max))+
  scale_fill_manual(values=c("CDS"="#073B4C","five_prime_utr"="#118AB2","three_prime_utr"="#118AB2"))+
  theme(axis.text = element_blank(), 
    axis.title = element_blank(), 
    legend.position = "none",
    plot.background = element_blank(),
    panel.background = element_blank(),
    strip.background = element_blank(),
    strip.text.x = element_blank(),
    axis.ticks = element_blank(),
    axis.line = element_blank())
ggsave("Browsers/CEACAM1_structure_L100Q_IP.pdf",width=4,height=.5)

#L100Q_IN
ggplot()+
  geom_area(data=L100Q_IN,aes(x=V2,y=V3),fill=L100_col)+
  #geom_rect(data=l100_peak,aes(xmin=Start,xmax=End),ymin=0,ymax=y_max,color = NA,linetype = "dashed",linewidth = 0,fill=L100_col,alpha=0.2)+
  theme_classic()+
  lims(y=c(0,y_max),x=c(min,max))+
  scale_fill_manual(values=c("CDS"="#073B4C","five_prime_utr"="#118AB2","three_prime_utr"="#118AB2"))+
  theme(axis.text = element_blank(), 
    axis.title = element_blank(), 
    legend.position = "none",
    plot.background = element_blank(),
    panel.background = element_blank(),
    strip.background = element_blank(),
    strip.text.x = element_blank(),
    axis.ticks = element_blank(),
    axis.line = element_blank())
ggsave("Browsers/CEACAM1_structure_L100Q_IN.pdf",width=4,height=.5)

```

#CD44
```{r}
rm(list=ls())
WT_IP<-read.table("../Omics-data/Browsers/C2_WT_IP_chr11_35137171_35234402.genomecov")
WT_IN<-read.table("../Omics-data/Browsers/C2_WT_IN_chr11_35137171_35234402.genomecov")

L100Q_IP<-read.table("../Omics-data/Browsers/C2_L100Q_IP_chr11_35137171_35234402.genomecov")
L100Q_IN<-read.table("../Omics-data/Browsers/C2_L100Q_IN_chr11_35137171_35234402.genomecov")

gene<-rtracklayer::import("~/Desktop/Dominguez_Lab/Chimera/Reference/Homo_sapiens.GRCh38.108.chr.gtf") %>% data.frame()
CD44<-gene[which(gene$gene_name=="CD44"),]
CD44<-gene[which(gene$transcript_id=="ENST00000433892"),]
CD44<-CD44[which(CD44$type %in% c("CDS","five_prime_utr","three_prime_utr")),]

CD44$y_start<-ifelse(CD44$type=="CDS",0,0.2)
CD44$y_end<-ifelse(CD44$type=="CDS",1,0.8)

arrow_positions <- seq(min(CD44$start),max(CD44$end), by = 5000)
arrow_df <- data.frame(x = arrow_positions,xend = arrow_positions + 5000,  y = 0.5,yend = 0.5)

min<-	min(CD44$start)
max<-max(CD44$start)

ggplot()+
  geom_rect(data = data.frame(1),xmin = min(CD44$start), xmax = max(CD44$end), ymin = 0.45, ymax = 0.55,fill="black")+
  geom_rect(data=CD44,aes(xmin=start,xmax=end,ymin=y_start,ymax=y_end,fill=type))+
  #geom_vline(xintercept = c(min,max), linetype = "dashed", color = "black", size = 0.1)+
  theme_classic()+
  scale_fill_manual(values=c("CDS"="black","five_prime_utr"="gray","three_prime_utr"="gray"))+
  theme(axis.text = element_blank(), 
    axis.title = element_blank(), 
    legend.position = "none",
    plot.background = element_blank(),
    panel.background = element_blank(),
    strip.background = element_blank(),
    strip.text.x = element_blank(),
    axis.ticks = element_blank(),
    axis.line = element_blank())
ggsave("Browsers/CD44_structure.pdf",width=4,height=.5)

#browser
WT_IP<-WT_IP[which(WT_IP$V2>=min & WT_IP$V2<=max),]
WT_IN<-WT_IN[which(WT_IN$V2>=min & WT_IN$V2<=max),]
L100Q_IP<-L100Q_IP[which(L100Q_IP$V2>=min & L100Q_IP$V2<=max),]
L100Q_IN<-L100Q_IN[which(L100Q_IN$V2>=min & L100Q_IN$V2<=max),]
y_max<-max(c(WT_IP$V3,WT_IN$V3,L100Q_IP$V3,L100Q_IN$V3))


WT_IP <- WT_IP[,c(2,3)] %>% tidyr::complete(V2 = seq(min(V2), max(V2)), fill = list(V3 = 0))
WT_IN <- WT_IN[,c(2,3)] %>% tidyr::complete(V2 = seq(min(V2), max(V2)), fill = list(V3 = 0))
L100Q_IP <- L100Q_IP[,c(2,3)] %>% tidyr::complete(V2 = seq(min(V2), max(V2)), fill = list(V3 = 0))
L100Q_IN <- L100Q_IN[,c(2,3)] %>% tidyr::complete(V2 = seq(min(V2), max(V2)), fill = list(V3 = 0))

WT_IP<-WT_IP[which(WT_IP$V2>35139114 & WT_IP$V2<35139342),]
WT_IN<-WT_IN[which(WT_IN$V2>35139114 & WT_IN$V2<35139342),]
L100Q_IP<-L100Q_IP[which(L100Q_IP$V2>35139114 & L100Q_IP$V2<35139342),]
L100Q_IN<-L100Q_IN[which(L100Q_IN$V2>35139114 & L100Q_IN$V2<35139342),]

#WT_IP
ggplot()+
  geom_area(data=WT_IP,aes(x=V2,y=V3),fill=Parent_col)+
  #geom_rect(data=wt_peak,aes(xmin=Start,xmax=End),ymin=0,ymax=y_max,color = NA,linetype = "dashed",linewidth = 0,fill=Parent_col,alpha=0.2)+
  theme_classic()+
  lims(y=c(0,y_max))+
  scale_fill_manual(values=c("CDS"="#073B4C","five_prime_utr"="#118AB2","three_prime_utr"="#118AB2"))+
  theme(axis.text = element_blank(), 
    axis.title = element_blank(),
    legend.position = "none",
    plot.background = element_blank(),
    panel.background = element_blank(),
    strip.background = element_blank(),
    strip.text.x = element_blank(),
    axis.ticks = element_blank(),
    axis.line = element_blank())
ggsave("Browsers/CD44_structure_WT_IP.pdf",width=4,height=.5)

#WT_IN
ggplot()+
  geom_area(data=WT_IN,aes(x=V2,y=V3),fill=Parent_col)+
  #geom_rect(data=wt_peak,aes(xmin=Start,xmax=End),ymin=0,ymax=y_max,color =NA,linetype = "dashed",linewidth = 0,fill=Parent_col,alpha=0.2)+
  theme_classic()+
  lims(y=c(0,y_max))+
  scale_fill_manual(values=c("CDS"="#073B4C","five_prime_utr"="#118AB2","three_prime_utr"="#118AB2"))+
  theme(axis.text = element_blank(), 
    axis.title = element_blank(), 
    legend.position = "none",
    plot.background = element_blank(),
    panel.background = element_blank(),
    strip.background = element_blank(),
    strip.text.x = element_blank(),
    axis.ticks = element_blank(),
    axis.line = element_blank())
ggsave("Browsers/CD44_structure_WT_IN.pdf",width=4,height=.5)

#L100Q_IP
ggplot()+
  geom_area(data=L100Q_IP,aes(x=V2,y=V3),fill=L100_col)+
  #geom_rect(data=l100_peak,aes(xmin=Start,xmax=End),ymin=0,ymax=y_max,color = NA,linetype = "dashed",linewidth = 0,fill=L100_col,alpha=0.2)+
  theme_classic()+
  lims(y=c(0,y_max))+
  scale_fill_manual(values=c("CDS"="#073B4C","five_prime_utr"="#118AB2","three_prime_utr"="#118AB2"))+
  theme(axis.text = element_blank(), 
    axis.title = element_blank(), 
    legend.position = "none",
    plot.background = element_blank(),
    panel.background = element_blank(),
    strip.background = element_blank(),
    strip.text.x = element_blank(),
    axis.ticks = element_blank(),
    axis.line = element_blank())
ggsave("Browsers/CD44_structure_L100Q_IP.pdf",width=4,height=.5)

#L100Q_IN
ggplot()+
  geom_area(data=L100Q_IN,aes(x=V2,y=V3),fill=L100_col)+
  #geom_rect(data=l100_peak,aes(xmin=Start,xmax=End),ymin=0,ymax=y_max,color = NA,linetype = "dashed",linewidth = 0,fill=L100_col,alpha=0.2)+
  theme_classic()+
  lims(y=c(0,y_max))+
  scale_fill_manual(values=c("CDS"="#073B4C","five_prime_utr"="#118AB2","three_prime_utr"="#118AB2"))+
  theme(axis.text = element_blank(), 
    axis.title = element_blank(), 
    legend.position = "none",
    plot.background = element_blank(),
    panel.background = element_blank(),
    strip.background = element_blank(),
    strip.text.x = element_blank(),
    axis.ticks = element_blank(),
    axis.line = element_blank())
ggsave("Browsers/CD44_structure_L100Q_IN.pdf",width=4,height=.5)

```

#Splicing titration

#Burkitt-ERCC1
```{r,fig.height=1.5,fig.width=1.75}
rm(list=ls())
df<-readxl::read_excel("../Data and Code In Experimental Order/Supplemental Figures (Jan 2026 organization) /7_Dom_negative_burkitt_doxTitration/Final splicing values burkitt dox titration.xlsx",sheet="ERCC1 PSI all reps burkitt")
colnames(df)<-c("Conc","WT_1","WT_2","WT_3","I302M_1","I302M_2","I302M_3","Y183*_1","Y183*_2","Y183*_3")
df_melt<-reshape2::melt(df,id.vars = "Conc")
df_melt<-df_melt[!is.na(df_melt$value),]
df_melt$Group<-sapply(as.character(df_melt$variable),function(x){strsplit(x,"_")[[1]][1]})
df_melt$Conc<-as.numeric(df_melt$Conc)

data_mean<-aggregate(value ~ Conc+Group, data = df_melt, FUN = mean)
mean_0<-data_mean[which(data_mean$Conc=="0"),]
data_mean<-merge(data_mean,mean_0[c("Group","value")],by=c("Group"),all.x=T)
data_mean$Del_Psi<-data_mean$value.x-data_mean$value.y
data_sd<-aggregate(value ~ Conc+Group, data = df_melt, FUN = sd)
comb<-merge(data_mean,data_sd,by=c("Conc","Group"))
colnames(comb)<-c("Conc","Group","Mean","Mean_0","Del_Psi","SD")
comb$Group<-factor(comb$Group,levels=c("WT","I302M","Y183*"))

ggplot(comb,aes(x=Conc,y=Del_Psi,group=Group))+
  geom_errorbar(aes(ymin = Del_Psi - SD, ymax = Del_Psi + SD,color=Group), width = 25,size=.25)+
  geom_line(size=0.3,aes(color=Group))+
  geom_point(aes(color=Group),size=0.5)+
  scale_color_manual(values = c("WT" ="#0096FE", "I302M" ="#932191","Y183*"="#ff9200"))+
  theme_classic()+
  ylab(bquote(Delta~"PSI"))+
  xlab(bquote("Dox conc." ~ "(" * ng / m*L * ")"))+
  theme(legend.position = c(0.9,0.9),
        axis.text=element_text(family="Arial",size=6, color="black"),
        axis.title = element_text(family="Arial",size=6, color="black"),
        legend.key.size = unit(0.2, "cm"),
        legend.spacing.y = unit(-0.15, "cm"),
        legend.text = element_text(family="Arial",size=6, color="black"),
        legend.title = element_blank(),
        panel.background = element_blank(),
        plot.background = element_blank(), 
        panel.border = element_blank(),
        legend.background = element_blank())
ggsave("Dosage/ERCC1_burkitt.pdf",height=1.5,width=1.75)
```

#Burkitt-ACIN1
```{r,fig.height=1.5,fig.width=1.75}
rm(list=ls())
df<-readxl::read_excel("../Data and Code In Experimental Order/Supplemental Figures (Jan 2026 organization) /7_Dom_negative_burkitt_doxTitration/Final splicing values burkitt dox titration.xlsx",sheet="ACIN1 PSI all reps burkitt")
colnames(df)<-c("Conc","WT_1","WT_2","WT_3","I302M_1","I302M_2","I302M_3","Y183*_1","Y183*_2","Y183*_3")
df_melt<-reshape2::melt(df,id.vars = "Conc")
df_melt<-df_melt[!is.na(df_melt$value),]
df_melt$Group<-sapply(as.character(df_melt$variable),function(x){strsplit(x,"_")[[1]][1]})
df_melt$Conc<-as.numeric(df_melt$Conc)

data_mean<-aggregate(value ~ Conc+Group, data = df_melt, FUN = mean)
mean_0<-data_mean[which(data_mean$Conc=="0"),]
data_mean<-merge(data_mean,mean_0[c("Group","value")],by=c("Group"),all.x=T)
data_mean$Del_Psi<-data_mean$value.x-data_mean$value.y
data_sd<-aggregate(value ~ Conc+Group, data = df_melt, FUN = sd)
comb<-merge(data_mean,data_sd,by=c("Conc","Group"))
colnames(comb)<-c("Conc","Group","Mean","Mean_0","Del_Psi","SD")
comb$Group<-factor(comb$Group,levels=c("WT","I302M","Y183*"))

ggplot(comb,aes(x=Conc,y=Del_Psi,group=Group))+
  geom_errorbar(aes(ymin = Del_Psi - SD, ymax = Del_Psi + SD,color=Group), width = 25,size=.25)+
  geom_line(size=0.3,aes(color=Group))+
  geom_point(aes(color=Group),size=0.5)+
  scale_color_manual(values = c("WT" ="#0096FE", "I302M" ="#932191","Y183*"="#ff9200"))+
  theme_classic()+
  ylab(bquote(Delta~"PSI"))+
  xlab(bquote("Dox conc." ~ "(" * ng / m*L * ")"))+
  theme(legend.position = c(0.9,0.9),
        axis.text=element_text(family="Arial",size=6, color="black"),
        axis.title = element_text(family="Arial",size=6, color="black"),
        legend.key.size = unit(0.2, "cm"),
        legend.spacing.y = unit(-0.15, "cm"),
        legend.text = element_text(family="Arial",size=6, color="black"),
        legend.title = element_blank(),
        panel.background = element_blank(),
        plot.background = element_blank(), 
        panel.border = element_blank(),
        legend.background = element_blank())
ggsave("Dosage/ACIN1_burkitt.pdf",height=1.5,width=1.75)
```

#Burkitt-BAG6
```{r,fig.height=1.5,fig.width=1.75}
rm(list=ls())
df<-readxl::read_excel("../Data and Code In Experimental Order/Supplemental Figures (Jan 2026 organization) /7_Dom_negative_burkitt_doxTitration/Final splicing values burkitt dox titration.xlsx",sheet="BAG6 PSI all reps Burkitt")
colnames(df)<-c("Conc","WT_1","WT_2","WT_3","I302M_1","I302M_2","I302M_3","Y183*_1","Y183*_2","Y183*_3")
df_melt<-reshape2::melt(df,id.vars = "Conc")
df_melt<-df_melt[!is.na(df_melt$value),]
df_melt$Group<-sapply(as.character(df_melt$variable),function(x){strsplit(x,"_")[[1]][1]})
df_melt$Conc<-as.numeric(df_melt$Conc)

data_mean<-aggregate(value ~ Conc+Group, data = df_melt, FUN = mean)
mean_0<-data_mean[which(data_mean$Conc=="0"),]
data_mean<-merge(data_mean,mean_0[c("Group","value")],by=c("Group"),all.x=T)
data_mean$Del_Psi<-data_mean$value.x-data_mean$value.y
data_sd<-aggregate(value ~ Conc+Group, data = df_melt, FUN = sd)
comb<-merge(data_mean,data_sd,by=c("Conc","Group"))
colnames(comb)<-c("Conc","Group","Mean","Mean_0","Del_Psi","SD")
comb$Group<-factor(comb$Group,levels=c("WT","I302M","Y183*"))

ggplot(comb,aes(x=Conc,y=Del_Psi,group=Group))+
  geom_errorbar(aes(ymin = Del_Psi - SD, ymax = Del_Psi + SD,color=Group), width = 25,size=.25)+
  geom_line(size=0.3,aes(color=Group))+
  geom_point(aes(color=Group),size=0.5)+
  scale_color_manual(values = c("WT" ="#0096FE", "I302M" ="#932191","Y183*"="#ff9200"))+
  theme_classic()+
  ylab(bquote(Delta~"PSI"))+
  xlab(bquote("Dox conc." ~ "(" * ng / m*L * ")"))+
  theme(legend.position = c(0.9,0.15),
        axis.text=element_text(family="Arial",size=6, color="black"),
        axis.title = element_text(family="Arial",size=6, color="black"),
        legend.key.size = unit(0.2, "cm"),
        legend.spacing.y = unit(-0.15, "cm"),
        legend.text = element_text(family="Arial",size=6, color="black"),
        legend.title = element_blank(),
        panel.background = element_blank(),
        plot.background = element_blank(), 
        panel.border = element_blank(),
        legend.background = element_blank())
ggsave("Dosage/BAG6_burkitt.pdf",height=1.5,width=1.75)
```

#Burkitt-CTTN
```{r,fig.height=1.5,fig.width=1.75}
rm(list=ls())
df<-readxl::read_excel("../Data and Code In Experimental Order/Supplemental Figures (Jan 2026 organization) /7_Dom_negative_burkitt_doxTitration/Final splicing values burkitt dox titration.xlsx",sheet="CTTN PSI all reps Burkitt")
colnames(df)<-c("Conc","WT_1","WT_2","WT_3","I302M_1","I302M_2","I302M_3","Y183*_1","Y183*_2","Y183*_3")
df_melt<-reshape2::melt(df,id.vars = "Conc")
df_melt<-df_melt[!is.na(df_melt$value),]
df_melt$Group<-sapply(as.character(df_melt$variable),function(x){strsplit(x,"_")[[1]][1]})
df_melt$Conc<-as.numeric(df_melt$Conc)

data_mean<-aggregate(value ~ Conc+Group, data = df_melt, FUN = mean)
mean_0<-data_mean[which(data_mean$Conc=="0"),]
data_mean<-merge(data_mean,mean_0[c("Group","value")],by=c("Group"),all.x=T)
data_mean$Del_Psi<-data_mean$value.x-data_mean$value.y
data_sd<-aggregate(value ~ Conc+Group, data = df_melt, FUN = sd)
comb<-merge(data_mean,data_sd,by=c("Conc","Group"))
colnames(comb)<-c("Conc","Group","Mean","Mean_0","Del_Psi","SD")
comb$Group<-factor(comb$Group,levels=c("WT","I302M","Y183*"))

ggplot(comb,aes(x=Conc,y=Del_Psi,group=Group))+
  geom_errorbar(aes(ymin = Del_Psi - SD, ymax = Del_Psi + SD,color=Group), width = 25,size=.25)+
  geom_line(size=0.3,aes(color=Group))+
  geom_point(aes(color=Group),size=0.5)+
  scale_color_manual(values = c("WT" ="#0096FE", "I302M" ="#932191","Y183*"="#ff9200"))+
  theme_classic()+
  ylab(bquote(Delta~"PSI"))+
  xlab(bquote("Dox conc." ~ "(" * ng / m*L * ")"))+
  theme(legend.position = c(0.9,0.9),
        axis.text=element_text(family="Arial",size=6, color="black"),
        axis.title = element_text(family="Arial",size=6, color="black"),
        legend.key.size = unit(0.2, "cm"),
        legend.spacing.y = unit(-0.15, "cm"),
        legend.text = element_text(family="Arial",size=6, color="black"),
        legend.title = element_blank(),
        panel.background = element_blank(),
        plot.background = element_blank(), 
        panel.border = element_blank(),
        legend.background = element_blank())
ggsave("Dosage/CTTN_burkitt.pdf",height=1.5,width=1.75)
```

#Burkitt-CRAT
```{r,fig.height=1.5,fig.width=1.75}
rm(list=ls())
df<-readxl::read_excel("../Data and Code In Experimental Order/Supplemental Figures (Jan 2026 organization) /7_Dom_negative_burkitt_doxTitration/Final splicing values burkitt dox titration.xlsx",sheet="CRAT PSI all reps Burkitt")
colnames(df)<-c("Conc","WT_1","WT_2","WT_3","I302M_1","I302M_2","I302M_3","Y183*_1","Y183*_2","Y183*_3")
df_melt<-reshape2::melt(df,id.vars = "Conc")
df_melt<-df_melt[!is.na(df_melt$value),]
df_melt$Group<-sapply(as.character(df_melt$variable),function(x){strsplit(x,"_")[[1]][1]})
df_melt$Conc<-as.numeric(df_melt$Conc)

data_mean<-aggregate(value ~ Conc+Group, data = df_melt, FUN = mean)
mean_0<-data_mean[which(data_mean$Conc=="0"),]
data_mean<-merge(data_mean,mean_0[c("Group","value")],by=c("Group"),all.x=T)
data_mean$Del_Psi<-data_mean$value.x-data_mean$value.y
data_sd<-aggregate(value ~ Conc+Group, data = df_melt, FUN = sd)
comb<-merge(data_mean,data_sd,by=c("Conc","Group"))
colnames(comb)<-c("Conc","Group","Mean","Mean_0","Del_Psi","SD")
comb$Group<-factor(comb$Group,levels=c("WT","I302M","Y183*"))

ggplot(comb,aes(x=Conc,y=Del_Psi,group=Group))+
  geom_errorbar(aes(ymin = Del_Psi - SD, ymax = Del_Psi + SD,color=Group), width = 25,size=.25)+
  geom_line(size=0.3,aes(color=Group))+
  geom_point(aes(color=Group),size=0.5)+
  scale_color_manual(values = c("WT" ="#0096FE", "I302M" ="#932191","Y183*"="#ff9200"))+
  theme_classic()+
  ylab(bquote(Delta~"PSI"))+
  xlab(bquote("Dox conc." ~ "(" * ng / m*L * ")"))+
  theme(legend.position = c(0.9,0.9),
        axis.text=element_text(family="Arial",size=6, color="black"),
        axis.title = element_text(family="Arial",size=6, color="black"),
        legend.key.size = unit(0.2, "cm"),
        legend.spacing.y = unit(-0.15, "cm"),
        legend.text = element_text(family="Arial",size=6, color="black"),
        legend.title = element_blank(),
        panel.background = element_blank(),
        plot.background = element_blank(), 
        panel.border = element_blank(),
        legend.background = element_blank())
ggsave("Dosage/CRAT_burkitt.pdf",height=1.5,width=1.75)
```

#Burkitt-ATP13A2
```{r,fig.height=1.5,fig.width=1.75}
rm(list=ls())
df<-readxl::read_excel("../Data and Code In Experimental Order/Supplemental Figures (Jan 2026 organization) /7_Dom_negative_burkitt_doxTitration/Final splicing values burkitt dox titration.xlsx",sheet="ATP13A2 PSI all reps Burkitt")
colnames(df)<-c("Conc","WT_1","WT_2","WT_3","I302M_1","I302M_2","I302M_3","Y183*_1","Y183*_2","Y183*_3")
df_melt<-reshape2::melt(df,id.vars = "Conc")
df_melt<-df_melt[!is.na(df_melt$value),]
df_melt$Group<-sapply(as.character(df_melt$variable),function(x){strsplit(x,"_")[[1]][1]})
df_melt$Conc<-as.numeric(df_melt$Conc)

data_mean<-aggregate(value ~ Conc+Group, data = df_melt, FUN = mean)
mean_0<-data_mean[which(data_mean$Conc=="0"),]
data_mean<-merge(data_mean,mean_0[c("Group","value")],by=c("Group"),all.x=T)
data_mean$Del_Psi<-data_mean$value.x-data_mean$value.y
data_sd<-aggregate(value ~ Conc+Group, data = df_melt, FUN = sd)
comb<-merge(data_mean,data_sd,by=c("Conc","Group"))
colnames(comb)<-c("Conc","Group","Mean","Mean_0","Del_Psi","SD")
comb$Group<-factor(comb$Group,levels=c("WT","I302M","Y183*"))

ggplot(comb,aes(x=Conc,y=Del_Psi,group=Group))+
  geom_errorbar(aes(ymin = Del_Psi - SD, ymax = Del_Psi + SD,color=Group), width = 25,size=.25)+
  geom_line(size=0.3,aes(color=Group))+
  geom_point(aes(color=Group),size=0.5)+
  scale_color_manual(values = c("WT" ="#0096FE", "I302M" ="#932191","Y183*"="#ff9200"))+
  theme_classic()+
  ylab(bquote(Delta~"PSI"))+
  xlab(bquote("Dox conc." ~ "(" * ng / m*L * ")"))+
  theme(legend.position = c(0.9,0.9),
        axis.text=element_text(family="Arial",size=6, color="black"),
        axis.title = element_text(family="Arial",size=6, color="black"),
        legend.key.size = unit(0.2, "cm"),
        legend.spacing.y = unit(-0.15, "cm"),
        legend.text = element_text(family="Arial",size=6, color="black"),
        legend.title = element_blank(),
        panel.background = element_blank(),
        plot.background = element_blank(), 
        panel.border = element_blank(),
        legend.background = element_blank())
ggsave("Dosage/ATP13A2_burkitt.pdf",height=1.5,width=1.75)
```

#L100Q-ERCC1
```{r,fig.height=1.5,fig.width=1.75}
rm(list=ls())
df<-readxl::read_excel("../Data and Code In Experimental Order/Supplemental Figures (Jan 2026 organization) /7_Dom_negative_L100Q_doxTitration/Final splicing values L100Q dox titration.xlsx",sheet="ERCC1 all reps L100Q")
colnames(df)<-c("Conc","WT_1","WT_2","WT_3","L100Q_1","L100Q_2","L100Q_3")
df_melt<-reshape2::melt(df,id.vars = "Conc")
df_melt<-df_melt[!is.na(df_melt$value),]
df_melt$Group<-sapply(as.character(df_melt$variable),function(x){strsplit(x,"_")[[1]][1]})
df_melt$Conc<-as.numeric(df_melt$Conc)

data_mean<-aggregate(value ~ Conc+Group, data = df_melt, FUN = mean)
mean_0<-data_mean[which(data_mean$Conc=="0"),]
data_mean<-merge(data_mean,mean_0[c("Group","value")],by=c("Group"),all.x=T)
data_mean$Del_Psi<-data_mean$value.x-data_mean$value.y
data_sd<-aggregate(value ~ Conc+Group, data = df_melt, FUN = sd)
comb<-merge(data_mean,data_sd,by=c("Conc","Group"))
colnames(comb)<-c("Conc","Group","Mean","Mean_0","Del_Psi","SD")
comb$Group<-factor(comb$Group,levels=c("WT","L100Q"))


ggplot(comb,aes(x=Conc,y=Del_Psi,group=Group))+
  geom_errorbar(aes(ymin = Del_Psi - SD, ymax = Del_Psi + SD,color=Group), width = 10,size=.25)+
  geom_line(size=0.3,aes(color=Group))+
  geom_point(aes(color=Group),size=0.5)+
  scale_color_manual(values = c("WT" ="#0096FE", "L100Q" ="#FF2600"))+
  theme_classic()+
  ylab(bquote(Delta~"PSI"))+
  xlab(bquote("Dox conc." ~ "(" * ng / m*L * ")"))+
  theme(legend.position = c(0.9,0.8),
        axis.text=element_text(family="Arial",size=6, color="black"),
        axis.title = element_text(family="Arial",size=6, color="black"),
        legend.key.size = unit(0.2, "cm"),
        legend.spacing.y = unit(-0.15, "cm"),
        legend.text = element_text(family="Arial",size=6, color="black"),
        legend.title = element_blank(),
        panel.background = element_blank(),
        plot.background = element_blank(), 
        panel.border = element_blank(),
        legend.background = element_blank())
ggsave("Dosage/ERCC1_L100Q.pdf",height=1.5,width=1.75)
```

#L100Q-ACIN1
```{r,fig.height=1.5,fig.width=1.75}
rm(list=ls())
df<-readxl::read_excel("../Data and Code In Experimental Order/Supplemental Figures (Jan 2026 organization) /7_Dom_negative_L100Q_doxTitration/Final splicing values L100Q dox titration.xlsx",sheet="ACIN1 all reps L100Q")
colnames(df)<-c("Conc","WT_1","WT_2","WT_3","L100Q_1","L100Q_2","L100Q_3")
df_melt<-reshape2::melt(df,id.vars = "Conc")
df_melt<-df_melt[!is.na(df_melt$value),]
df_melt$Group<-sapply(as.character(df_melt$variable),function(x){strsplit(x,"_")[[1]][1]})
df_melt$Conc<-as.numeric(df_melt$Conc)

data_mean<-aggregate(value ~ Conc+Group, data = df_melt, FUN = mean)
mean_0<-data_mean[which(data_mean$Conc=="0"),]
data_mean<-merge(data_mean,mean_0[c("Group","value")],by=c("Group"),all.x=T)
data_mean$Del_Psi<-data_mean$value.x-data_mean$value.y
data_sd<-aggregate(value ~ Conc+Group, data = df_melt, FUN = sd)
comb<-merge(data_mean,data_sd,by=c("Conc","Group"))
colnames(comb)<-c("Conc","Group","Mean","Mean_0","Del_Psi","SD")
comb$Group<-factor(comb$Group,levels=c("WT","L100Q"))

ggplot(comb,aes(x=Conc,y=Del_Psi,group=Group))+
  geom_errorbar(aes(ymin = Del_Psi - SD, ymax = Del_Psi + SD,color=Group), width = 10,size=.25)+
  geom_line(size=0.3,aes(color=Group))+
  geom_point(aes(color=Group),size=0.5)+
  scale_color_manual(values = c("WT" ="#0096FE", "L100Q" ="#FF2600"))+
  theme_classic()+
  ylab(bquote(Delta~"PSI"))+
  xlab(bquote("Dox conc." ~ "(" * ng / m*L * ")"))+
  theme(legend.position = c(0.85,0.1),
        axis.text=element_text(family="Arial",size=6, color="black"),
        axis.title = element_text(family="Arial",size=6, color="black"),
        legend.key.size = unit(0.2, "cm"),
        legend.spacing.y = unit(-0.15, "cm"),
        legend.text = element_text(family="Arial",size=6, color="black"),
        legend.title = element_blank(),
        panel.background = element_blank(),
        plot.background = element_blank(), 
        panel.border = element_blank(),
        legend.background = element_blank())
ggsave("Dosage/ACIN1_L100Q.pdf",height=1.5,width=1.75)
```

#L100Q-BAG6
```{r,fig.height=1.5,fig.width=1.75}
rm(list=ls())
df<-readxl::read_excel("../Data and Code In Experimental Order/Supplemental Figures (Jan 2026 organization) /7_Dom_negative_L100Q_doxTitration/Final splicing values L100Q dox titration.xlsx",sheet="BAG6 all reps L100Q")
colnames(df)<-c("Conc","WT_1","WT_2","WT_3","L100Q_1","L100Q_2","L100Q_3")
df_melt<-reshape2::melt(df,id.vars = "Conc")
df_melt<-df_melt[!is.na(df_melt$value),]
df_melt$Group<-sapply(as.character(df_melt$variable),function(x){strsplit(x,"_")[[1]][1]})
df_melt$Conc<-as.numeric(df_melt$Conc)

data_mean<-aggregate(value ~ Conc+Group, data = df_melt, FUN = mean)
mean_0<-data_mean[which(data_mean$Conc=="0"),]
data_mean<-merge(data_mean,mean_0[c("Group","value")],by=c("Group"),all.x=T)
data_mean$Del_Psi<-data_mean$value.x-data_mean$value.y
data_sd<-aggregate(value ~ Conc+Group, data = df_melt, FUN = sd)
comb<-merge(data_mean,data_sd,by=c("Conc","Group"))
colnames(comb)<-c("Conc","Group","Mean","Mean_0","Del_Psi","SD")
comb$Group<-factor(comb$Group,levels=c("WT","L100Q"))

ggplot(comb,aes(x=Conc,y=Del_Psi,group=Group))+
  geom_errorbar(aes(ymin = Del_Psi - SD, ymax = Del_Psi + SD,color=Group), width = 10,size=.25)+
  geom_line(size=0.3,aes(color=Group))+
  geom_point(aes(color=Group),size=0.5)+
  scale_color_manual(values = c("WT" ="#0096FE", "L100Q" ="#FF2600"))+
  theme_classic()+
  ylab(bquote(Delta~"PSI"))+
  xlab(bquote("Dox conc." ~ "(" * ng / m*L * ")"))+
  theme(legend.position = c(0.85,0.9),
        axis.text=element_text(family="Arial",size=6, color="black"),
        axis.title = element_text(family="Arial",size=6, color="black"),
        legend.key.size = unit(0.2, "cm"),
        legend.spacing.y = unit(-0.15, "cm"),
        legend.text = element_text(family="Arial",size=6, color="black"),
        legend.title = element_blank(),
        panel.background = element_blank(),
        plot.background = element_blank(), 
        panel.border = element_blank(),
        legend.background = element_blank())
ggsave("Dosage/BAG6_L100Q.pdf",height=1.5,width=1.75)
```

#L100Q-CTTN
```{r,fig.height=1.5,fig.width=1.75}
rm(list=ls())
df<-readxl::read_excel("../Data and Code In Experimental Order/Supplemental Figures (Jan 2026 organization) /7_Dom_negative_L100Q_doxTitration/Final splicing values L100Q dox titration.xlsx",sheet="CTTN all reps L100Q")
colnames(df)<-c("Conc","WT_1","WT_2","WT_3","L100Q_1","L100Q_2","L100Q_3")
df_melt<-reshape2::melt(df,id.vars = "Conc")
df_melt<-df_melt[!is.na(df_melt$value),]
df_melt$Group<-sapply(as.character(df_melt$variable),function(x){strsplit(x,"_")[[1]][1]})
df_melt$Conc<-as.numeric(df_melt$Conc)

data_mean<-aggregate(value ~ Conc+Group, data = df_melt, FUN = mean)
mean_0<-data_mean[which(data_mean$Conc=="0"),]
data_mean<-merge(data_mean,mean_0[c("Group","value")],by=c("Group"),all.x=T)
data_mean$Del_Psi<-data_mean$value.x-data_mean$value.y
data_sd<-aggregate(value ~ Conc+Group, data = df_melt, FUN = sd)
comb<-merge(data_mean,data_sd,by=c("Conc","Group"))
colnames(comb)<-c("Conc","Group","Mean","Mean_0","Del_Psi","SD")
comb$Group<-factor(comb$Group,levels=c("WT","L100Q"))

ggplot(comb,aes(x=Conc,y=Del_Psi,group=Group))+
  geom_errorbar(aes(ymin = Del_Psi - SD, ymax = Del_Psi + SD,color=Group), width = 10,size=.25)+
  geom_line(size=0.3,aes(color=Group))+
  geom_point(aes(color=Group),size=0.5)+
  scale_color_manual(values = c("WT" ="#0096FE", "L100Q" ="#FF2600"))+
  theme_classic()+
  ylab(bquote(Delta~"PSI"))+
  xlab(bquote("Dox conc." ~ "(" * ng / m*L * ")"))+
  theme(legend.position = c(0.85,0.1),
        axis.text=element_text(family="Arial",size=6, color="black"),
        axis.title = element_text(family="Arial",size=6, color="black"),
        legend.key.size = unit(0.2, "cm"),
        legend.spacing.y = unit(-0.15, "cm"),
        legend.text = element_text(family="Arial",size=6, color="black"),
        legend.title = element_blank(),
        panel.background = element_blank(),
        plot.background = element_blank(), 
        panel.border = element_blank(),
        legend.background = element_blank())
ggsave("Dosage/CTTN_L100Q.pdf",height=1.5,width=1.75)
```


#Combined

#ERCC1
```{r}
rm(list=ls())
df<-readxl::read_excel("../Data and Code In Experimental Order/Supplemental Figures (Jan 2026 organization) /7_Dom_negative_burkitt_doxTitration/Final splicing values burkitt dox titration.xlsx",sheet="ERCC1 PSI all reps burkitt")
colnames(df)<-c("Conc","WT_1","WT_2","WT_3","I302M_1","I302M_2","I302M_3","Y183*_1","Y183*_2","Y183*_3")
df_melt<-reshape2::melt(df,id.vars = "Conc")
df_melt<-df_melt[!is.na(df_melt$value),]
df_melt$Group<-sapply(as.character(df_melt$variable),function(x){strsplit(x,"_")[[1]][1]})
df_melt$Conc<-as.numeric(df_melt$Conc)

df2<-readxl::read_excel("../Data and Code In Experimental Order/Supplemental Figures (Jan 2026 organization) /7_Dom_negative_L100Q_doxTitration/Final splicing values L100Q dox titration.xlsx",sheet="ERCC1 all reps L100Q")
colnames(df2)<-c("Conc","WT_1","WT_2","WT_3","L100Q_1","L100Q_2","L100Q_3")
df2_melt<-reshape2::melt(df2,id.vars = "Conc")
df2_melt<-df2_melt[!is.na(df2_melt$value),]
df2_melt$Group<-sapply(as.character(df2_melt$variable),function(x){strsplit(x,"_")[[1]][1]})
df2_melt$Conc<-as.numeric(df2_melt$Conc)
df2_melt<-df2_melt[which(df2_melt$Group=="L100Q"),]

df_melt<-rbind(df_melt,df2_melt)
data_mean<-aggregate(value ~ Conc+Group, data = df_melt, FUN = mean)
mean_0<-data_mean[which(data_mean$Conc=="0"),]
data_mean<-merge(data_mean,mean_0[c("Group","value")],by=c("Group"),all.x=T)
data_mean$Del_Psi<-data_mean$value.x-data_mean$value.y
data_sd<-aggregate(value ~ Conc+Group, data = df_melt, FUN = sd)
comb<-merge(data_mean,data_sd,by=c("Conc","Group"))
colnames(comb)<-c("Conc","Group","Mean","Mean_0","Del_Psi","SD")
comb$Group<-factor(comb$Group,levels=c("WT","I302M","Y183*","L100Q"))

ggplot(comb,aes(x=Conc,y=Del_Psi,group=Group))+
  geom_errorbar(aes(ymin = Del_Psi - SD, ymax = Del_Psi + SD,color=Group), width = 25,size=.25)+
  geom_line(size=0.3,aes(color=Group))+
  geom_point(aes(color=Group),size=0.5)+
  scale_color_manual(values = c("WT" ="#0096FE", "I302M" ="#932191","Y183*"="#ff9200", "L100Q" ="#FF2600"))+
  theme_classic()+
  ylab(bquote(Delta~"PSI"))+
  xlab(bquote("Dox conc." ~ "(" * ng / m*L * ")"))+
  theme(legend.position = c(0.9,0.9),
        axis.text=element_text(family="Arial",size=6, color="black"),
        axis.title = element_text(family="Arial",size=6, color="black"),
        legend.key.size = unit(0.2, "cm"),
        legend.spacing.y = unit(-0.15, "cm"),
        legend.text = element_text(family="Arial",size=6, color="black"),
        legend.title = element_blank(),
        panel.background = element_blank(),
        plot.background = element_blank(), 
        panel.border = element_blank(),
        legend.background = element_blank())
ggsave("Dosage/ERCC1_combined.pdf",height=1.5,width=1.75)
```

#ACIN1
```{r}
rm(list=ls())
df<-readxl::read_excel("../Data and Code In Experimental Order/Supplemental Figures (Jan 2026 organization) /7_Dom_negative_burkitt_doxTitration/Final splicing values burkitt dox titration.xlsx",sheet="ACIN1 PSI all reps burkitt")
colnames(df)<-c("Conc","WT_1","WT_2","WT_3","I302M_1","I302M_2","I302M_3","Y183*_1","Y183*_2","Y183*_3")
df_melt<-reshape2::melt(df,id.vars = "Conc")
df_melt<-df_melt[!is.na(df_melt$value),]
df_melt$Group<-sapply(as.character(df_melt$variable),function(x){strsplit(x,"_")[[1]][1]})
df_melt$Conc<-as.numeric(df_melt$Conc)

df2<-readxl::read_excel("../Data and Code In Experimental Order/Supplemental Figures (Jan 2026 organization) /7_Dom_negative_L100Q_doxTitration/Final splicing values L100Q dox titration.xlsx",sheet="ACIN1 all reps L100Q")
colnames(df2)<-c("Conc","WT_1","WT_2","WT_3","L100Q_1","L100Q_2","L100Q_3")
df2_melt<-reshape2::melt(df2,id.vars = "Conc")
df2_melt<-df2_melt[!is.na(df2_melt$value),]
df2_melt$Group<-sapply(as.character(df2_melt$variable),function(x){strsplit(x,"_")[[1]][1]})
df2_melt$Conc<-as.numeric(df2_melt$Conc)
df2_melt<-df2_melt[which(df2_melt$Group=="L100Q"),]

df_melt<-rbind(df_melt,df2_melt)
data_mean<-aggregate(value ~ Conc+Group, data = df_melt, FUN = mean)
mean_0<-data_mean[which(data_mean$Conc=="0"),]
data_mean<-merge(data_mean,mean_0[c("Group","value")],by=c("Group"),all.x=T)
data_mean$Del_Psi<-data_mean$value.x-data_mean$value.y
data_sd<-aggregate(value ~ Conc+Group, data = df_melt, FUN = sd)
comb<-merge(data_mean,data_sd,by=c("Conc","Group"))
colnames(comb)<-c("Conc","Group","Mean","Mean_0","Del_Psi","SD")
comb$Group<-factor(comb$Group,levels=c("WT","I302M","Y183*","L100Q"))

ggplot(comb,aes(x=Conc,y=Del_Psi,group=Group))+
  geom_errorbar(aes(ymin = Del_Psi - SD, ymax = Del_Psi + SD,color=Group), width = 25,size=.25)+
  geom_line(size=0.3,aes(color=Group))+
  geom_point(aes(color=Group),size=0.5)+
  scale_color_manual(values = c("WT" ="#0096FE", "I302M" ="#932191","Y183*"="#ff9200","L100Q" ="#FF2600"))+
  theme_classic()+
  ylab(bquote(Delta~"PSI"))+
  xlab(bquote("Dox conc." ~ "(" * ng / m*L * ")"))+
  theme(legend.position = c(0.9,0.9),
        axis.text=element_text(family="Arial",size=6, color="black"),
        axis.title = element_text(family="Arial",size=6, color="black"),
        legend.key.size = unit(0.2, "cm"),
        legend.spacing.y = unit(-0.15, "cm"),
        legend.text = element_text(family="Arial",size=6, color="black"),
        legend.title = element_blank(),
        panel.background = element_blank(),
        plot.background = element_blank(), 
        panel.border = element_blank(),
        legend.background = element_blank())
ggsave("Dosage/ACIN1_combined.pdf",height=1.5,width=1.75)
```

#BAG6
```{r}
rm(list=ls())
df<-readxl::read_excel("../Data and Code In Experimental Order/Supplemental Figures (Jan 2026 organization) /7_Dom_negative_burkitt_doxTitration/Final splicing values burkitt dox titration.xlsx",sheet="BAG6 PSI all reps Burkitt")
colnames(df)<-c("Conc","WT_1","WT_2","WT_3","I302M_1","I302M_2","I302M_3","Y183*_1","Y183*_2","Y183*_3")
df_melt<-reshape2::melt(df,id.vars = "Conc")
df_melt<-df_melt[!is.na(df_melt$value),]
df_melt$Group<-sapply(as.character(df_melt$variable),function(x){strsplit(x,"_")[[1]][1]})
df_melt$Conc<-as.numeric(df_melt$Conc)

df2<-readxl::read_excel("../Data and Code In Experimental Order/Supplemental Figures (Jan 2026 organization) /7_Dom_negative_L100Q_doxTitration/Final splicing values L100Q dox titration.xlsx",sheet="BAG6 all reps L100Q")
colnames(df2)<-c("Conc","WT_1","WT_2","WT_3","L100Q_1","L100Q_2","L100Q_3")
df2_melt<-reshape2::melt(df2,id.vars = "Conc")
df2_melt<-df2_melt[!is.na(df2_melt$value),]
df2_melt$Group<-sapply(as.character(df2_melt$variable),function(x){strsplit(x,"_")[[1]][1]})
df2_melt$Conc<-as.numeric(df2_melt$Conc)
df2_melt<-df2_melt[which(df2_melt$Group=="L100Q"),]


df_melt<-rbind(df_melt,df2_melt)
data_mean<-aggregate(value ~ Conc+Group, data = df_melt, FUN = mean)
mean_0<-data_mean[which(data_mean$Conc=="0"),]
data_mean<-merge(data_mean,mean_0[c("Group","value")],by=c("Group"),all.x=T)
data_mean$Del_Psi<-data_mean$value.x-data_mean$value.y
data_sd<-aggregate(value ~ Conc+Group, data = df_melt, FUN = sd)
comb<-merge(data_mean,data_sd,by=c("Conc","Group"))
colnames(comb)<-c("Conc","Group","Mean","Mean_0","Del_Psi","SD")
comb$Group<-factor(comb$Group,levels=c("WT","I302M","Y183*","L100Q"))

ggplot(comb,aes(x=Conc,y=Del_Psi,group=Group))+
  geom_errorbar(aes(ymin = Del_Psi - SD, ymax = Del_Psi + SD,color=Group), width = 25,size=.25)+
  geom_line(size=0.3,aes(color=Group))+
  geom_point(aes(color=Group),size=0.5)+
  scale_color_manual(values = c("WT" ="#0096FE", "I302M" ="#932191","Y183*"="#ff9200","L100Q" ="#FF2600"))+
  theme_classic()+
  ylab(bquote(Delta~"PSI"))+
  xlab(bquote("Dox conc." ~ "(" * ng / m*L * ")"))+
  theme(legend.position = c(0.9,0.9),
        axis.text=element_text(family="Arial",size=6, color="black"),
        axis.title = element_text(family="Arial",size=6, color="black"),
        legend.key.size = unit(0.2, "cm"),
        legend.spacing.y = unit(-0.15, "cm"),
        legend.text = element_text(family="Arial",size=6, color="black"),
        legend.title = element_blank(),
        panel.background = element_blank(),
        plot.background = element_blank(), 
        panel.border = element_blank(),
        legend.background = element_blank())
ggsave("Dosage/BAG6_combined.pdf",height=1.5,width=1.75)
```

#CTTN
```{r,fig.height=1.5,fig.width=1.75}
rm(list=ls())
df<-readxl::read_excel("../Data and Code In Experimental Order/Supplemental Figures (Jan 2026 organization) /7_Dom_negative_burkitt_doxTitration/Final splicing values burkitt dox titration.xlsx",sheet="CTTN PSI all reps Burkitt")
colnames(df)<-c("Conc","WT_1","WT_2","WT_3","I302M_1","I302M_2","I302M_3","Y183*_1","Y183*_2","Y183*_3")
df_melt<-reshape2::melt(df,id.vars = "Conc")
df_melt<-df_melt[!is.na(df_melt$value),]
df_melt$Group<-sapply(as.character(df_melt$variable),function(x){strsplit(x,"_")[[1]][1]})
df_melt$Conc<-as.numeric(df_melt$Conc)

df2<-readxl::read_excel("../Data and Code In Experimental Order/Supplemental Figures (Jan 2026 organization) /7_Dom_negative_L100Q_doxTitration/Final splicing values L100Q dox titration.xlsx",sheet="CTTN all reps L100Q")
colnames(df2)<-c("Conc","WT_1","WT_2","WT_3","L100Q_1","L100Q_2","L100Q_3")
df2_melt<-reshape2::melt(df2,id.vars = "Conc")
df2_melt<-df2_melt[!is.na(df2_melt$value),]
df2_melt$Group<-sapply(as.character(df2_melt$variable),function(x){strsplit(x,"_")[[1]][1]})
df2_melt$Conc<-as.numeric(df2_melt$Conc)
df2_melt<-df2_melt[which(df2_melt$Group=="L100Q"),]

df_melt<-rbind(df_melt,df2_melt)
data_mean<-aggregate(value ~ Conc+Group, data = df_melt, FUN = mean)
mean_0<-data_mean[which(data_mean$Conc=="0"),]
data_mean<-merge(data_mean,mean_0[c("Group","value")],by=c("Group"),all.x=T)
data_mean$Del_Psi<-data_mean$value.x-data_mean$value.y
data_sd<-aggregate(value ~ Conc+Group, data = df_melt, FUN = sd)
comb<-merge(data_mean,data_sd,by=c("Conc","Group"))
colnames(comb)<-c("Conc","Group","Mean","Mean_0","Del_Psi","SD")
comb$Group<-factor(comb$Group,levels=c("WT","I302M","Y183*","L100Q"))

ggplot(comb,aes(x=Conc,y=Del_Psi,group=Group))+
  geom_errorbar(aes(ymin = Del_Psi - SD, ymax = Del_Psi + SD,color=Group), width = 25,size=.25)+
  geom_line(size=0.3,aes(color=Group))+
  geom_point(aes(color=Group),size=0.5)+
  scale_color_manual(values = c("WT" ="#0096FE", "I302M" ="#932191","Y183*"="#ff9200","L100Q" ="#FF2600"))+
  theme_classic()+
  ylab(bquote(Delta~"PSI"))+
  xlab(bquote("Dox conc." ~ "(" * ng / m*L * ")"))+
  theme(legend.position = c(0.9,0.9),
        axis.text=element_text(family="Arial",size=6, color="black"),
        axis.title = element_text(family="Arial",size=6, color="black"),
        legend.key.size = unit(0.2, "cm"),
        legend.spacing.y = unit(-0.15, "cm"),
        legend.text = element_text(family="Arial",size=6, color="black"),
        legend.title = element_blank(),
        panel.background = element_blank(),
        plot.background = element_blank(), 
        panel.border = element_blank(),
        legend.background = element_blank())
ggsave("Dosage/CTTN_combined.pdf",height=1.5,width=1.75)
```


#RMSD
```{r,fig.width=1.5,fig.height=1.5}
rm(list=ls())

#Interdomain
files<-list.files("~/Desktop/Dominguez_Lab/PCBP1_FINAL/MD/for-grant/figures/data/")
bins<-files[grepl("interdomain-dists-bins.txt",files)]
counts<-files[grepl("interdomain-dists-counts.txt",files)]

bins<-paste("~/Desktop/Dominguez_Lab/PCBP1_FINAL/MD/for-grant/figures/data/",bins,sep="")
counts<-paste("~/Desktop/Dominguez_Lab/PCBP1_FINAL/MD/for-grant/figures/data/",counts,sep="")

#loading
bins_list<-list()
for (f in bins){
  bins_list[[f]]<-read.table(f)
}

bins2_list<-list()
for (f in names(bins_list)){
  bins2_list[[f]]<-data.frame(bin_start = bins_list[[f]][-nrow(bins_list[[f]]),],bin_end = bins_list[[f]][-1,])
}

counts_list<-list()
for (f in counts){
  counts_list[[f]]<-read.table(f)
}

comb_list<-list()
for (i in 1:8){
  comb_list[[names(bins2_list)[i]]]<-cbind(bins2_list[[i]],counts_list[[i]])
}

files_df<-dplyr::bind_rows(comb_list, .id = "source")
files_df$Sample<-sapply(files_df$source,function(x){strsplit(x,"/")[[1]][9]})
files_df$Protein<-sapply(files_df$Sample,function(x){strsplit(x,"-")[[1]][1]})
files_df$Condition<-sapply(files_df$Sample,function(x){strsplit(x,"-")[[1]][2]})
files_df$bin_mid<-(files_df$bin_start+files_df$bin_end)/2
files_df$bin_width<-files_df$bin_end-files_df$bin_start


#hnRNP_A2B1
hnRNP_A2B1<-files_df[which(files_df$Protein=="hnRNP_A2B1"),]


ggplot(hnRNP_A2B1[which(hnRNP_A2B1$Condition %in% c("D76V","WT")),], 
       aes(x = bin_mid,y=V1, fill = Condition,color=Condition)) +
  geom_col(alpha = .8, position = "identity",size=.2,width=0.01) +
  scale_fill_manual(values = c("WT" = "#ff9c00ff","D76V" = "red")) +
  scale_color_manual(values = c("WT" = "#ff9c00ff","D76V" = "red")) +
  theme_classic()+
  labs(x="Distance, (Å)",y="Probabiity")+
  theme(legend.position = c(0.9,0.9),
        axis.text=element_text(family="Arial",size=6, color="black"),
        legend.text = element_text(family="Arial",size=6, color="black"),
        legend.title = element_blank(),
        axis.title = element_text(family="Arial",size=6, color="black"),
        panel.background = element_blank(),
        plot.background = element_blank(), 
        panel.border = element_blank(),
        legend.background = element_blank(),
        legend.key.width= unit(0.2, 'cm'),
        legend.key.height= unit(0.2, 'cm'))
ggsave("RMSD/HNRNPA1_main.pdf",height=1.5,width=1.5)

ggplot(hnRNP_A2B1[which(hnRNP_A2B1$Condition %in% c("D76N","D76H","WT")),], aes(x = bin_mid,y=V1, fill = Condition)) +
  geom_col(alpha = .8, position = "identity",color="black",size=.2,width=0.1) +
  scale_fill_manual(values = c("WT" = "#ff9c00ff","D76N" = "red","D76H"="pink")) +
  theme_classic()+
  labs(x="Distance, (Å)",y="Probability")+
  theme(legend.position = c(0.9,0.9),
        axis.text=element_text(family="Arial",size=6, color="black"),
        legend.text = element_text(family="Arial",size=6, color="black"),
        legend.title = element_blank(),
        axis.title = element_text(family="Arial",size=6, color="black"),
        panel.background = element_blank(),
        plot.background = element_blank(), 
        panel.border = element_blank(),
        legend.background = element_blank(),
        legend.key.width= unit(0.2, 'cm'),
        legend.key.height= unit(0.2, 'cm'))

ggsave("RMSD/HNRNPA1_supp.pdf",height=1.5,width=1.5)

#hnRNP_A2B1
UP1<-files_df[which(files_df$Protein=="UP1"),]

ggplot(UP1, aes(x=bin_mid,y = V1, fill = Condition)) +
  geom_col(alpha = .8, position = "identity",color="black",size=.2,width=0.1) +
  scale_fill_manual(values = c("WT" = "#ffff47ff","M72I" = "red")) +
  theme_classic()+
  labs(x="Distance, (Å)",y="Probability")+
  theme(legend.position = c(0.9,0.9),
        axis.text=element_text(family="Arial",size=6, color="black"),
        legend.text = element_text(family="Arial",size=6, color="black"),
        legend.title = element_blank(),
        axis.title = element_text(family="Arial",size=6, color="black"),
        panel.background = element_blank(),
        plot.background = element_blank(), 
        panel.border = element_blank(),
        legend.background = element_blank(),
        legend.key.width= unit(0.2, 'cm'),
        legend.key.height= unit(0.2, 'cm'))

ggsave("RMSD//UP1_main.pdf",height=1.5,width=1.5)


#PCBP1
PCBP1<-files_df[which(files_df$Protein=="PCBP1"),]
PCBP1$Condition[which(PCBP1$Condition=="wt")]<-"WT"

ggplot(PCBP1, aes(x=bin_mid,y = V1, fill = Condition)) +
  geom_col(alpha = .8, position = "identity",color="black",size=.2,width=0.1) +
  scale_fill_manual(values = c("WT" = "#ffff47ff","L100Q" = "red")) +
  theme_classic()+
  labs(x="Distance, (Å)",y="Probability")+
  theme(legend.position = c(0.85,0.9),
        axis.text=element_text(family="Arial",size=6, color="black"),
        legend.text = element_text(family="Arial",size=6, color="black"),
        legend.title = element_blank(),
        axis.title = element_text(family="Arial",size=6, color="black"),
        panel.background = element_blank(),
        plot.background = element_blank(), 
        panel.border = element_blank(),
        legend.background = element_blank(),
        legend.key.width= unit(0.2, 'cm'),
        legend.key.height= unit(0.2, 'cm'))

ggsave("RMSD//PCBP1_main.pdf",height=1.5,width=1.5)



leg<-read.table("MD/for-grant/figures/data/hnRNP_A2B1-D76H-rad-0.30-interdomain-dists-bins.txt")
leg2<-read.table("MD/for-grant/figures/data/hnRNP_A2B1-D76H-rad-0.30-interdomain-dists-counts.txt")


```


